### 2014-04-10 tech-project/paper.tex
adding paper

% CpSc 855 - Final paper
% Takumi Bolte & Dan Welch - Spring 2014.
\documentclass{sig-alternate}
%\usepackage{flushend}		% For automatically balancing reference columns

\begin{document}
\conferenceinfo{Clemson 2014}{7th Clemson University Mini-Conference on Embedded Network Systems}
\title{An Extensible Approach to Verification of Embedded Network Systems*}

%Re-evaluating Verification of Embedded Network Systems:
%An Extensible Approach to Verification of Embedded Network Systems*}
\numberofauthors{2}
\author{
\alignauthor
%author
Daniel Welch\\
\affaddr{School of Computing, Clemson University}\\
\affaddr{Clemson, South Carolina, 29634}\\
\email{\texttt{\large{\{dtwelch\}@clemson.edu}}}
%author
\alignauthor
Takumi Bolte\\
\affaddr{School of Computing, Clemson University}\\
\affaddr{Clemson, South Carolina, 29634}\\
\email{\texttt{\large{\{tbolte\}@clemson.edu}}}
}

\maketitle
\begin{abstract}

In this paper we present a flexible means of specifying and verifying the correctness of software for embedded network systems. Our approach uses RESOLVE, an imperative, component based programming and mathematical specification language, to verify the functional correctness of TinyOS applications. In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non RESOLVE) realizations. We demonstrate these additions with a revised version of the LED template originally presented in \cite{regula:2010} that showcases some of the more recent mathematical developments in ``string theory" (resolve's mathematical string library) as well as verification of a simple enhancement for Leds template that includes preliminary generation of performance profile characteristics.
\end{abstract}

\category{D.2.8}{Software Engineering and Data Communication}{Verification}[VCs, automated proving, modular software]
\terms{Reliability, Verification, Languages, Networks}
\keywords{automation, components, formal methods, specification, verifying compiler, embedded networks, wireless sensing}

\section{Introduction}
\label{sec:intro}
Within little more than a decade, the area of embedded network systems and wireless sensing has exploded in popularity within industry and academia alike. Tempering however this extremely quick rise in popularity is the inherent difficulties in developing applications that function as intended in low power, event-driven environments. In response to these difficulties, a variety of tools and languages have been put forth  to help ease the burden on developers. On one end of this effort are languages such as NesC (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions. The other end is largely comprised of simulation tools such as TOSSIM, Cooja, and Arora that make use of high-fidelity simulations of mote network and hardware behavior to model networks offline in controlled, repeatable environments.

Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed in the field.

In this paper, we approach this problem by using RESOLVE (Reusable Software Language with Verification) [CITE] [CITE] [CITE] as means of specifying, writing, and ultimately verifying proposed embedded code at a high level, then present a technique of translating this verified code down into lower level, embedded-platform friendly C.

Our choice to use RESOLVE as a language and verification frontend stems from the language's well acknowledged characteristics [CITE] that emphasize the following:
\begin{itemize}
\item \textbf{Modularity} At the language level, a strict separation of concerns is enforced between module specifications and client implementations. Thus, for any one particular specification, there can be any number of interchangeable implementations. This separation is ideal considering that many embedded applications are composed in similar fashion: Various drivers oftentimes provide a fixed set of operations, but have many distinct implementations that vary from platform to platform, vendor to vendor.

\item \textbf{Mathematical flexibility} RESOLVE offers a flexible mathematical typing system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or create their own.

\end{itemize}

This paper aims to leverage RESOLVE's mathematical flexibility of and component based design principles to the challenge of formally verifying an LED driver for the Telos motestack family.

We discuss this challenge in three parts. In the first, we provide both a short overview of the Telos family mote platform -- including a description of the LEDs driver which we later specify, verify, and translate -- as well as a short overview of the RESOLVE language itself. In the second section, we provide revised specifications for the LED drivers as well as a single enhancement on these drivers. This is followed by a review discussing the results of verification along with a review of some verification conditions generated by the compiler involving preliminary results for performance characteristics of enhancements. In the third and final section of the paper, we discuss the tool itself -- providing implementation details as well as a discussion of how this iteration of the tool differs from that originally detailed in \cite{regula:2010}. Finally, we conclude by discussing tool improvements and directions for future research.
\begin{figure*}
\centering
\includegraphics[scale=.55]{figs/ast_traversal.pdf}
\caption{An AST of a RESOLVE operation and its corresponding AST treewalker call sequence.}
\end{figure*}
\label{fig:ast}
\section{A model for c translation}

One of the primary challenges in translating from RESOLVE to C is finding a suitable C representation for each RESOLVE module and the constructs allowable in each. As we are dealing with an environment where functional correctness is a primary concern, it is especially important that the code generated represents as closely as possible the original RESOLVE source. In an effort to make such considerations, at the highest level, our tool outputs code specifically tailored to one of three distinct RESOLVE module types.

\begin{description}
\item [Concepts]
To model as closely as possible the role of a concept module, our tool produces a single .h file that contains structures for each parameter to a concept, pointers corresponding to the abstract types defined by the concept, as well as set of function pointers for each of the methods provided by the original RESOLVE concept.

\item [Realizations] 
Referring to both enhancement realizations as well as concept realizations, these are translated into a .h/.c pair. The header portion of this pair contains function declarations for the creation and destruction of a ``Realization\_Specific" facility. Elements of this facility are accessible only through a concept interface. The .c file has 5 sections:

\item [Facilities]

\end{description}

The representation of objects make use of a special

\section{Implementation}
Development of the tool presented here can be logically partitioned into two phases: The tool that performs the actual translation from RESOLVE to C, and a separate tool that is called by the generated code that is responsible for allocating appropriate amounts of memory on the motestack without needing to resort to static allocation.

\subsection{Translation AST walking}
Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST). The traversal mechanism used is a dervivative of the visitor pattern that provides a SAX-dom style pre-post traversal over all nodes in the tree. Thus, for any given node present, a total of two visits occur: One corresponding to the node being `hit' during the pre traversal stage, and one for the post.

To make this more concrete, consider the following dummy operation.

\begin{verbatim}
operation nothing() procedure;
    var x : Integer;
    x := 3;
end nothing;
\end{verbatim}

Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{nothing}. Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack. Each of these calls are received in the translator in the order in which they are visited within the tree. It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.

We feel this particular traversal pattern lends itself well to the this application for the following reasons:

\begin{itemize}
\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to an appropriate C construct $y$.

\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.

\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden. This makes it especially easy to tweak and optimize the size of the codebase for the C translator.
\end{itemize}

\subsection{Translation output}
Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates. Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.

An example of a template for a function/operation definition might look like the following:

\begin{verbatim}
function_def(modifier, type, name, params, 
                               vars, stmts) ::= <<
<modifier> <type> <name> (<params; sep = ", ">) {
    <vars; sep = "\n">
    <stmts; sep = "\n">
}>>
\end{verbatim}

Words enclosed in \texttt{<..>} signifies an attribute passable to the template and indicates where it will be positioned. It is entirely up to the user to define which attributes they wish to fill in, and at what level of granularity they wish to compose their templates. For example, the user might opt to fill-in and pass the \texttt{parameter(..)} template shown below to the \texttt{params} attribute, or, alternatively, a simple string.

\begin{verbatim}
parameter(type, name) ::= "<type> <name>"
\end{verbatim}

In the context of language translation, these templates when stored on a stack and manipulated over the course of the AST traversal, simplify the task of producing arbitrarily complicated, nested blocks of C output. For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in. As \texttt{preOperationDec}'s children get visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the corresponding child nodes. Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in -- assuming the user implemented the visit methods for the children.

Hence, the only work being done within visit methods themselves is forwarding appropriate information from tree-nodes to an externally defined template. This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in our translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).

%One of the primary allures of this approach to translation is that that adheres to strict MVC design principles -- meaning that all output logic is distinctly separated from translation related logic.

%We take advantage of these pre post methods using templates and simple stack to implement

%Going even further, we demonstrate this by showing the steps taken to translate a simple operation declaration \texttt{nothing} to C.

% for each construct to remain encapsulated within that method, and (almost) completely eliminates the need for complex loop or iteration mechanisms.

%This particular traversal pattern lends itself well to the language translation challenge (specifically source to source) where the pre methods align naturally with beginning of a construct, and conclude with its corresponding post method.  For instance, in the case above, this allows us, upon receiving a callback for In an effort to keep logic implementing our translator distinct and separate from the output language, we used a model view controller framework for implementing

%To illustrate this, consider once again facility \texttt{DoNothing}.

\subsection{Garbage collection}

a source to source translator which, given a resolve component, outputs a C representation of that component.

%To date there have been very few practical applications of verifiable code on physical media.

\section{Acknowledgements}

Special thanks to Mike Kabanni and Mark Todd whose initial contributions and suggestions for the model of C translation paved the way to this paper.

%Open up the .tex file and compile it using Latex (Shift+Apple+L) then compile it using Bibtex (Shift+Apple+B)
\bibliographystyle{unsrt}
\bibliography{sigproc}
\end{document}

### 2014-04-20 tech-project/paper.tex
updating paper

@@
 \documentclass{sig-alternate}
-%\usepackage{flushend}		% For automatically balancing reference columns
 
+\usepackage{mathrsfs}
+\usepackage{booktabs}
+\usepackage{placeins}
+\usepackage{graphicx}
+\usepackage{subfigure}
+\usepackage{listings}
 \begin{document}
@@
 Our approach uses RESOLVE, an imperative, component based programming and mathematical specification language, to verify the functional correctness of TinyOS applications.
-In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non RESOLVE) realizations.
-We demonstrate these additions with a revised version of the LED template originally presented in \cite{regula:2010} that showcases some of the more recent mathematical developments in ``string theory" (resolve's mathematical string library) as well as verification of a simple enhancement for Leds template that includes preliminary generation of performance profile characteristics.
+In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non-native RESOLVE) realizations.
+We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of two enhancements that we demonstrate running on a Telos mote.
 \end{abstract}
@@
 In response to these difficulties, a variety of tools and languages have been put forth  to help ease the burden on developers.
-On one end of this effort are languages such as NesC (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
-The other end is largely comprised of simulation tools such as TOSSIM, Cooja, and Arora that make use of high-fidelity simulations of mote network and hardware behavior to model networks offline in controlled, repeatable environments.
-
+On one end of this effort are languages such as NesC, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
+The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Arora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
 Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed in the field.
 
-In this paper, we approach this problem by using RESOLVE (Reusable Software Language with Verification) [CITE] [CITE] [CITE] as means of specifying, writing, and ultimately verifying proposed embedded code at a high level, then present a technique of translating this verified code down into lower level, embedded-platform friendly C.
+We approach this problem by using RESOLVE (Reusable SOftware Language with VErification) as means of authoring, specifying, and ultimately verifying code for embedded network systems.
+Our decision to use RESOLVE as a language frontend -- as opposed to verifying C code directly -- ultimately stems from a verification amenability standpoint: Not only does RESOLVE prohibit verification crippling operations such as uncontrolled referencing and aliasing (prevalent in C and many other current languages)\cite{kulczycki:2004}, but also embodies a number of other characteristics ideal for embedded platforms including:
 
-Our choice to use RESOLVE as a language and verification frontend stems from the language's well acknowledged characteristics [CITE] that emphasize the following:
 \begin{itemize}
-\item \textbf{Modularity} At the language level, a strict separation of concerns is enforced between module specifications and client implementations.
-Thus, for any one particular specification, there can be any number of interchangeable implementations.
-This separation is ideal considering that many embedded applications are composed in similar fashion: Various drivers oftentimes provide a fixed set of operations, but have many distinct implementations that vary from platform to platform, vendor to vendor.
+\item \textbf{Modularity} RESOLVE enforces a strict separation of concerns between module specifications and client implementations.
+As a result, for any one particular specification, there can be any number of interchangeable implementations.
+This separation is ideal considering that many embedded applications happen to fit this pattern nicely: Various drivers oftentimes provide a common set of functionality, but in general have many distinct implementations that vary arbitrarily from platform to platform, vendor to vendor.
 
-\item \textbf{Mathematical flexibility} RESOLVE offers a flexible mathematical typing system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or create their own.
+\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
+This ideal in a setting where various driver applications are varied and new contexts might require creating new theory constituents appropriate for specific drivers.
+% reword this to be less vague.
 
@@
 
-This paper aims to leverage RESOLVE's mathematical flexibility of and component based design principles to the challenge of formally verifying an LED driver for the Telos motestack family.
+The paper is organized as follows: First, we open with a brief overview of the Telos mote platform.
+Next, we present revised specifications of an LED driver component with a formally verified enhancement.
+This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used.
+The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code.
+We conclude with suggestions for tool improvements, as well as a review of some longer term research goals.
 
-We discuss this challenge in three parts.
-In the first, we provide both a short overview of the Telos family mote platform -- including a description of the LEDs driver which we later specify, verify, and translate -- as well as a short overview of the RESOLVE language itself.
-In the second section, we provide revised specifications for the LED drivers as well as a single enhancement on these drivers.
-This is followed by a review discussing the results of verification along with a review of some verification conditions generated by the compiler involving preliminary results for performance characteristics of enhancements.
-In the third and final section of the paper, we discuss the tool itself -- providing implementation details as well as a discussion of how this iteration of the tool differs from that originally detailed in \cite{regula:2010}.
-Finally, we conclude by discussing tool improvements and directions for future research.
+\section{The Telos Platform}
+
+The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley.
+Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory.
+A cc2420 radio stack provides the mote with broadcast and receiving capabilities, while optional sensing capabilities may be added in the form of light, humidity, and temperature sensors.
+The mote also contains three onboard LEDs: One blue, one red, and one green.
+
+%Additionally, the Telos board contains a total of three LEDs -- one red, one green, and one blue.
+\section{Specifiying LED behavior in Resolve}
+\label{sec:specifiying}
+
+In RESOLVE, programs are composed of several different modules that range from interfaces and realizations, to client (facility) modules.
+In this section, we provide mathematical and programmatic elements of an LED strip component to give readers both a concrete look at the language, and introduce some new features aimed at making it more amenable to the development of embedded applications.
+Note that while we provide the level of detail necessary to understand the current example, readers interested in gaining a more complete, in depth knowledge of the language are encouraged to refer to \cite{sitaraman:2011, kulczycki:2008}.
+
+\subsection{Concepts}
+
+A \textit{concept} module in RESOLVE defines a specification for a mathematical, abstract type.
+Similar to an interface in Java, a concept provides a number of operation signatures that implementors are expected to realize.
+Shown below is a \texttt{LED\_Template} concept that provides a light strip abstraction.
+
+\begin{verbatim}
+Concept LED_Template(eval Strip_Length: Integer);
+    uses Boolean_Theory, String_Theory;
+    requires 0 < Strip_Length <= 4;
+
+    Type Family LED is modeled by Str(B);
+        exemplar L;
+        constraint |L| = Strip_Length;
+        initialization ensures 
+            ...
+
+    Oper Set(updates L : LED; eval b : Boolean; 
+                             eval i : Integer);
+        requires 0 <= i < |L|;
+        ensures |L| = |#L| and 
+                   Element_At(i, L) = b;
+
+    Oper Status(preserves L : LED; 
+                   eval i : Integer) : Boolean;
+        requires 0 <= i < |L|;
+        ensures Status = Element_At(i, L);
+
+end LEDs_Template;
+\end{verbatim}
+
+We model our conceptual LED strip using a mathematical string (finite sequence) of booleans, denoted \texttt{Str(B)}, where each boolean within the string indicates the status of that particular LED: On (true) or off (false).
+The \texttt{exemplar} clause located immediately below provides a handle to this abstract model, and is used throughout the remainder of the specification.
+
+%The \texttt{Type Family} clause introduces an abstract type for the LED strip which we mathematically model using strings of booleans, denoted \texttt{Str(B)}, while the \texttt{exemplar} declared immediately after provides a handle to this type family.
+Use of the \texttt{exemplar} can be observed in the \texttt{constraint} clause, where it is used to assert that length of the strip is fixed to be whatever the user has specified via the \texttt{Strip\_Length} parameter.
+Finally, the \texttt{initialization} \texttt{ensures} clause makes explicit the state of the structure at the time it is initialized.
+We omit this verification specific clause, as it has little bearing on verification due to the fact that the realization we provide is \textit{externally} realized -- a point discussed in the next section\footnote{This clause, if it were provided, would need to communicate the following: ``For each position $i$ within the strip, the LED (or, value) at position $i$ is initially false."}
+
+It's worth noting that unlike the \texttt{LED\_Template} presented in \cite{regula:2010} which models an LED as the \textit{cartesian product} of booleans $b_1$, $b_2$, \ldots , $b_4$, the strip model we present here instead uses strings for the following reasons:
+\begin{itemize}
+\item Strings are indexible, and thus do not require separate \texttt{Set} and \texttt{Status} operations for each individual LED.
+\item This approach demonstrates the benefits of reusable mathematical theories.
+The specifications here are based solely in \texttt{String\_Theory}, a pre-existing RESOLVE math library that provides all the definitions and theorems used in this specification.
+\end{itemize}
+
+The concept provides two operations.
+The first of the two, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
+The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion that:
+\begin{enumerate}
+\item The length of the outgoing strip \texttt{L}, is the same length as the incoming strip, \texttt{\#L} (where \texttt{\#} signifies its incoming state).
+\item The LED in position \texttt{i} of \texttt{L} is set to boolean parameter \texttt{b}. 
+\end{enumerate}
+Operation \texttt{Status}, which simply returns the state of the LED at position \texttt{i}, is specified similarly.
+
+%Each operation carries with it a pre and post condition in the form of \texttt{requires} and \texttt{ensures} clause, which make explicit what must be true coming into the function, and what must be true after.
+For instance, the requires clause to \texttt{Status} states that \texttt{i} must fall somewhere within the bounds of the string which models our LED strip, while the \texttt{ensures} clause makes use of a \texttt{String\_Theory} definition, \texttt{Element\_At}, to assert that the boolean returned from \texttt{Status} is indeed the value occupying position \texttt{i} of \texttt{L}.
+It's important to note that the variables appearing in the \texttt{requires} and \texttt{ensures} clauses are strictly mathematical values.
+Thus, the \texttt{L} parameter of operation \texttt{Status} is referring to the mathematical value of an \texttt{LED}, as opposed to a programmatic one (typically defined in a realization).
+
+%\subsection{An External LED Realization}
+
+%Armed with a specification, the RESOLVE programmer would now ideally provide a verifiable implementation of \texttt{LEDs\_Template} via a RESOLVE realization.
+However, as our target platform is embedded, and our concept  aims to provide control for LEDs -- a decidedly low level feature -- our realization is forced to operate at similarly low levels by manually interfacing with hardware pins provided by msp430 chipset.
+RESOLVE, however in its current state is far too high level of a language to perform these tasks directly -- that is, it currently lacks driver support to do so.
+To address this difficulty, we introduce language support for \textit{external realizations}, which, in essence, leaves the user free to write their own realization of a concept in whatever language is most convenient.
+In the case of \texttt{LEDs\_Template}, we provide a hand written \texttt{Telos\_LEDs\_Realiz} C realization that matches as closely as possible the model of translation detailed in Section \#.
+
+%More than givingHaving the freedom to use RESOLVE's specificational capabilities
+
+\subsection{Enhancements}
+
+RESOLVE also allows users to extend the functionality provided by the base concept through \textit{enhancements} -- a form of specification inheritance.
+The enhancement we provide here is  \texttt{Toggling\_Capability}, which gives users of the LED component the ability to toggle a specific LED on or off.
+
+Shown below is a specification for \texttt{Toggling\_Capability} and one particular realization of it.
+
+\begin{verbatim}
+Enhancement Toggling_Capability for LEDs_Template;
+
+    Oper Toggle(upd L : LED; eval i : Integer);
+        requires 0 <= i < |L|;
+        ensures Element_At(i, L) = 
+                        not(Element_At(i, #L));
+end Toggling_Capability;
+
+Realization Toggling_Realiz for
+            Toggling_Capability of LEDs_Template;
+
+    Proc Toggle(upd L : LED; eval i : Integer);
+        Var Content : Boolean;
+
+        Content := Status(L, Replica(i));
+        Set(L, Not(Content), Replica(i));
+    end Toggle;
+
+end Toggling_Realiz;
+\end{verbatim}
+
+The specification of \texttt{Toggle} states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
+
+Note that the enhancement specifications themselves look and function largely the same as a normal concept: Each specifies a purely conceptual module, and hence is implementation neutral.
+
+Even realizations of enhancements are neutral since they are only permitted to call operations provided by the base concept -- thus requiring no knowledge of how the called operation is actually implemented.
+
+\subsection{Verification}
+
+In this section we verify our realization of \texttt{Toggling\_Capability}.
+The first step in this process is to generate verification conditions (VCs) for \texttt{Toggling\_Realiz}, which, if proven, will establish the correctness of that particular realization\footnote{Note: VCs themselves are typically generated from specific lines of a realization to ensure that the overall content of a realization is consistent with its specification.}.
+
+\begin{figure}[!htb]
+\centering
+\begin{tabular}{lccc}
+	\toprule
+	Condition \# & Time (ms)	& Steps	& Search \\
+	\midrule
+	VC 0\_1	& 4426	& 5	& 0	\\
+	VC 0\_2	& 5039	& 5	& 0	\\
+	VC 0\_3	& 6324	& 5	& 0	\\
+	\bottomrule
+\end{tabular}
+\end{figure}
+
+The results of verification are summarized Figure \ref{fig:results}.
+As shown, the correctness of \texttt{Toggle} is straightforward enough for the prover to establish automatically, however \texttt{Set\_First\_And\_Last}'s VC 0\_5 failed to be dispatched.
+
+\begin{figure}[!htb]
+\begin{verbatim}
+Goal:
+Element_At((|L'|  - |L'|), L') = b
+
+Given:
+    ...
+1. |L| = Strip_Length and
+2. |L|  > 1 and
+3. |L''| = |L| and
+4. Element_At(0, L'') = b
+5. |L'| = |L''| and
+6. Element_At((|L''|  - 1), L') = b)
+\end{verbatim}
+\caption{A problematic VC}
+\label{fig:problematicVC}
+\end{figure}
+
+A cursory examination of the unproven VC, shown in Figure \ref{fig:problematicVC}, reveals that prover was not able to employ the seemingly relevant \texttt{given \#4} since \texttt{L"}, could not be considered (rightfully so) the same as \texttt{L'} due to the changing boolean value.
+There are several means of correcting this: The first involves amending the \texttt{ensures} clause of operation \texttt{Set} (which is used in \texttt{Set First And Last}) to intuitively say that ``the content of \textit{outgoing} \texttt{L} is equivalent to the that of the incoming \texttt{L} with the exception of position \texttt{i}.
+The second route -- perhaps the less preferable of the two -- involves adding new theorems to \texttt{String\_Theory} which state this.
+
+FIGURE OUT AN ELEGANT WAY TO CONCLUDE THIS SECTION...
+
+\subsection{Facilities}
+\label{sec:facilities}
+The most straightforward means of utilizing our previously defined Led strip component and its verified enhancements is a via \textit{facility} module. Figure \# depicts a simple
+
+%mention performance stuff in future work section.
+
 \begin{figure*}
@@
 \includegraphics[scale=.55]{figs/ast_traversal.pdf}
-\caption{An AST of a RESOLVE operation and its corresponding AST treewalker call sequence.}
+\caption{A RESOLVE operation AST, the walk call sequence, and sample translation output.}
 \end{figure*}
 \label{fig:ast}
-\section{A model for c translation}
 
-One of the primary challenges in translating from RESOLVE to C is finding a suitable C representation for each RESOLVE module and the constructs allowable in each.
-As we are dealing with an environment where functional correctness is a primary concern, it is especially important that the code generated represents as closely as possible the original RESOLVE source.
-In an effort to make such considerations, at the highest level, our tool outputs code specifically tailored to one of three distinct RESOLVE module types.
+% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE...
+AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE.
+BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
+\section{Implementation}
+Development of the tool presented here can be logically partitioned into three distinct phases: 
+\begin{enumerate}
+\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
+\item Implementing reusable mechanisms for carrying out the C code generation process.
+\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
+\end{enumerate}
+In this section we discuss each of these phases, concluding with a demo illustrating each working in tandem to realize the example presented in section \ref{sec:specifiying}.
 
-\begin{description}
-\item [Concepts]
-To model as closely as possible the role of a concept module, our tool produces a single .h file that contains structures for each parameter to a concept, pointers corresponding to the abstract types defined by the concept, as well as set of function pointers for each of the methods provided by the original RESOLVE concept.
+\subsection{C Translation Model}
+One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each.
+Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source.
+In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
 
-\item [Realizations] 
-Referring to both enhancement realizations as well as concept realizations, these are translated into a .h/.c pair.
-The header portion of this pair contains function declarations for the creation and destruction of a ``Realization\_Specific" facility.
-Elements of this facility are accessible only through a concept interface.
-The .c file has 5 sections:
+The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
 
-\item [Facilities]
+Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
 
-\end{description}
+\begin{figure}
+\centering
+\includegraphics[scale=.55]{figs/relationship.pdf}
+\caption{RESOLVE module types and their corresponding C representation}
+\end{figure}
+\label{fig:ast}
 
-The representation of objects make use of a special
+\subsection{Translator Implementation}
 
-\section{Implementation}
-Development of the tool presented here can be logically partitioned into two phases: The tool that performs the actual translation from RESOLVE to C, and a separate tool that is called by the generated code that is responsible for allocating appropriate amounts of memory on the motestack without needing to resort to static allocation.
-
-\subsection{Translation AST walking}
+\subsubsection{AST Traversal}
 Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
@@
 \begin{verbatim}
-operation nothing() procedure;
-    var x : Integer;
-    x := 3;
-end nothing;
+Operation Nothing(); Procedure
+        Var X : Integer;
+        X := 3;
+end Nothing;
 \end{verbatim}
 
-Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{nothing}.
+Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
 Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack.
@@
 
-We feel this particular traversal pattern lends itself well to the this application for the following reasons:
+We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
 
 \begin{itemize}
-\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to an appropriate C construct $y$.
+\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
 
@@
 \item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
-This makes it especially easy to tweak and optimize the size of the codebase for the C translator.
+This makes it easy to tweak and optimize the size of the translator's codebase, implementing only visit method for language constructs that explicitly require translation.
 \end{itemize}
 
-\subsection{Translation output}
+\subsubsection{Translation output}
 Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
@@
 
-An example of a template for a function/operation definition might look like the following:
+An example C function definition template is shown below.
 
@@
 
-Words enclosed in \texttt{<..>} signifies an attribute passable to the template and indicates where it will be positioned.
-It is entirely up to the user to define which attributes they wish to fill in, and at what level of granularity they wish to compose their templates.
-For example, the user might opt to fill-in and pass the \texttt{parameter(..)} template shown below to the \texttt{params} attribute, or, alternatively, a simple string.
+User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
+It is entirely up to the user to define which attributes to fill in, and how complex they want them to be.
+For example, the user might choose to fill the \texttt{params} attribute with a simple string, or a separately defined \texttt{parameter} template, which in turn might use another separately defined \texttt{type} template.
 
@@
 
-In the context of language translation, these templates when stored on a stack and manipulated over the course of the AST traversal, simplify the task of producing arbitrarily complicated, nested blocks of C output.
+In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
 For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in.
-As \texttt{preOperationDec}'s children get visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the corresponding child nodes.
-Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in -- assuming the user implemented the visit methods for the children.
+As \texttt{preOperationDec}'s children are visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the nodes being walked.
+Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in with the appropriate templates -- assuming the user has implemented the children's visit methods.
 
-Hence, the only work being done within visit methods themselves is forwarding appropriate information from tree-nodes to an externally defined template.
-This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in our translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).
+Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
+This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).
 
@@
 
-\subsection{Garbage collection}
+\subsection{Memory Allocation}
 
-a source to source translator which, given a resolve component, outputs a C representation of that component.
+Dynamic memory allocation does not lend itself well with an embedded programming paradigm.
+With hardware constraints, embedded systems have limited capacities on RAM.
+The telos motes are limited to 128 bytes of RAM.
+Many programs, however, require dynamic memory allocation to be used, including RESOLVE, in order to make it extensible.
+In this section we introduce a stack memory allocator.
+
+\subsubsection{Allocation using salloc}
+
+The \texttt{salloc} is a first fit memory allocator that is provided memory of fixed size that is determined at compile time.
+It requires a small section of meta-data called a block which stores information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
+A sample representation of the stack as shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=.55]{figs/stack.pdf}
+\caption{Representation of memory stack}
+\end{figure}
+\label{fig:stack}
+
+\subsubsection{Deallocation using sfree}
+
+A memory allocator must provide a mechanism to release  or free memory in order to indicate that it is not being used and can be reallocated for something else.
+The \texttt{sfree} operation is an analogous implementation to the standard C \texttt{free} function for the stack.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=.55]{figs/free.pdf}
+\caption{sfree to free memory}
+\end{figure}
+\label{fig:free}
+
+\subsubsection{Optimizations}
+
+A common problem that can occur in memory allocation is fragmentation.
+As show in figure ??, fragmentation can lead to inefficient and increased memory usage.
+This problem is magnified on embedded systems with limited memory capabilities.
+Simple optimizations can be made however to reduce fragmentation.
+Splitting is one optimization that \texttt{salloc} uses to maximize memory usage.
+Shown in figure \ref{fig:split}, previously allocated blocks that have been freed, can be split to the size that is required by a call to \texttt{salloc}.
+Another means of optimizing memory usage is fusing together freed blocks.
+When a call to \texttt{sfree()} is made, neighboring blocks are coalesced together, as shown in figure \ref{fig:fuse}.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=.55]{figs/split.pdf}
+\caption{block-splitting}
+\end{figure}
+\label{fig:split}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=.55]{figs/fuse.pdf}
+\caption{fusing blocks}
+\end{figure}
+\label{fig:fuse}
+%A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.
 
@@
 
-Special thanks to Mike Kabanni and Mark Todd whose initial contributions and suggestions for the model of C translation paved the way to this paper.
+Special thanks to Mike Kabanni, Mark Todd, and Bruce Weide whose suggestions and initial contributions in constructing the current model of RESOLVE to C translation made this work possible.
 

### 2014-04-20 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Boolean_Template/Std_Boolean_Realiz.c

@@ -5,98 +5,98 @@ static int ValueOf(r_type_ptr r) {
 }
 
 static r_type_ptr createFromBoolean(int I, type_info* ti) {
-	int *space = calloc(1, sizeof(int));
+	int *space = scalloc(1, sizeof(int));
 	*space = I;
-	int** ret = malloc(sizeof(int*));
+	int** ret = salloc(sizeof(int*));
 	*ret = space;
 	return (r_type_ptr)ret;
 }
 
 static r_type_ptr createBoolean(type_info* ti) {
-    int* t = calloc(1, sizeof(int));
+    int* t = scalloc(1, sizeof(int));
     *t = 0;
-    int** ret = malloc(sizeof(int*));
+    int** ret = salloc(sizeof(int*));
     *ret = t;
     return (r_type_ptr)ret;
 }
 
 static void destroyBoolean (r_type_ptr r, type_info* ti) {
-    free(*r);
-    free(r);
+    sfree(*r);
+    sfree(r);
 }
 
 static type_info* newBoolean() {
-    type_info* pc = calloc(1, sizeof(type_info));
+    type_info* pc = scalloc(1, sizeof(type_info));
     pc->create = createBoolean;
     pc->destroy = destroyBoolean;
     return pc;
 }
 
 static r_type_ptr True(Boolean_Template* this) {
-	int *space = calloc(1, sizeof(int));
+	int *space = scalloc(1, sizeof(int));
 	*space = 1;
-	int** ret = malloc(sizeof(int*));
+	int** ret = salloc(sizeof(int*));
 	*ret = space;
 	return (r_type_ptr)ret;
 }
 
 static r_type_ptr False(Boolean_Template* this) {
-	int *space = calloc(1, sizeof(int));
+	int *space = scalloc(1, sizeof(int));
 	*space = 0;
-	int** ret = malloc(sizeof(int*));
+	int** ret = salloc(sizeof(int*));
 	*ret = space;
 	return (r_type_ptr)ret;
 }
 
 static r_type_ptr And(r_type_ptr b1, r_type_ptr b2, Boolean_Template* this) {
-	int *space = calloc(1, sizeof(int));
+	int *space = scalloc(1, sizeof(int));
 	*space = ((**(int**)b1 == 1) && (**(int**)b2 == 1));
 
-	int** ret = malloc(sizeof(int*));
+	int** ret = salloc(sizeof(int*));
 	*ret = space;
[…]

### 2014-04-20 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Integer_Template/Std_Integer_Realiz.c

@@ -5,48 +5,52 @@ static int ValueOf(r_type_ptr r) {
     return **(int**)r;
 }
 
+static void assign(r_type_ptr r, r_type_ptr i, IntegerTemplate* this) {
+	**(int**)r = **(int**)i;	
+}
+
 static r_type_ptr createFromInteger(int I, type_info* ti) {
-	int *space = calloc(1, sizeof(int));
+	int *space = scalloc(1, sizeof(int));
 	*space = I;
-	int** ret = malloc(sizeof(int*));
+	int** ret = salloc(sizeof(int*));
 	*ret = space;
 	return (r_type_ptr)ret;
 }
 
 static r_type_ptr createInteger(type_info* ti) {
-    int* t = calloc(1, sizeof(int));
+    int* t = scalloc(1, sizeof(int));
     *t = 0;
-    int** ret = malloc(sizeof(int*));
+    int** ret = salloc(sizeof(int*));
     *ret = t;
     return (r_type_ptr)ret;
 }
 
 static void destroyInteger (r_type_ptr r, type_info* ti) {
-    free(*r);
-    free(r);
+    sfree(*r);
+    sfree(r);
 }
 
 static type_info* newInteger() {
-    type_info* pc = calloc(1, sizeof(type_info));
+    type_info* pc = scalloc(1, sizeof(type_info));
     pc->create = createInteger;
     pc->destroy = destroyInteger;
     return pc;
 }
 
 static r_type_ptr Is_Zero(r_type_ptr i, Integer_Template* this) {
-	int *space = calloc(1, sizeof(int));
+	int *space = scalloc(1, sizeof(int));
 	*space = (**(int**)i == 0);
 
-	int** ret = malloc(sizeof(int*));
+	int** ret = salloc(sizeof(int*));
 	*ret = space;
 	return (r_type_ptr)ret;
 }
 
 static r_type_ptr Is_Not_Zero(r_type_ptr i, Integer_Template* this) {
-	int *space = calloc(1, sizeof(int));
+	int *space = scalloc(1, sizeof(int));
 	*space = (**(int**)i != 0);
 
-	int** ret = malloc(sizeof(int*));
+	int** ret = salloc(sizeof(int*));
 	*ret = space;
 	return (r_type_ptr)ret;
 }
@@ -60,91 +64,91 @@ static void Decrement(r_type_ptr i, Integer_Template* this) {
 }
 
[…]

### 2014-04-20 RESOLVE-Workspace/RESOLVE/Main/Facilities/General_Examples/Int_Do_Nothing_Exercise.c

@@ -20,7 +20,12 @@ void Do_Nothing(r_type_ptr I) {
 
 void Main() {
 	r_type_ptr X = Std_Integer_Fac_Var.core->Integer->create(Std_Integer_Fac_Var.core->Integer);
-
+	X = Std_Integer_Fac_Var.core->createFromInteger(0x01, Std_Integer_Fac_Var.core->Integer);
+	Std_Integer_Fac_Var.core->Write_Line(X, Std_Integer_Fac_Var.core);
+    Std_Integer_Fac_Var.core->Integer->destroy(X, Std_Integer_Fac_Var.core->Integer);
+    Std_Integer_Fac_Var.core->Write_Line(X, Std_Integer_Fac_Var.core);
+    printf("Done Running\n");
+	
 }
 
 int main() {

### 2014-04-20 RESOLVE-Workspace/RESOLVE/Main/Facilities/General_Examples/Int_Do_Nothing_Exercise.h

@@ -6,8 +6,8 @@
 #define __INT_DO_NOTHING_EXERCISE_H
 
 #include "../../../RESOLVE.h"
-#include "../../../Main/Concepts/Standard/Static_Array_Template/Static_Array_Template.h"
-#include "../../../Main/Concepts/Standard/Location_Linking_Template_1/Location_Linking_Template_1.h"
+//#include "../../../Main/Concepts/Standard/Static_Array_Template/Static_Array_Template.h"
+//#include "../../../Main/Concepts/Standard/Location_Linking_Template_1/Location_Linking_Template_1.h"
 #include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
 #include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
 

### 2014-04-20 RESOLVE-Workspace/RESOLVE/Main/Facilities/General_Examples/naive_malloc.c

@@ -1,0 +1,193 @@
+#ifdef DEBUG
+#include <stdio.h>
+#endif
+
+#include "naive_malloc.h"
+
+#define MAX_MEM 1024
+#define align4(x) (((((x)-1)>>2)<<2)+4)
+
+static void *stack[MAX_MEM];
+static void *base = NULL;
+static void *cur_brk = (void*)&stack[0];
+
+typedef struct block_t *block;
+
+struct block_t
+{
+	size_t size;
+	block next;
+	block prev;
+	int free;
+	int pad;
+	void *ptr;
+	char data[1];
+};
+
+
+#define BLOCK_SIZE (sizeof(struct block_t)-sizeof(char*))
+
+block get_block(void *p);
+int valid_addr(void *p);
+block fusion(block b);
+
+void split_block(block b, size_t size) 
+{
+	block new_block;
+	new_block = (void*)b->data + size;
+	new_block->size = b->size - size - BLOCK_SIZE;
+	new_block->free = 1;
+	b->size = size;
+	b->next = new_block;	
+	new_block->next = b->next;
+	new_block->prev = b;
+	new_block->ptr = new_block->data;
+}
+
+block find_block(block *last, size_t size) 
+{
+	block b = base;
+	while(b && !(b->free && b->size >= size)) {
+		*last = b;
+		b = b->next;
+	}
+
+	return b;
+}
+
+void *stack_sbrk(int n)
+{
+	cur_brk += n;
+	if(cur_brk > (void*)&stack[MAX_MEM-1]) {
+		return (void*)-1;
+	}
+	return (void*)(cur_brk);		
+}
+
+void stack_brk(void *ptr)
+{
+	cur_brk = ptr;
+}
+
+block extend_stack(block last, size_t size)
+{
+	block b;
+	b = stack_sbrk(0);
+	if(stack_sbrk(BLOCK_SIZE + size) == (void*)-1) {
+		return NULL;
+	}
+	b->size = size;
+	b->next = NULL;
+	b->ptr = b->data;
+	if(last) {
+		last->next = b;
+		b->prev = last;
+	}
+	b->free = 0;
+	return b;
+}
+
+void *scalloc(int n, size_t size) {
+	size_t *new;
+	size_t s4, i;
+	new = salloc(n * size);
+	if(new) {
+		s4 = align4(n * size) << 2;
+		for(i = 0; i < s4; i++) {
+			new[i] = 0;
+		}
+	}
[…]

### 2014-04-20 RESOLVE-Workspace/RESOLVE/Main/Facilities/General_Examples/naive_malloc.h

@@ -1,0 +1,10 @@
+#ifndef __NAIVE_MALLOC_H__
+#define __NAIVE_MALLOC_H__
+
+#include <stdlib.h>
+
+void *salloc(size_t size);
+void *scalloc(int n, size_t size);
+void sfree(void *ptr);
+
+#endif

### 2014-04-20 RESOLVE-Workspace/RESOLVE/RESOLVE.h

@@ -5,6 +5,7 @@
 #include <string.h>
 #include <stdio.h>
 #include <stdarg.h>
+#include "naive_malloc.h"
 
 typedef void* rtype;
 typedef rtype* r_type_ptr;

### 2014-04-21 tech-project/paper.tex
paper changes

@@
 
+\begin{figure*}[!htb]
+\centering
+\includegraphics[scale=.45]{figs/implementation.pdf}
+\caption{RESOLVE module types and their corresponding C representation}
+\end{figure*}
+\label{fig:imp}
+
 \subsection{Verification}
@@
 Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
-
-\begin{figure}
-\centering
-\includegraphics[scale=.55]{figs/relationship.pdf}
-\caption{RESOLVE module types and their corresponding C representation}
-\end{figure}
-\label{fig:ast}
 
@@
 Many programs, however, require dynamic memory allocation to be used, including RESOLVE, in order to make it extensible.
-In this section we introduce a stack memory allocator.
+Previous RESOVE translations to C required static memory allocation \cite{regula:2010}.
+In this section a stack based dynamic memory allocator is introduced.
 
-\subsubsection{Allocation using salloc}
+\subsubsection{Allocation using \texttt{salloc}}
 
-The \texttt{salloc} is a first fit memory allocator that is provided memory of fixed size that is determined at compile time.
-It requires a small section of meta-data called a block which stores information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
-A sample representation of the stack as shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
+The \texttt{salloc()} is a first fit memory allocator.
+Rather than allocating on the heap, \texttt{salloc()} uses the stack.
+At compilation, the allocator provisions a fixed size of memory.
+It requires a small section of meta-data called a block which contains information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
+A sample representation of the stack shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
 
@@
 
-\subsubsection{Deallocation using sfree}
+\subsubsection{Deallocation using \texttt{sfree}}
 
-A memory allocator must provide a mechanism to release  or free memory in order to indicate that it is not being used and can be reallocated for something else.
-The \texttt{sfree} operation is an analogous implementation to the standard C \texttt{free} function for the stack.
+A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated for something else.
+The \texttt{sfree()} operation is an analogous implementation to the standard C \texttt{free()} function for the stack.
 
@@
 \centering
-\includegraphics[scale=.55]{figs/free.pdf}
+\includegraphics[scale=.55]{figs/sfree.pdf}
 \caption{sfree to free memory}
@@
 A common problem that can occur in memory allocation is fragmentation.
-As show in figure ??, fragmentation can lead to inefficient and increased memory usage.
+As shown in figure \ref{fig:fragmentation}, fragmentation can lead to inefficient and increased memory usage.
 This problem is magnified on embedded systems with limited memory capabilities.
 Simple optimizations can be made however to reduce fragmentation.
-Splitting is one optimization that \texttt{salloc} uses to maximize memory usage.
-Shown in figure \ref{fig:split}, previously allocated blocks that have been freed, can be split to the size that is required by a call to \texttt{salloc}.
-Another means of optimizing memory usage is fusing together freed blocks.
+Splitting is one optimization that \texttt{salloc()} to maximize memory usage.
+Shown in figure \ref{fig:split}, blocks can be split to the size that is required.
+Another means of optimizing memory usage is joining together freed blocks.
 When a call to \texttt{sfree()} is made, neighboring blocks are coalesced together, as shown in figure \ref{fig:fuse}.
@@
 \centering
+\includegraphics[scale=.55]{figs/fragmentation.pdf}
+\caption{fragmentation}
+\end{figure}
+\label{fig:fragmentation}
+
+\begin{figure}[!htb]
+\centering
 \includegraphics[scale=.55]{figs/split.pdf}
-\caption{block-splitting}
+\caption{block splitting}
 \end{figure}
@@
 \includegraphics[scale=.55]{figs/fuse.pdf}
-\caption{fusing blocks}
+\caption{block fusing}
 \end{figure}

### 2014-04-21 tech-project/paper.tex
paper updated

@@
 In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non-native RESOLVE) realizations.
-We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of two enhancements that we demonstrate running on a Telos mote.
+We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of a toggling capability enhancement that we demonstrate running on a Telos mote.
 \end{abstract}
@@
 The concept provides two operations.
-The first of the two, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion that:
-\begin{enumerate}
-\item The length of the outgoing strip \texttt{L}, is the same length as the incoming strip, \texttt{\#L} (where \texttt{\#} signifies its incoming state).
-\item The LED in position \texttt{i} of \texttt{L} is set to boolean parameter \texttt{b}. 
-\end{enumerate}
-Operation \texttt{Status}, which simply returns the state of the LED at position \texttt{i}, is specified similarly.
+The first operation, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
+The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion of the operation that the length of the outgoing strip \texttt{L} is the same length as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
+The \texttt{Status} operation is specified similarly.
 
@@
 RESOLVE also allows users to extend the functionality provided by the base concept through \textit{enhancements} -- a form of specification inheritance.
-The enhancement we provide here is  \texttt{Toggling\_Capability}, which gives users of the LED component the ability to toggle a specific LED on or off.
+The enhancement we provide here, \texttt{Toggling\_Capability}, allows users to flip a specific LED to its complement.
 
@@
 
-The specification of \texttt{Toggle} states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
+The enhancement adds a single operation, \texttt{Toggle}, which states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
 
@@
 
-Even realizations of enhancements are neutral since they are only permitted to call operations provided by the base concept -- thus requiring no knowledge of how the called operation is actually implemented.
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=.45]{figs/implementation.pdf}
-\caption{RESOLVE module types and their corresponding C representation}
-\end{figure*}
-\label{fig:imp}
+Even enhancement realizations are neutral since only the operations called are those provided by the base concept -- and thus require no knowledge of how the called operation is implemented.
 
@@
 
-In this section we verify our realization of \texttt{Toggling\_Capability}.
-The first step in this process is to generate verification conditions (VCs) for \texttt{Toggling\_Realiz}, which, if proven, will establish the correctness of that particular realization\footnote{Note: VCs themselves are typically generated from specific lines of a realization to ensure that the overall content of a realization is consistent with its specification.}.
+In this section we give a short overview of the verification results of \texttt{Toggling\_Realiz}.
+The first step in proving this particular realization correct is to generate verification conditions (VCs), which, if proven, will establish the correctness of this particular realization\footnote{Note: VCs themselves are typically generated from specific lines of a realization to ensure that the overall content of a realization is consistent with its specification.}.
 
@@
 	VC 0\_2	& 5039	& 5	& 0	\\
-	VC 0\_3	& 6324	& 5	& 0	\\
+	VC 0\_3	& 6324	& 6	& 0	\\
 	\bottomrule
 \end{tabular}
+\caption{Verification results for \texttt{Toggle} (left)}
+\label{fig:results}
 \end{figure}
@@
 The results of verification are summarized Figure \ref{fig:results}.
-As shown, the correctness of \texttt{Toggle} is straightforward enough for the prover to establish automatically, however \texttt{Set\_First\_And\_Last}'s VC 0\_5 failed to be dispatched.
-
-\begin{figure}[!htb]
-\begin{verbatim}
-Goal:
-Element_At((|L'|  - |L'|), L') = b
-
-Given:
-    ...
-1. |L| = Strip_Length and
-2. |L|  > 1 and
-3. |L''| = |L| and
-4. Element_At(0, L'') = b
-5. |L'| = |L''| and
-6. Element_At((|L''|  - 1), L') = b)
-\end{verbatim}
-\caption{A problematic VC}
-\label{fig:problematicVC}
-\end{figure}
-
-A cursory examination of the unproven VC, shown in Figure \ref{fig:problematicVC}, reveals that prover was not able to employ the seemingly relevant \texttt{given \#4} since \texttt{L"}, could not be considered (rightfully so) the same as \texttt{L'} due to the changing boolean value.
-There are several means of correcting this: The first involves amending the \texttt{ensures} clause of operation \texttt{Set} (which is used in \texttt{Set First And Last}) to intuitively say that ``the content of \textit{outgoing} \texttt{L} is equivalent to the that of the incoming \texttt{L} with the exception of position \texttt{i}.
-The second route -- perhaps the less preferable of the two -- involves adding new theorems to \texttt{String\_Theory} which state this.
-
-FIGURE OUT AN ELEGANT WAY TO CONCLUDE THIS SECTION...
+Using the RESOLVE compiler's integrated prover, we are able to mechanically and automatically dispatch all VCs generated by operation \texttt{Toggle}, thus verifying its correctness.
+In terms of proof difficulty, given the number of steps and time taken to establish each, leads us to conclude that the VCs generated were of a straightforward variety.
+Though readers interested in a more detailed discussion of how exactly the prover goes about transforming and dispatching VCs are encouraged to refer to \cite{smith:2013}.
 
@@
 \label{sec:facilities}
-The most straightforward means of utilizing our previously defined Led strip component and its verified enhancements is a via \textit{facility} module. Figure \# depicts a simple
+
+With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now present a sample embedded application that iteratively toggles all lights in a single strip.
+
+Shown below is a RESOLVE facility module that implements the client logic 
+\begin{verbatim}
+Facility LED_Telos_Demo;
+    uses Std_Clock_Fac;
+
+    Facility Leds_Fac is LED_Template(3)
+        externally realized by Std_Led_Realiz
+     enhanced by Toggling_Capability
+        realized by Toggling_Realiz;
+
+    Operation Main(); Procedure
+        Var I1, I2, I3 : Integer;
+        Var Loop : Boolean;
+        Var L : Led;
+
+        I1 := 1; I2 := 2; I3 := 3;
+
+        Loop := True();
+        While(Loop)
+            changing Loop;
+            maintaining ...
+        do
+            Leds_Fac.Toggle(L, I1);
+            Std_Clock_Fac.Wait_500_Milli_Seconds();
+
+            Leds_Fac.Toggle(L, I2);
+            Std_Clock_Fac.Wait_500_Milli_Seconds();
+
+            Leds_Fac.Toggle(L, I3);
+            Std_Clock_Fac.Wait_500_Milli_Seconds();
+        end;
+    end Main;
+
+end LED_Telos_Demo;
+\end{verbatim}
+
+Prior to manipulating the LED component developed in the previous sections, we must first pair its specification with a realization. This is accomplished via a facility declaration:
 
 %mention performance stuff in future work section.
+
+\begin{figure*}[!htb]
+\centering
+\includegraphics[scale=.45]{figs/implementation.pdf}
+\caption{RESOLVE module types and their corresponding C representation}
+\end{figure*}
+\label{fig:imp}
 

### 2014-04-21 tech-project/paper.tex
adding information on our new shiny external syntax. I love the smell of new syntax in the morning

@@
 In this paper we present a flexible means of specifying and verifying the correctness of software for embedded network systems.
-Our approach uses RESOLVE, an imperative, component based programming and mathematical specification language, to verify the functional correctness of TinyOS applications.
+Our approach uses RESOLVE, an imperative, component based programming and mathematical specification language, to verify the functional correctness of embedded applications.
 In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non-native RESOLVE) realizations.
@@
 \subsection{Concepts}
-
+\label{ssec:concepts}
 A \textit{concept} module in RESOLVE defines a specification for a mathematical, abstract type.
@@
 \item This approach demonstrates the benefits of reusable mathematical theories.
-The specifications here are based solely in \texttt{String\_Theory}, a pre-existing RESOLVE math library that provides all the definitions and theorems used in this specification.
+The specifications listed here are rooted in \texttt{String\_Theory}, a pre-existing RESOLVE math library that provides most of the definitions and theorems used throughout the specifications.
 \end{itemize}
 
-The concept provides two operations.
-The first operation, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion of the operation that the length of the outgoing strip \texttt{L} is the same length as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
+Finally, the concept provides two operations.
+The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
+The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion that the length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
 The \texttt{Status} operation is specified similarly.
@@
 Thus, the \texttt{L} parameter of operation \texttt{Status} is referring to the mathematical value of an \texttt{LED}, as opposed to a programmatic one (typically defined in a realization).
-
-%\subsection{An External LED Realization}
-
-%Armed with a specification, the RESOLVE programmer would now ideally provide a verifiable implementation of \texttt{LEDs\_Template} via a RESOLVE realization.
-However, as our target platform is embedded, and our concept  aims to provide control for LEDs -- a decidedly low level feature -- our realization is forced to operate at similarly low levels by manually interfacing with hardware pins provided by msp430 chipset.
-RESOLVE, however in its current state is far too high level of a language to perform these tasks directly -- that is, it currently lacks driver support to do so.
-To address this difficulty, we introduce language support for \textit{external realizations}, which, in essence, leaves the user free to write their own realization of a concept in whatever language is most convenient.
-In the case of \texttt{LEDs\_Template}, we provide a hand written \texttt{Telos\_LEDs\_Realiz} C realization that matches as closely as possible the model of translation detailed in Section \#.
-
-%More than givingHaving the freedom to use RESOLVE's specificational capabilities
 
@@
 
-Even enhancement realizations are neutral since only the operations called are those provided by the base concept -- and thus require no knowledge of how the called operation is implemented.
+Even enhancement realizations are neutral since only the operations called are those provided by the base concept -- and require no knowledge of how the called operation is implemented.
 
@@
 \end{tabular}
-\caption{Verification results for \texttt{Toggle} (left)}
+\caption{Verification results for operation \texttt{Toggle}}
 \label{fig:results}
@@
 
-The results of verification are summarized Figure \ref{fig:results}.
-Using the RESOLVE compiler's integrated prover, we are able to mechanically and automatically dispatch all VCs generated by operation \texttt{Toggle}, thus verifying its correctness.
-In terms of proof difficulty, given the number of steps and time taken to establish each, leads us to conclude that the VCs generated were of a straightforward variety.
-Though readers interested in a more detailed discussion of how exactly the prover goes about transforming and dispatching VCs are encouraged to refer to \cite{smith:2013}.
+As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness.
+In terms of proof difficulty, given the number of steps and time taken to establish each, we may conclude that the VCs generated were of a straightforward variety.
+Readers interested however in learning more about how the prover goes about transforming and dispatching similar (and other, more complex) VCs should refer to \cite{smith:2013}.
 
@@
 
-Shown below is a RESOLVE facility module that implements the client logic 
+Shown below is a RESOLVE facility module that implements the client logic of our embedded application.
 \begin{verbatim}
@@
     Operation Main(); Procedure
+
+        (* Declare LED strip indices *)
         Var I1, I2, I3 : Integer;
         Var Loop : Boolean;
+
+        (* Declare an LED strip *)
         Var L : Led;
@@
 
-Prior to manipulating the LED component developed in the previous sections, we must first pair its specification with a realization. This is accomplished via a facility declaration:
+Prior to using the LED component developed in the previous sections, we must first pair our \texttt{LED\_Template} specification with an appropriate realization.
+This is accomplished via the facility declaration located directly beneath the uses clause which pairs our LED specification, \texttt{LED\_Template}, with a ``\texttt{Std\_Led\_Realiz}" realization.
+In order to give LED strip instances the ability to toggle specific LEDs, we also similarly pair the specification, \texttt{Toggling\_Capability} with our \texttt{Toggling\_Realiz} realization.
+
+The bulk of logic driving the actual application rests in the non terminating busy loop inside operation \texttt{Main}, where we use the operation provided by \texttt{Toggling\_Capability} to turn each light on the strip on then off in succession.
+
+\subsubsection{``External'' Realization Support}
+\label{ssec:external}
+
+Readers might note that we never presented a realization of \texttt{LED\_Template}.
+Indeed, the RESOLVE programmer would ideally, after writing the concept, provide a verifiable native RESOLVE implementation.
+However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by manually interfacing with hardware pins provided by msp430 chipset.
+
+RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- that is, it currently lacks the driver support to do so.
+In an effort to address this difficulty, we introduce the notion of \textit{external realizations}, which allows the user to write their own realization of a concept in a language of their choosing.
+In the case of \texttt{LED\_Template}, we chose to provide a hand written \texttt{Std\_Leds\_Realiz} C realization that matches as closely as possible the conventions and model of translation later detailed in Section \#.
+An example above shows how users communicate to the compiler that a realization is external.
+
+% Applies to base types in resolve as well
+
+% Similar to NesC, the towers of abstraction idea...
+
+We feel this addition to the language is appropriate and useful for the following reasons:
+
+%More than givingHaving the freedom to use RESOLVE's specificational capabilities
 

### 2014-04-22 tech-project/paper.tex
working some more on externally -gents.

@@
 
-With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now present a sample embedded application that iteratively toggles all lights in a single strip.
+With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now present a demo embedded application that iteratively toggles all lights in a single strip.
 
-Shown below is a RESOLVE facility module that implements the client logic of our embedded application.
+Shown below is a RESOLVE facility module that implements the client logic of our small embedded application.
 \begin{verbatim}
@@
 \end{verbatim}
+%smaller file sizes
+%reusable code
+%only have to translate a file once
+% be able to say that the code we have is the code that was verified.
+% our approach takes less ROM. Its not less efficient, it is differently efficient.
+Prior to using the LED component developed in the previous sections, we first must associate our \texttt{LED\_Template} specification with an appropriate realization.
+This is accomplished via the facility declaration located directly beneath the uses clause, which pairs \texttt{LED\_Template}, with a ``\texttt{Std\_Led\_Realiz}" realization.
+The ability to toggle lights is added to this facility in a similar fashion.
 
-Prior to using the LED component developed in the previous sections, we must first pair our \texttt{LED\_Template} specification with an appropriate realization.
-This is accomplished via the facility declaration located directly beneath the uses clause which pairs our LED specification, \texttt{LED\_Template}, with a ``\texttt{Std\_Led\_Realiz}" realization.
-In order to give LED strip instances the ability to toggle specific LEDs, we also similarly pair the specification, \texttt{Toggling\_Capability} with our \texttt{Toggling\_Realiz} realization.
+The bulk of the logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use the \texttt{Toggle} operation -- provided by our formally verified \texttt{Toggling\_Capability} enhancement -- to successively turn each light within the strip on then off.
 
-The bulk of logic driving the actual application rests in the non terminating busy loop inside operation \texttt{Main}, where we use the operation provided by \texttt{Toggling\_Capability} to turn each light on the strip on then off in succession.
-
-\subsubsection{``External'' Realization Support}
+\subsection{``External'' Realization Support}
 \label{ssec:external}
@@
 
-RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- that is, it currently lacks the driver support to do so.
-In an effort to address this difficulty, we introduce the notion of \textit{external realizations}, which allows the user to write their own realization of a concept in a language of their choosing.
-In the case of \texttt{LED\_Template}, we chose to provide a hand written \texttt{Std\_Leds\_Realiz} C realization that matches as closely as possible the conventions and model of translation later detailed in Section \#.
-An example above shows how users communicate to the compiler that a realization is external.
+RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- as it lacks the appropriate driver support to do so.
+In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
+In the case of \texttt{LED\_Template}, we chose to provide a hand written \texttt{Std\_Leds\_Realiz} C realization, that matches as closely as possible the conventions and model of translation later detailed in Section \#.
+
+The \texttt{LED\_Telos\_Demo} facility above demonstrates this through the \texttt{externally realized by} phrase.
+This phrase signals to the RESOLVE compiler that the user is providing a non-native realization, with the expectation that this external realization conforms to the specifications dictated in the concept.
 
@@
 % Similar to NesC, the towers of abstraction idea...
+eventually, similar to nesc, we get enough abstraction  through machinery such as enhancements, etc to with pieces built on top of these externally realized components.
+
+% gives flexibility to those wishing to write other drivers and new
 
@@
 In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
+
+Resolve is not just concerned with functional correctness, but also considers as a part of overall program correctness performance and space considerations -- and has mechanisms in the language to formally specify these as well.
+By having a dynamic memory allocation component, we allow our translated code to not have to make special considerations for a hidden steps in compilation that does static allocation.
+Instead
 

### 2014-04-22 tech-project/paper.tex
updated paper

--- 2014-04-21 tech-project/paper.tex
@@
 In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
+Another such consideration includes memory, and decisions on dynamic or static allocation.
+RESOLVE does not currently provide specifications towards a memory model but is in aspirations of providing a dynamically allocatable system.
+Following suit, we will introduce a stack based memory allocator in section \#.
 
 The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
+Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
+Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
+Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
+RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
 
-Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
+%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
 

### 2014-04-22 tech-project/paper.tex
finished my initial work on externally

--- 2014-04-22 tech-project/paper.tex
@@
 \item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
-This ideal in a setting where various driver applications are varied and new contexts might require creating new theory constituents appropriate for specific drivers.
-% reword this to be less vague.
+This is ideal in a setting where drivers might encompass a wide spectrum possible applications, where each might require unique, new mathematical developments.% reword this to be less vague.
 
@@
 
-In RESOLVE, programs are composed of several different modules that range from interfaces and realizations, to client (facility) modules.
 In this section, we provide mathematical and programmatic elements of an LED strip component to give readers both a concrete look at the language, and introduce some new features aimed at making it more amenable to the development of embedded applications.
@@
 \label{ssec:concepts}
+In RESOLVE, programs are composed of several different modules that range from interfaces and realizations, to client (facility) modules.
 A \textit{concept} module in RESOLVE defines a specification for a mathematical, abstract type.
@@
 
-It's worth noting that unlike the \texttt{LED\_Template} presented in \cite{regula:2010} which models an LED as the \textit{cartesian product} of booleans $b_1$, $b_2$, \ldots , $b_4$, the strip model we present here instead uses strings for the following reasons:
+It's worth noting that unlike the \texttt{LED\_Template} presented in \cite{regula:2010} which models an LED as the \textit{cartesian product} of booleans $b_0$, $b_1$, \ldots , $b_4$, the strip model we present here instead uses strings for the following reasons:
 \begin{itemize}
@@
 \item This approach demonstrates the benefits of reusable mathematical theories.
-The specifications listed here are rooted in \texttt{String\_Theory}, a pre-existing RESOLVE math library that provides most of the definitions and theorems used throughout the specifications.
+The specifications listed here are based (almost) entirely in \texttt{String\_Theory} and are therefore able to make use of RESOLVE's pre-existing math libraries.
 \end{itemize}
@@
 The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion that the length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
+The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion that: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
 The \texttt{Status} operation is specified similarly.
@@
 
-The enhancement adds a single operation, \texttt{Toggle}, which states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
+The enhancement specifies a single operation, \texttt{Toggle}, which states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
 
@@
 
-Even enhancement realizations are neutral since only the operations called are those provided by the base concept -- and require no knowledge of how the called operation is implemented.
+Enhancement realizations are neutral as well since any method called within the context of an enhancement realization refers to the operation specified in the concept -- meaning no knowledge of implementation details is required.
 
@@
 As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness.
-In terms of proof difficulty, given the number of steps and time taken to establish each, we may conclude that the VCs generated were of a straightforward variety.
+In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety.
 Readers interested however in learning more about how the prover goes about transforming and dispatching similar (and other, more complex) VCs should refer to \cite{smith:2013}.
@@
 
-With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now present a demo embedded application that iteratively toggles all lights in a single strip.
+With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now turn to a small embedded application that combines these elements to iteratively toggle the lights within an LED strip.
 
-Shown below is a RESOLVE facility module that implements the client logic of our small embedded application.
+Shown below is a RESOLVE facility module that implements the client logic of this embedded application.
 \begin{verbatim}
@@
 Prior to using the LED component developed in the previous sections, we first must associate our \texttt{LED\_Template} specification with an appropriate realization.
-This is accomplished via the facility declaration located directly beneath the uses clause, which pairs \texttt{LED\_Template}, with a ``\texttt{Std\_Led\_Realiz}" realization.
-The ability to toggle lights is added to this facility in a similar fashion.
+This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
+Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
 
-The bulk of the logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use the \texttt{Toggle} operation -- provided by our formally verified \texttt{Toggling\_Capability} enhancement -- to successively turn each light within the strip on then off.
+The bulk of the logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
 
@@
 Readers might note that we never presented a realization of \texttt{LED\_Template}.
-Indeed, the RESOLVE programmer would ideally, after writing the concept, provide a verifiable native RESOLVE implementation.
-However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by manually interfacing with hardware pins provided by msp430 chipset.
+Indeed, after having written the concept, the RESOLVE programmer would ideally provide it with a verifiable, native RESOLVE implementation.
+However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by directly manipulating hardware pins provided by msp430's chipset.
 
-RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- as it lacks the appropriate driver support to do so.
+RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
 In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
@@
 
-The \texttt{LED\_Telos\_Demo} facility above demonstrates this through the \texttt{externally realized by} phrase.
-This phrase signals to the RESOLVE compiler that the user is providing a non-native realization, with the expectation that this external realization conforms to the specifications dictated in the concept.
+The \texttt{LED\_Telos\_Demo} facility showcased above demonstrates this through its use of the ``\texttt{externally realized}" phrase.
+This signals to the RESOLVE compiler that the user is providing a non-native realization, with the expectation that it conforms to the specifications dictated in the concept.
 
@@
 
-We feel this addition to the language is appropriate and useful for the following reasons:
+We feel this new keyword is useful for the following reasons:
+\begin{itemize}
+\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code.
+The keyword now transparently indicates this.
+\item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
+\end{itemize}
+
+In the context of embedded systems especially, we feel these developments will allow users to flexibly and transparently specify all low level components of the sort required in most embedded applications (e.g.
+LED strip drivers).
+It is our intent that new (native) resolve components are layered on top of these low level drivers to provide a system (not unlike NesC) that deals with verified component graphs of ..
+
+%In a very real sense, gives the language the capability of specifying its foundational components flexibly, and transparently which can later have all native RESOLVE components added on top.
 
@@
 \label{fig:fuse}
+
+\section{Conclusion}
+In this paper we presented a formally specified driver component in RESOLVE, and a single verified enhancement on this component.
+We introduced a new keyword that allows users to specify in a flexible and transparent fashion the foundational components of the language over which native RESOLVE realizations may be layered.
+We presented a revised model of RESOLVE to C code and a dynamic allocation scheme that accompanies this new model.
 %A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.

### 2014-04-22 tech-project/paper.tex
paper changes

@@
 In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
-
-Resolve is not just concerned with functional correctness, but also considers as a part of overall program correctness performance and space considerations -- and has mechanisms in the language to formally specify these as well.
-By having a dynamic memory allocation component, we allow our translated code to not have to make special considerations for a hidden steps in compilation that does static allocation.
-Instead
+Another such consideration includes memory, and decisions on dynamic or static allocation.
+RESOLVE does not currently provide specifications towards a memory model but is in aspirations of providing a dynamically allocatable system.
+Following suit, we will introduce a stack based memory allocator in section \#.
 
 The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
+Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
+Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
+Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
+RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
 
-Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
+%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
 
@@
 \label{fig:fuse}
-
-\section{Conclusion}
-In this paper we presented a formally specified driver component in RESOLVE, and a single verified enhancement on this component.
-We introduced a new keyword that allows users to specify in a flexible and transparent fashion the foundational components of the language over which native RESOLVE realizations may be layered.
-We presented a revised model of RESOLVE to C code and a dynamic allocation scheme that accompanies this new model.
 %A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.

### 2014-04-22 tech-project/paper.tex
refined some of the previous sections -- wording, etc

@@
 \item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
-This is ideal in a setting where drivers might encompass a wide spectrum possible applications, where each might require unique, new mathematical developments.% reword this to be less vague.
+This is ideal in a setting where drivers might encompass a wide spectrum possible applications wherein the need for new mathematical developments may arise.% reword this to be less vague.
 
@@
 The paper is organized as follows: First, we open with a brief overview of the Telos mote platform.
-Next, we present revised specifications of an LED driver component with a formally verified enhancement.
+Next, we present revised specifications of an LED driver component that is accompanied by a small enhancement.
 This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used.
 The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code.
-We conclude with suggestions for tool improvements, as well as a review of some longer term research goals.
+We conclude with a review of related works and suggestions for future research and tool improvements.
 
@@
 Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory.
-A cc2420 radio stack provides the mote with broadcast and receiving capabilities, while optional sensing capabilities may be added in the form of light, humidity, and temperature sensors.
+A cc2420 radio stack provides broadcast and receiving capabilities, while optional sensing capabilities may be added to the mote in the form of light, humidity, and temperature sensors.
 The mote also contains three onboard LEDs: One blue, one red, and one green.
@@
 The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion that: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
+The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} two things upon completion: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
 The \texttt{Status} operation is specified similarly.
@@
 
-In this section we give a short overview of the verification results of \texttt{Toggling\_Realiz}.
-The first step in proving this particular realization correct is to generate verification conditions (VCs), which, if proven, will establish the correctness of this particular realization\footnote{Note: VCs themselves are typically generated from specific lines of a realization to ensure that the overall content of a realization is consistent with its specification.}.
+We now turn to the task of verifying our small toggling enhancement.
+The first step in doing so is to generate Verification Conditions (VCs) for \texttt{Toggle\_Realiz}, which, if proven, will establish the correctness of this particular implementation of \texttt{Toggling\_Capability}.
+One thing to note about the VCs themselves is that they are generated from specific lines of a realization, and exist to ensure that the content of the realization is consistent with its specification: This entails checking for things such as array access boundary violations, etc.
 
@@
 In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety.
-Readers interested however in learning more about how the prover goes about transforming and dispatching similar (and other, more complex) VCs should refer to \cite{smith:2013}.
+Readers interested however in learning more about the steps and specific actions the prover takes in transforming givens and dispatching similar (and more complex) VCs should refer to \cite{smith:2013}.
 
@@
 Facility LED_Telos_Demo;
-    uses Std_Clock_Fac;
+    uses Std_Clock_Fac, Std_Boolean_Fac, 
+            Std_Integer_Fac;
 
@@
 % our approach takes less ROM. Its not less efficient, it is differently efficient.
-Prior to using the LED component developed in the previous sections, we first must associate our \texttt{LED\_Template} specification with an appropriate realization.
+Prior to using the LED component developed in the previous sections, we first must bind our \texttt{LED\_Template} specification with an appropriate realization.
 This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
@@
 
-RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
+RESOLVE, however, in its current state is too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
 In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
@@
 \item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code.
-The keyword now transparently indicates this.
+The ``externally" keyword now transparently indicates this.
 \item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
@@
 
-In the context of embedded systems especially, we feel these developments will allow users to flexibly and transparently specify all low level components of the sort required in most embedded applications (e.g.
+In the context of embedded systems especially, we feel these developments allow flexibility and transparency in the way users specify low level components of the sort required in most embedded applications (e.g.
 LED strip drivers).
-It is our intent that new (native) resolve components are layered on top of these low level drivers to provide a system (not unlike NesC) that deals with verified component graphs of ..
+It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually building up to a system (not unlike NesC) that deals exclusively in verified, native RESOLVE components.
 
@@
 \section{Implementation}
-Development of the tool presented here can be logically partitioned into three distinct phases: 
+Development of our C translation tool can be logically partitioned into three distinct pieces: 
 \begin{enumerate}
@@
 \end{enumerate}
-In this section we discuss each of these phases, concluding with a demo illustrating each working in tandem to realize the example presented in section \ref{sec:specifiying}.
+In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.
 

### 2014-04-22 tech-project/paper.tex
updating C Translation Model.

--- 2014-04-22 tech-project/paper.tex
@@
 In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
-Another such consideration includes memory, and decisions on dynamic or static allocation.
-RESOLVE does not currently provide specifications towards a memory model but is in aspirations of providing a dynamically allocatable system.
-Following suit, we will introduce a stack based memory allocator in section \#.
+
+The memory model must also be considered as an additional verifiable component.
+Currently, RESOLVE is not capable of creating a complete specification of memory\footnote{RESOLVE is an object based language and has variable sized structures.
+Using dynamically allocatable memory is the favored approach to allow arbitrarily sized data.}.
+Thus, a memory model must be realized without a specification.
+To provide a straight forward translation from RESOLVE to C, we provide a dynamically-based memory allocator for use on embedded systems.
 

### 2014-04-25 tech-project/paper.tex
changes

--- 2014-04-22 tech-project/paper.tex
@@
 We now turn to the task of verifying our small toggling enhancement.
-The first step in doing so is to generate Verification Conditions (VCs) for \texttt{Toggle\_Realiz}, which, if proven, will establish the correctness of this particular implementation of \texttt{Toggling\_Capability}.
+The first step in doing so is to generate Verification Conditions (VCs) for \texttt{Toggle\_Realiz}, which, if proven, will establish the correctness of this particular implementation.
 One thing to note about the VCs themselves is that they are generated from specific lines of a realization, and exist to ensure that the content of the realization is consistent with its specification: This entails checking for things such as array access boundary violations, etc.
@@
 Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
-
-The bulk of the logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
+The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
 
@@
 \label{ssec:external}
+
+\begin{figure*}[!htb]
+\centering
+\includegraphics[scale=.55]{figs/component_graph.pdf}
+\caption{A diagram illustrating inter-component relationships for the example in Section \ref{sec:specifying}}
+\end{figure*}
+\label{fig:imp}
 
@@
 In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
-In the case of \texttt{LED\_Template}, we chose to provide a hand written \texttt{Std\_Leds\_Realiz} C realization, that matches as closely as possible the conventions and model of translation later detailed in Section \#.
 
-The \texttt{LED\_Telos\_Demo} facility showcased above demonstrates this through its use of the ``\texttt{externally realized}" phrase.
-This signals to the RESOLVE compiler that the user is providing a non-native realization, with the expectation that it conforms to the specifications dictated in the concept.
+The \texttt{LED\_Telos\_Demo} facility above demonstrates these developments through its use of the ``\texttt{externally realized}" phrase.
+This signals to the RESOLVE compiler that the user is providing a non-native realization of the \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.
 
@@
 
-We feel this new keyword is useful for the following reasons:
+We feel this new keyword is beneficial for the following reasons:
 \begin{itemize}
@@
 
-In the context of embedded systems especially, we feel these developments allow flexibility and transparency in the way users specify low level components of the sort required in most embedded applications (e.g.
-LED strip drivers).
-It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually building up to a system (not unlike NesC) that deals exclusively in verified, native RESOLVE components.
+In the terms of embedded systems, these developments are especially as it allows us to write custom low level of the sort required for most embedded applications (e.g.
+LED strip drivers) while still providing formally specified interfaces that might later form the foundation .
+It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstract where we can concern ourselves exclusively with verified, native RESOLVE components.
 
@@
 %mention performance stuff in future work section.
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=.45]{figs/implementation.pdf}
-\caption{RESOLVE module types and their corresponding C representation}
-\end{figure*}
-\label{fig:imp}
 

### 2014-04-25 tech-project/implementation.tex
changes to paper

--- 2014-04-22 tech-project/paper.tex
@@
-% CpSc 855 - Final paper
-% Takumi Bolte & Dan Welch - Spring 2014.
-\documentclass{sig-alternate}
-
-\usepackage{mathrsfs}
-\usepackage{booktabs}
-\usepackage{placeins}
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{listings}
-\begin{document}
-\conferenceinfo{Clemson 2014}{7th Clemson University Mini-Conference on Embedded Network Systems}
-\title{An Extensible Approach to Verification of Embedded Network Systems*}
-
-%Re-evaluating Verification of Embedded Network Systems:
-%An Extensible Approach to Verification of Embedded Network Systems*}
-\numberofauthors{2}
-\author{
-\alignauthor
-%author
-Daniel Welch\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{dtwelch\}@clemson.edu}}}
-%author
-\alignauthor
-Takumi Bolte\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{tbolte\}@clemson.edu}}}
-}
-
-\maketitle
-\begin{abstract}
-
-In this paper we present a flexible means of specifying and verifying the correctness of software for embedded network systems.
-Our approach uses RESOLVE, an imperative, component based programming and mathematical specification language, to verify the functional correctness of embedded applications.
-In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non-native RESOLVE) realizations.
-We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of a toggling capability enhancement that we demonstrate running on a Telos mote.
-\end{abstract}
-
-\category{D.2.8}{Software Engineering and Data Communication}{Verification}[VCs, automated proving, modular software]
-\terms{Reliability, Verification, Languages, Networks}
-\keywords{automation, components, formal methods, specification, verifying compiler, embedded networks, wireless sensing}
-
-\section{Introduction}
-\label{sec:intro}
-Within little more than a decade, the area of embedded network systems and wireless sensing has exploded in popularity within industry and academia alike.
-Tempering however this extremely quick rise in popularity is the inherent difficulties in developing applications that function as intended in low power, event-driven environments.
-In response to these difficulties, a variety of tools and languages have been put forth  to help ease the burden on developers.
-On one end of this effort are languages such as NesC, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
-The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Arora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
-Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed in the field.
-
-We approach this problem by using RESOLVE (Reusable SOftware Language with VErification) as means of authoring, specifying, and ultimately verifying code for embedded network systems.
-Our decision to use RESOLVE as a language frontend -- as opposed to verifying C code directly -- ultimately stems from a verification amenability standpoint: Not only does RESOLVE prohibit verification crippling operations such as uncontrolled referencing and aliasing (prevalent in C and many other current languages)\cite{kulczycki:2004}, but also embodies a number of other characteristics ideal for embedded platforms including:
-
-\begin{itemize}
-\item \textbf{Modularity} RESOLVE enforces a strict separation of concerns between module specifications and client implementations.
-As a result, for any one particular specification, there can be any number of interchangeable implementations.
-This separation is ideal considering that many embedded applications happen to fit this pattern nicely: Various drivers oftentimes provide a common set of functionality, but in general have many distinct implementations that vary arbitrarily from platform to platform, vendor to vendor.
-
-\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
-This is ideal in a setting where drivers might encompass a wide spectrum possible applications, where each might require unique, new mathematical developments.% reword this to be less vague.
-
-\end{itemize}
-
-The paper is organized as follows: First, we open with a brief overview of the Telos mote platform.
-Next, we present revised specifications of an LED driver component with a formally verified enhancement.
-This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used.
-The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code.
-We conclude with suggestions for tool improvements, as well as a review of some longer term research goals.
-
-\section{The Telos Platform}
-
-The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley.
-Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory.
-A cc2420 radio stack provides the mote with broadcast and receiving capabilities, while optional sensing capabilities may be added in the form of light, humidity, and temperature sensors.
-The mote also contains three onboard LEDs: One blue, one red, and one green.
-
-%Additionally, the Telos board contains a total of three LEDs -- one red, one green, and one blue.
-\section{Specifiying LED behavior in Resolve}
-\label{sec:specifiying}
-
-In this section, we provide mathematical and programmatic elements of an LED strip component to give readers both a concrete look at the language, and introduce some new features aimed at making it more amenable to the development of embedded applications.
-Note that while we provide the level of detail necessary to understand the current example, readers interested in gaining a more complete, in depth knowledge of the language are encouraged to refer to \cite{sitaraman:2011, kulczycki:2008}.
-
-\subsection{Concepts}
-\label{ssec:concepts}
-In RESOLVE, programs are composed of several different modules that range from interfaces and realizations, to client (facility) modules.
-A \textit{concept} module in RESOLVE defines a specification for a mathematical, abstract type.
-Similar to an interface in Java, a concept provides a number of operation signatures that implementors are expected to realize.
-Shown below is a \texttt{LED\_Template} concept that provides a light strip abstraction.
-
-\begin{verbatim}
-Concept LED_Template(eval Strip_Length: Integer);
-    uses Boolean_Theory, String_Theory;
-    requires 0 < Strip_Length <= 4;
-
-    Type Family LED is modeled by Str(B);
-        exemplar L;
-        constraint |L| = Strip_Length;
-        initialization ensures 
-            ...
-
-    Oper Set(updates L : LED; eval b : Boolean; 
-                             eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures |L| = |#L| and 
-                   Element_At(i, L) = b;
-
-    Oper Status(preserves L : LED; 
-                   eval i : Integer) : Boolean;
-        requires 0 <= i < |L|;
-        ensures Status = Element_At(i, L);
-
-end LEDs_Template;
-\end{verbatim}
-
-We model our conceptual LED strip using a mathematical string (finite sequence) of booleans, denoted \texttt{Str(B)}, where each boolean within the string indicates the status of that particular LED: On (true) or off (false).
-The \texttt{exemplar} clause located immediately below provides a handle to this abstract model, and is used throughout the remainder of the specification.
-
-%The \texttt{Type Family} clause introduces an abstract type for the LED strip which we mathematically model using strings of booleans, denoted \texttt{Str(B)}, while the \texttt{exemplar} declared immediately after provides a handle to this type family.
-Use of the \texttt{exemplar} can be observed in the \texttt{constraint} clause, where it is used to assert that length of the strip is fixed to be whatever the user has specified via the \texttt{Strip\_Length} parameter.
-Finally, the \texttt{initialization} \texttt{ensures} clause makes explicit the state of the structure at the time it is initialized.
-We omit this verification specific clause, as it has little bearing on verification due to the fact that the realization we provide is \textit{externally} realized -- a point discussed in the next section\footnote{This clause, if it were provided, would need to communicate the following: ``For each position $i$ within the strip, the LED (or, value) at position $i$ is initially false."}
-
-It's worth noting that unlike the \texttt{LED\_Template} presented in \cite{regula:2010} which models an LED as the \textit{cartesian product} of booleans $b_0$, $b_1$, \ldots , $b_4$, the strip model we present here instead uses strings for the following reasons:
-\begin{itemize}
-\item Strings are indexible, and thus do not require separate \texttt{Set} and \texttt{Status} operations for each individual LED.
-\item This approach demonstrates the benefits of reusable mathematical theories.
-The specifications listed here are based (almost) entirely in \texttt{String\_Theory} and are therefore able to make use of RESOLVE's pre-existing math libraries.
-\end{itemize}
-
-Finally, the concept provides two operations.
-The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion that: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
-The \texttt{Status} operation is specified similarly.
-
-%Each operation carries with it a pre and post condition in the form of \texttt{requires} and \texttt{ensures} clause, which make explicit what must be true coming into the function, and what must be true after.
-For instance, the requires clause to \texttt{Status} states that \texttt{i} must fall somewhere within the bounds of the string which models our LED strip, while the \texttt{ensures} clause makes use of a \texttt{String\_Theory} definition, \texttt{Element\_At}, to assert that the boolean returned from \texttt{Status} is indeed the value occupying position \texttt{i} of \texttt{L}.
-It's important to note that the variables appearing in the \texttt{requires} and \texttt{ensures} clauses are strictly mathematical values.
-Thus, the \texttt{L} parameter of operation \texttt{Status} is referring to the mathematical value of an \texttt{LED}, as opposed to a programmatic one (typically defined in a realization).
-
-\subsection{Enhancements}
-
-RESOLVE also allows users to extend the functionality provided by the base concept through \textit{enhancements} -- a form of specification inheritance.
-The enhancement we provide here, \texttt{Toggling\_Capability}, allows users to flip a specific LED to its complement.
-
-Shown below is a specification for \texttt{Toggling\_Capability} and one particular realization of it.
-
-\begin{verbatim}
-Enhancement Toggling_Capability for LEDs_Template;
-
-    Oper Toggle(upd L : LED; eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures Element_At(i, L) = 
-                        not(Element_At(i, #L));
-end Toggling_Capability;
-
-Realization Toggling_Realiz for
-            Toggling_Capability of LEDs_Template;
-
-    Proc Toggle(upd L : LED; eval i : Integer);
-        Var Content : Boolean;
-
-        Content := Status(L, Replica(i));
-        Set(L, Not(Content), Replica(i));
-    end Toggle;
-
-end Toggling_Realiz;
-\end{verbatim}
-
-The enhancement specifies a single operation, \texttt{Toggle}, which states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
-
-Note that the enhancement specifications themselves look and function largely the same as a normal concept: Each specifies a purely conceptual module, and hence is implementation neutral.
-
-Enhancement realizations are neutral as well since any method called within the context of an enhancement realization refers to the operation specified in the concept -- meaning no knowledge of implementation details is required.
-
-\subsection{Verification}
-
-In this section we give a short overview of the verification results of \texttt{Toggling\_Realiz}.
-The first step in proving this particular realization correct is to generate verification conditions (VCs), which, if proven, will establish the correctness of this particular realization\footnote{Note: VCs themselves are typically generated from specific lines of a realization to ensure that the overall content of a realization is consistent with its specification.}.
-
-\begin{figure}[!htb]
-\centering
-\begin{tabular}{lccc}
-	\toprule
-	Condition \# & Time (ms)	& Steps	& Search \\
-	\midrule
-	VC 0\_1	& 4426	& 5	& 0	\\
-	VC 0\_2	& 5039	& 5	& 0	\\
-	VC 0\_3	& 6324	& 6	& 0	\\
-	\bottomrule
-\end{tabular}
-\caption{Verification results for operation \texttt{Toggle}}
-\label{fig:results}
-\end{figure}
-
-As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness.
-In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety.
-Readers interested however in learning more about how the prover goes about transforming and dispatching similar (and other, more complex) VCs should refer to \cite{smith:2013}.
-
-\subsection{Facilities}
-\label{sec:facilities}
-
-With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now turn to a small embedded application that combines these elements to iteratively toggle the lights within an LED strip.
-
-Shown below is a RESOLVE facility module that implements the client logic of this embedded application.
-\begin{verbatim}
-Facility LED_Telos_Demo;
-    uses Std_Clock_Fac;
-
-    Facility Leds_Fac is LED_Template(3)
-        externally realized by Std_Led_Realiz
-     enhanced by Toggling_Capability
-        realized by Toggling_Realiz;
-
-    Operation Main(); Procedure
-
-        (* Declare LED strip indices *)
-        Var I1, I2, I3 : Integer;
-        Var Loop : Boolean;
-
-        (* Declare an LED strip *)
-        Var L : Led;
-
-        I1 := 1; I2 := 2; I3 := 3;
-
-        Loop := True();
-        While(Loop)
-            changing Loop;
-            maintaining ...
-        do
-            Leds_Fac.Toggle(L, I1);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I2);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I3);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-        end;
-    end Main;
-
-end LED_Telos_Demo;
-\end{verbatim}
-%smaller file sizes
-%reusable code
-%only have to translate a file once
-% be able to say that the code we have is the code that was verified.
-% our approach takes less ROM. Its not less efficient, it is differently efficient.
-Prior to using the LED component developed in the previous sections, we first must associate our \texttt{LED\_Template} specification with an appropriate realization.
-This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
-Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
-
-The bulk of the logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
-
-\subsection{``External'' Realization Support}
-\label{ssec:external}
-
-Readers might note that we never presented a realization of \texttt{LED\_Template}.
-Indeed, after having written the concept, the RESOLVE programmer would ideally provide it with a verifiable, native RESOLVE implementation.
-However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by directly manipulating hardware pins provided by msp430's chipset.
-
-RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
-In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
-In the case of \texttt{LED\_Template}, we chose to provide a hand written \texttt{Std\_Leds\_Realiz} C realization, that matches as closely as possible the conventions and model of translation later detailed in Section \#.
-
-The \texttt{LED\_Telos\_Demo} facility showcased above demonstrates this through its use of the ``\texttt{externally realized}" phrase.
-This signals to the RESOLVE compiler that the user is providing a non-native realization, with the expectation that it conforms to the specifications dictated in the concept.
-
-% Applies to base types in resolve as well
-
-% Similar to NesC, the towers of abstraction idea...
-eventually, similar to nesc, we get enough abstraction  through machinery such as enhancements, etc to with pieces built on top of these externally realized components.
-
-% gives flexibility to those wishing to write other drivers and new
-
-We feel this new keyword is useful for the following reasons:
-\begin{itemize}
-\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code.
-The keyword now transparently indicates this.
-\item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
-\end{itemize}
-
-In the context of embedded systems especially, we feel these developments will allow users to flexibly and transparently specify all low level components of the sort required in most embedded applications (e.g.
-LED strip drivers).
-It is our intent that new (native) resolve components are layered on top of these low level drivers to provide a system (not unlike NesC) that deals with verified component graphs of ..
-
-%In a very real sense, gives the language the capability of specifying its foundational components flexibly, and transparently which can later have all native RESOLVE components added on top.
-
-%More than givingHaving the freedom to use RESOLVE's specificational capabilities
-
-%mention performance stuff in future work section.
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=.45]{figs/implementation.pdf}
-\caption{RESOLVE module types and their corresponding C representation}
-\end{figure*}
-\label{fig:imp}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=.55]{figs/ast_traversal.pdf}
-\caption{A RESOLVE operation AST, the walk call sequence, and sample translation output.}
-\end{figure*}
-\label{fig:ast}
-
 % IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE...
@@
 %A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation. 
-
 %To date there have been very few practical applications of verifiable code on physical media.
 
-\section{Acknowledgements}
+\subsection{An LED Implementation}
 
-Special thanks to Mike Kabanni, Mark Todd, and Bruce Weide whose suggestions and initial contributions in constructing the current model of RESOLVE to C translation made this work possible.
-
-%Open up the .tex file and compile it using Latex (Shift+Apple+L) then compile it using Bibtex (Shift+Apple+B)
-\bibliographystyle{unsrt}
-\bibliography{sigproc}
-\end{document}
+\begin{verbatim}
+void LED_Telos_create() {
+		Std_Boolean_Fac_create();
+		Std_Integer_Fac_create();
+		Std_Clock_Fac_create();
+		r_type_ptr __arg_0 = Std_Integer_Fac_Var.core->createFromInteger(4, Std_Integer_Fac_Var.core->Integer);
+		LED_Telos_Facility_Var.core = new_Std_LED_Realiz_for_Leds_Template(__arg_0);
+		LED_Telos_Facility_Var.Toggling_Capability = new_Toggling_Capability_of_Leds_Template(LED_Telos_Facility_Var.core);
+		Std_Integer_Fac_Var.core->Integer->destroy(__arg_0, Std_Integer_Fac_Var.core->Integer);
+}
+\end{verbatim}

### 2014-04-25 tech-project/specify_led.tex
changes to paper

--- 2014-04-22 tech-project/paper.tex
@@
-% CpSc 855 - Final paper
-% Takumi Bolte & Dan Welch - Spring 2014.
-\documentclass{sig-alternate}
-
-\usepackage{mathrsfs}
-\usepackage{booktabs}
-\usepackage{placeins}
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{listings}
-\begin{document}
-\conferenceinfo{Clemson 2014}{7th Clemson University Mini-Conference on Embedded Network Systems}
-\title{An Extensible Approach to Verification of Embedded Network Systems*}
-
-%Re-evaluating Verification of Embedded Network Systems:
-%An Extensible Approach to Verification of Embedded Network Systems*}
-\numberofauthors{2}
-\author{
-\alignauthor
-%author
-Daniel Welch\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{dtwelch\}@clemson.edu}}}
-%author
-\alignauthor
-Takumi Bolte\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{tbolte\}@clemson.edu}}}
-}
-
-\maketitle
-\begin{abstract}
-
-In this paper we present a flexible means of specifying and verifying the correctness of software for embedded network systems.
-Our approach uses RESOLVE, an imperative, component based programming and mathematical specification language, to verify the functional correctness of embedded applications.
-In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non-native RESOLVE) realizations.
-We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of a toggling capability enhancement that we demonstrate running on a Telos mote.
-\end{abstract}
-
-\category{D.2.8}{Software Engineering and Data Communication}{Verification}[VCs, automated proving, modular software]
-\terms{Reliability, Verification, Languages, Networks}
-\keywords{automation, components, formal methods, specification, verifying compiler, embedded networks, wireless sensing}
-
-\section{Introduction}
-\label{sec:intro}
-Within little more than a decade, the area of embedded network systems and wireless sensing has exploded in popularity within industry and academia alike.
-Tempering however this extremely quick rise in popularity is the inherent difficulties in developing applications that function as intended in low power, event-driven environments.
-In response to these difficulties, a variety of tools and languages have been put forth  to help ease the burden on developers.
-On one end of this effort are languages such as NesC, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
-The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Arora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
-Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed in the field.
-
-We approach this problem by using RESOLVE (Reusable SOftware Language with VErification) as means of authoring, specifying, and ultimately verifying code for embedded network systems.
-Our decision to use RESOLVE as a language frontend -- as opposed to verifying C code directly -- ultimately stems from a verification amenability standpoint: Not only does RESOLVE prohibit verification crippling operations such as uncontrolled referencing and aliasing (prevalent in C and many other current languages)\cite{kulczycki:2004}, but also embodies a number of other characteristics ideal for embedded platforms including:
-
-\begin{itemize}
-\item \textbf{Modularity} RESOLVE enforces a strict separation of concerns between module specifications and client implementations.
-As a result, for any one particular specification, there can be any number of interchangeable implementations.
-This separation is ideal considering that many embedded applications happen to fit this pattern nicely: Various drivers oftentimes provide a common set of functionality, but in general have many distinct implementations that vary arbitrarily from platform to platform, vendor to vendor.
-
-\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
-This is ideal in a setting where drivers might encompass a wide spectrum possible applications, where each might require unique, new mathematical developments.% reword this to be less vague.
-
-\end{itemize}
-
-The paper is organized as follows: First, we open with a brief overview of the Telos mote platform.
-Next, we present revised specifications of an LED driver component with a formally verified enhancement.
-This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used.
-The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code.
-We conclude with suggestions for tool improvements, as well as a review of some longer term research goals.
-
-\section{The Telos Platform}
-
-The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley.
-Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory.
-A cc2420 radio stack provides the mote with broadcast and receiving capabilities, while optional sensing capabilities may be added in the form of light, humidity, and temperature sensors.
-The mote also contains three onboard LEDs: One blue, one red, and one green.
-
-%Additionally, the Telos board contains a total of three LEDs -- one red, one green, and one blue.
 \section{Specifiying LED behavior in Resolve}
@@
 \label{fig:ast}
-
-% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE...
-AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE.
-BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
-\section{Implementation}
-Development of the tool presented here can be logically partitioned into three distinct phases: 
-\begin{enumerate}
-\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
-\item Implementing reusable mechanisms for carrying out the C code generation process.
-\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
-\end{enumerate}
-In this section we discuss each of these phases, concluding with a demo illustrating each working in tandem to realize the example presented in section \ref{sec:specifiying}.
-
-\subsection{C Translation Model}
-One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each.
-Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source.
-In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
-
-The memory model must also be considered as an additional verifiable component.
-Currently, RESOLVE is not capable of creating a complete specification of memory\footnote{RESOLVE is an object based language and has variable sized structures.
-Using dynamically allocatable memory is the favored approach to allow arbitrarily sized data.}.
-Thus, a memory model must be realized without a specification.
-To provide a straight forward translation from RESOLVE to C, we provide a dynamically-based memory allocator for use on embedded systems.
-
-The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
-Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
-Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
-Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
-RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
-
-%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
-
-\subsection{Translator Implementation}
-
-\subsubsection{AST Traversal}
-Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
-The traversal mechanism used is a dervivative of the visitor pattern that provides a SAX-dom style pre-post traversal over all nodes in the tree.
-Thus, for any given node present, a total of two visits occur: One corresponding to the node being `hit' during the pre traversal stage, and one for the post.
-
-To make this more concrete, consider the following dummy operation.
-
-\begin{verbatim}
-Operation Nothing(); Procedure
-        Var X : Integer;
-        X := 3;
-end Nothing;
-\end{verbatim}
-
-Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
-Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack.
-Each of these calls are received in the translator in the order in which they are visited within the tree.
-It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
-
-We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
-
-\begin{itemize}
-\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
-
-\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.
-
-\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
-This makes it easy to tweak and optimize the size of the translator's codebase, implementing only visit method for language constructs that explicitly require translation.
-\end{itemize}
-
-\subsubsection{Translation output}
-Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
-Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.
-
-An example C function definition template is shown below.
-
-\begin{verbatim}
-function_def(modifier, type, name, params, 
-                               vars, stmts) ::= <<
-<modifier> <type> <name> (<params; sep = ", ">) {
-    <vars; sep = "\n">
-    <stmts; sep = "\n">
-}>>
-\end{verbatim}
-
-User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
-It is entirely up to the user to define which attributes to fill in, and how complex they want them to be.
-For example, the user might choose to fill the \texttt{params} attribute with a simple string, or a separately defined \texttt{parameter} template, which in turn might use another separately defined \texttt{type} template.
-
-\begin{verbatim}
-parameter(type, name) ::= "<type> <name>"
-\end{verbatim}
-
-In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
-For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in.
-As \texttt{preOperationDec}'s children are visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the nodes being walked.
-Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in with the appropriate templates -- assuming the user has implemented the children's visit methods.
-
-Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
-This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).
-
-%One of the primary allures of this approach to translation is that that adheres to strict MVC design principles -- meaning that all output logic is distinctly separated from translation related logic.
-
-%We take advantage of these pre post methods using templates and simple stack to implement
-
-%Going even further, we demonstrate this by showing the steps taken to translate a simple operation declaration \texttt{nothing} to C.
-
-% for each construct to remain encapsulated within that method, and (almost) completely eliminates the need for complex loop or iteration mechanisms.
-
-%This particular traversal pattern lends itself well to the language translation challenge (specifically source to source) where the pre methods align naturally with beginning of a construct, and conclude with its corresponding post method.
-For instance, in the case above, this allows us, upon receiving a callback for In an effort to keep logic implementing our translator distinct and separate from the output language, we used a model view controller framework for implementing
-
-%To illustrate this, consider once again facility \texttt{DoNothing}.
-
-\subsection{Memory Allocation}
-
-Dynamic memory allocation does not lend itself well with an embedded programming paradigm.
-With hardware constraints, embedded systems have limited capacities on RAM.
-The telos motes are limited to 128 bytes of RAM.
-Many programs, however, require dynamic memory allocation to be used, including RESOLVE, in order to make it extensible.
-Previous RESOVE translations to C required static memory allocation \cite{regula:2010}.
-In this section a stack based dynamic memory allocator is introduced.
-
-\subsubsection{Allocation using \texttt{salloc}}
-
-The \texttt{salloc()} is a first fit memory allocator.
-Rather than allocating on the heap, \texttt{salloc()} uses the stack.
-At compilation, the allocator provisions a fixed size of memory.
-It requires a small section of meta-data called a block which contains information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
-A sample representation of the stack shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/stack.pdf}
-\caption{Representation of memory stack}
-\end{figure}
-\label{fig:stack}
-
-\subsubsection{Deallocation using \texttt{sfree}}
-
-A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated for something else.
-The \texttt{sfree()} operation is an analogous implementation to the standard C \texttt{free()} function for the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/sfree.pdf}
-\caption{sfree to free memory}
-\end{figure}
-\label{fig:free}
-
-\subsubsection{Optimizations}
-
-A common problem that can occur in memory allocation is fragmentation.
-As shown in figure \ref{fig:fragmentation}, fragmentation can lead to inefficient and increased memory usage.
-This problem is magnified on embedded systems with limited memory capabilities.
-Simple optimizations can be made however to reduce fragmentation.
-Splitting is one optimization that \texttt{salloc()} to maximize memory usage.
-Shown in figure \ref{fig:split}, blocks can be split to the size that is required.
-Another means of optimizing memory usage is joining together freed blocks.
-When a call to \texttt{sfree()} is made, neighboring blocks are coalesced together, as shown in figure \ref{fig:fuse}.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fragmentation.pdf}
-\caption{fragmentation}
-\end{figure}
-\label{fig:fragmentation}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/split.pdf}
-\caption{block splitting}
-\end{figure}
-\label{fig:split}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fuse.pdf}
-\caption{block fusing}
-\end{figure}
-\label{fig:fuse}
-%A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.
-
-%To date there have been very few practical applications of verifiable code on physical media.
-
-\section{Acknowledgements}
-
-Special thanks to Mike Kabanni, Mark Todd, and Bruce Weide whose suggestions and initial contributions in constructing the current model of RESOLVE to C translation made this work possible.
-
-%Open up the .tex file and compile it using Latex (Shift+Apple+L) then compile it using Bibtex (Shift+Apple+B)
-\bibliographystyle{unsrt}
-\bibliography{sigproc}
-\end{document}

### 2014-04-25 tech-project/telos_platform.tex
changes to paper

--- 2014-04-22 tech-project/paper.tex
@@
-% CpSc 855 - Final paper
-% Takumi Bolte & Dan Welch - Spring 2014.
-\documentclass{sig-alternate}
-
-\usepackage{mathrsfs}
-\usepackage{booktabs}
-\usepackage{placeins}
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{listings}
-\begin{document}
-\conferenceinfo{Clemson 2014}{7th Clemson University Mini-Conference on Embedded Network Systems}
-\title{An Extensible Approach to Verification of Embedded Network Systems*}
-
-%Re-evaluating Verification of Embedded Network Systems:
-%An Extensible Approach to Verification of Embedded Network Systems*}
-\numberofauthors{2}
-\author{
-\alignauthor
-%author
-Daniel Welch\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{dtwelch\}@clemson.edu}}}
-%author
-\alignauthor
-Takumi Bolte\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{tbolte\}@clemson.edu}}}
-}
-
-\maketitle
-\begin{abstract}
-
-In this paper we present a flexible means of specifying and verifying the correctness of software for embedded network systems.
-Our approach uses RESOLVE, an imperative, component based programming and mathematical specification language, to verify the functional correctness of embedded applications.
-In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non-native RESOLVE) realizations.
-We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of a toggling capability enhancement that we demonstrate running on a Telos mote.
-\end{abstract}
-
-\category{D.2.8}{Software Engineering and Data Communication}{Verification}[VCs, automated proving, modular software]
-\terms{Reliability, Verification, Languages, Networks}
-\keywords{automation, components, formal methods, specification, verifying compiler, embedded networks, wireless sensing}
-
-\section{Introduction}
-\label{sec:intro}
-Within little more than a decade, the area of embedded network systems and wireless sensing has exploded in popularity within industry and academia alike.
-Tempering however this extremely quick rise in popularity is the inherent difficulties in developing applications that function as intended in low power, event-driven environments.
-In response to these difficulties, a variety of tools and languages have been put forth  to help ease the burden on developers.
-On one end of this effort are languages such as NesC, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
-The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Arora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
-Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed in the field.
-
-We approach this problem by using RESOLVE (Reusable SOftware Language with VErification) as means of authoring, specifying, and ultimately verifying code for embedded network systems.
-Our decision to use RESOLVE as a language frontend -- as opposed to verifying C code directly -- ultimately stems from a verification amenability standpoint: Not only does RESOLVE prohibit verification crippling operations such as uncontrolled referencing and aliasing (prevalent in C and many other current languages)\cite{kulczycki:2004}, but also embodies a number of other characteristics ideal for embedded platforms including:
-
-\begin{itemize}
-\item \textbf{Modularity} RESOLVE enforces a strict separation of concerns between module specifications and client implementations.
-As a result, for any one particular specification, there can be any number of interchangeable implementations.
-This separation is ideal considering that many embedded applications happen to fit this pattern nicely: Various drivers oftentimes provide a common set of functionality, but in general have many distinct implementations that vary arbitrarily from platform to platform, vendor to vendor.
-
-\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
-This is ideal in a setting where drivers might encompass a wide spectrum possible applications, where each might require unique, new mathematical developments.% reword this to be less vague.
-
-\end{itemize}
-
-The paper is organized as follows: First, we open with a brief overview of the Telos mote platform.
-Next, we present revised specifications of an LED driver component with a formally verified enhancement.
-This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used.
-The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code.
-We conclude with suggestions for tool improvements, as well as a review of some longer term research goals.
-
 \section{The Telos Platform}
@@
 %Additionally, the Telos board contains a total of three LEDs -- one red, one green, and one blue.
-\section{Specifiying LED behavior in Resolve}
-\label{sec:specifiying}
-
-In this section, we provide mathematical and programmatic elements of an LED strip component to give readers both a concrete look at the language, and introduce some new features aimed at making it more amenable to the development of embedded applications.
-Note that while we provide the level of detail necessary to understand the current example, readers interested in gaining a more complete, in depth knowledge of the language are encouraged to refer to \cite{sitaraman:2011, kulczycki:2008}.
-
-\subsection{Concepts}
-\label{ssec:concepts}
-In RESOLVE, programs are composed of several different modules that range from interfaces and realizations, to client (facility) modules.
-A \textit{concept} module in RESOLVE defines a specification for a mathematical, abstract type.
-Similar to an interface in Java, a concept provides a number of operation signatures that implementors are expected to realize.
-Shown below is a \texttt{LED\_Template} concept that provides a light strip abstraction.
-
-\begin{verbatim}
-Concept LED_Template(eval Strip_Length: Integer);
-    uses Boolean_Theory, String_Theory;
-    requires 0 < Strip_Length <= 4;
-
-    Type Family LED is modeled by Str(B);
-        exemplar L;
-        constraint |L| = Strip_Length;
-        initialization ensures 
-            ...
-
-    Oper Set(updates L : LED; eval b : Boolean; 
-                             eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures |L| = |#L| and 
-                   Element_At(i, L) = b;
-
-    Oper Status(preserves L : LED; 
-                   eval i : Integer) : Boolean;
-        requires 0 <= i < |L|;
-        ensures Status = Element_At(i, L);
-
-end LEDs_Template;
-\end{verbatim}
-
-We model our conceptual LED strip using a mathematical string (finite sequence) of booleans, denoted \texttt{Str(B)}, where each boolean within the string indicates the status of that particular LED: On (true) or off (false).
-The \texttt{exemplar} clause located immediately below provides a handle to this abstract model, and is used throughout the remainder of the specification.
-
-%The \texttt{Type Family} clause introduces an abstract type for the LED strip which we mathematically model using strings of booleans, denoted \texttt{Str(B)}, while the \texttt{exemplar} declared immediately after provides a handle to this type family.
-Use of the \texttt{exemplar} can be observed in the \texttt{constraint} clause, where it is used to assert that length of the strip is fixed to be whatever the user has specified via the \texttt{Strip\_Length} parameter.
-Finally, the \texttt{initialization} \texttt{ensures} clause makes explicit the state of the structure at the time it is initialized.
-We omit this verification specific clause, as it has little bearing on verification due to the fact that the realization we provide is \textit{externally} realized -- a point discussed in the next section\footnote{This clause, if it were provided, would need to communicate the following: ``For each position $i$ within the strip, the LED (or, value) at position $i$ is initially false."}
-
-It's worth noting that unlike the \texttt{LED\_Template} presented in \cite{regula:2010} which models an LED as the \textit{cartesian product} of booleans $b_0$, $b_1$, \ldots , $b_4$, the strip model we present here instead uses strings for the following reasons:
-\begin{itemize}
-\item Strings are indexible, and thus do not require separate \texttt{Set} and \texttt{Status} operations for each individual LED.
-\item This approach demonstrates the benefits of reusable mathematical theories.
-The specifications listed here are based (almost) entirely in \texttt{String\_Theory} and are therefore able to make use of RESOLVE's pre-existing math libraries.
-\end{itemize}
-
-Finally, the concept provides two operations.
-The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion that: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
-The \texttt{Status} operation is specified similarly.
-
-%Each operation carries with it a pre and post condition in the form of \texttt{requires} and \texttt{ensures} clause, which make explicit what must be true coming into the function, and what must be true after.
-For instance, the requires clause to \texttt{Status} states that \texttt{i} must fall somewhere within the bounds of the string which models our LED strip, while the \texttt{ensures} clause makes use of a \texttt{String\_Theory} definition, \texttt{Element\_At}, to assert that the boolean returned from \texttt{Status} is indeed the value occupying position \texttt{i} of \texttt{L}.
-It's important to note that the variables appearing in the \texttt{requires} and \texttt{ensures} clauses are strictly mathematical values.
-Thus, the \texttt{L} parameter of operation \texttt{Status} is referring to the mathematical value of an \texttt{LED}, as opposed to a programmatic one (typically defined in a realization).
-
-\subsection{Enhancements}
-
-RESOLVE also allows users to extend the functionality provided by the base concept through \textit{enhancements} -- a form of specification inheritance.
-The enhancement we provide here, \texttt{Toggling\_Capability}, allows users to flip a specific LED to its complement.
-
-Shown below is a specification for \texttt{Toggling\_Capability} and one particular realization of it.
-
-\begin{verbatim}
-Enhancement Toggling_Capability for LEDs_Template;
-
-    Oper Toggle(upd L : LED; eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures Element_At(i, L) = 
-                        not(Element_At(i, #L));
-end Toggling_Capability;
-
-Realization Toggling_Realiz for
-            Toggling_Capability of LEDs_Template;
-
-    Proc Toggle(upd L : LED; eval i : Integer);
-        Var Content : Boolean;
-
-        Content := Status(L, Replica(i));
-        Set(L, Not(Content), Replica(i));
-    end Toggle;
-
-end Toggling_Realiz;
-\end{verbatim}
-
-The enhancement specifies a single operation, \texttt{Toggle}, which states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
-
-Note that the enhancement specifications themselves look and function largely the same as a normal concept: Each specifies a purely conceptual module, and hence is implementation neutral.
-
-Enhancement realizations are neutral as well since any method called within the context of an enhancement realization refers to the operation specified in the concept -- meaning no knowledge of implementation details is required.
-
-\subsection{Verification}
-
-In this section we give a short overview of the verification results of \texttt{Toggling\_Realiz}.
-The first step in proving this particular realization correct is to generate verification conditions (VCs), which, if proven, will establish the correctness of this particular realization\footnote{Note: VCs themselves are typically generated from specific lines of a realization to ensure that the overall content of a realization is consistent with its specification.}.
-
-\begin{figure}[!htb]
-\centering
-\begin{tabular}{lccc}
-	\toprule
-	Condition \# & Time (ms)	& Steps	& Search \\
-	\midrule
-	VC 0\_1	& 4426	& 5	& 0	\\
-	VC 0\_2	& 5039	& 5	& 0	\\
-	VC 0\_3	& 6324	& 6	& 0	\\
-	\bottomrule
-\end{tabular}
-\caption{Verification results for operation \texttt{Toggle}}
-\label{fig:results}
-\end{figure}
-
-As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness.
-In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety.
-Readers interested however in learning more about how the prover goes about transforming and dispatching similar (and other, more complex) VCs should refer to \cite{smith:2013}.
-
-\subsection{Facilities}
-\label{sec:facilities}
-
-With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now turn to a small embedded application that combines these elements to iteratively toggle the lights within an LED strip.
-
-Shown below is a RESOLVE facility module that implements the client logic of this embedded application.
-\begin{verbatim}
-Facility LED_Telos_Demo;
-    uses Std_Clock_Fac;
-
-    Facility Leds_Fac is LED_Template(3)
-        externally realized by Std_Led_Realiz
-     enhanced by Toggling_Capability
-        realized by Toggling_Realiz;
-
-    Operation Main(); Procedure
-
-        (* Declare LED strip indices *)
-        Var I1, I2, I3 : Integer;
-        Var Loop : Boolean;
-
-        (* Declare an LED strip *)
-        Var L : Led;
-
-        I1 := 1; I2 := 2; I3 := 3;
-
-        Loop := True();
-        While(Loop)
-            changing Loop;
-            maintaining ...
-        do
-            Leds_Fac.Toggle(L, I1);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I2);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I3);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-        end;
-    end Main;
-
-end LED_Telos_Demo;
-\end{verbatim}
-%smaller file sizes
-%reusable code
-%only have to translate a file once
-% be able to say that the code we have is the code that was verified.
-% our approach takes less ROM. Its not less efficient, it is differently efficient.
-Prior to using the LED component developed in the previous sections, we first must associate our \texttt{LED\_Template} specification with an appropriate realization.
-This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
-Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
-
-The bulk of the logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
-
-\subsection{``External'' Realization Support}
-\label{ssec:external}
-
-Readers might note that we never presented a realization of \texttt{LED\_Template}.
-Indeed, after having written the concept, the RESOLVE programmer would ideally provide it with a verifiable, native RESOLVE implementation.
-However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by directly manipulating hardware pins provided by msp430's chipset.
-
-RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
-In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
-In the case of \texttt{LED\_Template}, we chose to provide a hand written \texttt{Std\_Leds\_Realiz} C realization, that matches as closely as possible the conventions and model of translation later detailed in Section \#.
-
-The \texttt{LED\_Telos\_Demo} facility showcased above demonstrates this through its use of the ``\texttt{externally realized}" phrase.
-This signals to the RESOLVE compiler that the user is providing a non-native realization, with the expectation that it conforms to the specifications dictated in the concept.
-
-% Applies to base types in resolve as well
-
-% Similar to NesC, the towers of abstraction idea...
-eventually, similar to nesc, we get enough abstraction  through machinery such as enhancements, etc to with pieces built on top of these externally realized components.
-
-% gives flexibility to those wishing to write other drivers and new
-
-We feel this new keyword is useful for the following reasons:
-\begin{itemize}
-\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code.
-The keyword now transparently indicates this.
-\item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
-\end{itemize}
-
-In the context of embedded systems especially, we feel these developments will allow users to flexibly and transparently specify all low level components of the sort required in most embedded applications (e.g.
-LED strip drivers).
-It is our intent that new (native) resolve components are layered on top of these low level drivers to provide a system (not unlike NesC) that deals with verified component graphs of ..
-
-%In a very real sense, gives the language the capability of specifying its foundational components flexibly, and transparently which can later have all native RESOLVE components added on top.
-
-%More than givingHaving the freedom to use RESOLVE's specificational capabilities
-
-%mention performance stuff in future work section.
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=.45]{figs/implementation.pdf}
-\caption{RESOLVE module types and their corresponding C representation}
-\end{figure*}
-\label{fig:imp}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=.55]{figs/ast_traversal.pdf}
-\caption{A RESOLVE operation AST, the walk call sequence, and sample translation output.}
-\end{figure*}
-\label{fig:ast}
-
-% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE...
-AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE.
-BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
-\section{Implementation}
-Development of the tool presented here can be logically partitioned into three distinct phases: 
-\begin{enumerate}
-\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
-\item Implementing reusable mechanisms for carrying out the C code generation process.
-\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
-\end{enumerate}
-In this section we discuss each of these phases, concluding with a demo illustrating each working in tandem to realize the example presented in section \ref{sec:specifiying}.
-
-\subsection{C Translation Model}
-One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each.
-Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source.
-In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
-
-The memory model must also be considered as an additional verifiable component.
-Currently, RESOLVE is not capable of creating a complete specification of memory\footnote{RESOLVE is an object based language and has variable sized structures.
-Using dynamically allocatable memory is the favored approach to allow arbitrarily sized data.}.
-Thus, a memory model must be realized without a specification.
-To provide a straight forward translation from RESOLVE to C, we provide a dynamically-based memory allocator for use on embedded systems.
-
-The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
-Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
-Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
-Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
-RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
-
-%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
-
-\subsection{Translator Implementation}
-
-\subsubsection{AST Traversal}
-Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
-The traversal mechanism used is a dervivative of the visitor pattern that provides a SAX-dom style pre-post traversal over all nodes in the tree.
-Thus, for any given node present, a total of two visits occur: One corresponding to the node being `hit' during the pre traversal stage, and one for the post.
-
-To make this more concrete, consider the following dummy operation.
-
-\begin{verbatim}
-Operation Nothing(); Procedure
-        Var X : Integer;
-        X := 3;
-end Nothing;
-\end{verbatim}
-
-Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
-Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack.
-Each of these calls are received in the translator in the order in which they are visited within the tree.
-It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
-
-We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
-
-\begin{itemize}
-\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
-
-\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.
-
-\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
-This makes it easy to tweak and optimize the size of the translator's codebase, implementing only visit method for language constructs that explicitly require translation.
-\end{itemize}
-
-\subsubsection{Translation output}
-Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
-Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.
-
-An example C function definition template is shown below.
-
-\begin{verbatim}
-function_def(modifier, type, name, params, 
-                               vars, stmts) ::= <<
-<modifier> <type> <name> (<params; sep = ", ">) {
-    <vars; sep = "\n">
-    <stmts; sep = "\n">
-}>>
-\end{verbatim}
-
-User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
-It is entirely up to the user to define which attributes to fill in, and how complex they want them to be.
-For example, the user might choose to fill the \texttt{params} attribute with a simple string, or a separately defined \texttt{parameter} template, which in turn might use another separately defined \texttt{type} template.
-
-\begin{verbatim}
-parameter(type, name) ::= "<type> <name>"
-\end{verbatim}
-
-In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
-For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in.
-As \texttt{preOperationDec}'s children are visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the nodes being walked.
-Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in with the appropriate templates -- assuming the user has implemented the children's visit methods.
-
-Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
-This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).
-
-%One of the primary allures of this approach to translation is that that adheres to strict MVC design principles -- meaning that all output logic is distinctly separated from translation related logic.
-
-%We take advantage of these pre post methods using templates and simple stack to implement
-
-%Going even further, we demonstrate this by showing the steps taken to translate a simple operation declaration \texttt{nothing} to C.
-
-% for each construct to remain encapsulated within that method, and (almost) completely eliminates the need for complex loop or iteration mechanisms.
-
-%This particular traversal pattern lends itself well to the language translation challenge (specifically source to source) where the pre methods align naturally with beginning of a construct, and conclude with its corresponding post method.
-For instance, in the case above, this allows us, upon receiving a callback for In an effort to keep logic implementing our translator distinct and separate from the output language, we used a model view controller framework for implementing
-
-%To illustrate this, consider once again facility \texttt{DoNothing}.
-
-\subsection{Memory Allocation}
-
-Dynamic memory allocation does not lend itself well with an embedded programming paradigm.
-With hardware constraints, embedded systems have limited capacities on RAM.
-The telos motes are limited to 128 bytes of RAM.
-Many programs, however, require dynamic memory allocation to be used, including RESOLVE, in order to make it extensible.
-Previous RESOVE translations to C required static memory allocation \cite{regula:2010}.
-In this section a stack based dynamic memory allocator is introduced.
-
-\subsubsection{Allocation using \texttt{salloc}}
-
-The \texttt{salloc()} is a first fit memory allocator.
-Rather than allocating on the heap, \texttt{salloc()} uses the stack.
-At compilation, the allocator provisions a fixed size of memory.
-It requires a small section of meta-data called a block which contains information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
-A sample representation of the stack shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/stack.pdf}
-\caption{Representation of memory stack}
-\end{figure}
-\label{fig:stack}
-
-\subsubsection{Deallocation using \texttt{sfree}}
-
-A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated for something else.
-The \texttt{sfree()} operation is an analogous implementation to the standard C \texttt{free()} function for the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/sfree.pdf}
-\caption{sfree to free memory}
-\end{figure}
-\label{fig:free}
-
-\subsubsection{Optimizations}
-
-A common problem that can occur in memory allocation is fragmentation.
-As shown in figure \ref{fig:fragmentation}, fragmentation can lead to inefficient and increased memory usage.
-This problem is magnified on embedded systems with limited memory capabilities.
-Simple optimizations can be made however to reduce fragmentation.
-Splitting is one optimization that \texttt{salloc()} to maximize memory usage.
-Shown in figure \ref{fig:split}, blocks can be split to the size that is required.
-Another means of optimizing memory usage is joining together freed blocks.
-When a call to \texttt{sfree()} is made, neighboring blocks are coalesced together, as shown in figure \ref{fig:fuse}.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fragmentation.pdf}
-\caption{fragmentation}
-\end{figure}
-\label{fig:fragmentation}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/split.pdf}
-\caption{block splitting}
-\end{figure}
-\label{fig:split}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fuse.pdf}
-\caption{block fusing}
-\end{figure}
-\label{fig:fuse}
-%A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.
-
-%To date there have been very few practical applications of verifiable code on physical media.
-
-\section{Acknowledgements}
-
-Special thanks to Mike Kabanni, Mark Todd, and Bruce Weide whose suggestions and initial contributions in constructing the current model of RESOLVE to C translation made this work possible.
-
-%Open up the .tex file and compile it using Latex (Shift+Apple+L) then compile it using Bibtex (Shift+Apple+B)
-\bibliographystyle{unsrt}
-\bibliography{sigproc}
-\end{document}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Bdd_Spiral_Template/Array_Realiz.rb
cleaned house

@@ -1,21 +1,0 @@
-Realization Array_Realiz for Bdd_Spiral_Template;
-	
-	Facility Ceramic_Array_Fac is 
-		Static_Array_Template(Label, 1, Max_Length)
-		externally realized by Std_Array_Realiz;
-		
-	Type Spiral_Pos is represented by Record
-			Labl : Ceramic_Array_Fac.Static_Array;
-			Length, Curr : Integer;
-		end;
-		convention 0 <= P.Curr <= P.Length and 
-				   P.Length <= Max_Length;
-		correspondence true;
-	end;
-	
-	Proc Lengthen(upd P : Spiral_Pos; alt New_Lab : Label);
-		Ceramic_Array_Fac.Swap_Entry(P.Labl, New_Lab, P.Length);
-		P.Length := P.Length + 1;
-	end Lengthen;
-	
-end Array_Realiz;	

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Clock_Template/Clock_Template.h

@@ -1,19 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __CLOCK_TEMPLATE_H
-#define __CLOCK_TEMPLATE_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-
-typedef struct Clock_Template Clock_Template;
-struct Clock_Template {
-    void* Realization_Specific;
-    void (*Wait_1_Second) (Clock_Template*);
-    void (*Wait_5_Seconds) (Clock_Template*);
-    void (*Wait_500_Milli_Seconds) (Clock_Template*);
-};
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Clock_Template/Std_Clock_Realiz.c

@@ -1,47 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#include "Std_Clock_Realiz.h"
-#include "Clock_Template.h"
-#ifdef TELOS
-#include <msp430.h>
-#include <legacymsp430.h>
-#endif
-
-extern void free_Std_Clock_Realiz_for_Clock_Template(Clock_Template* toFree) {
-	sfree(toFree);
-}
-
-static void Wait_1_Second(Clock_Template* this) {
-#ifdef TELOS
-	__delay_cycles(40000000);	
-#else
-	printf("Waiting 1 Second...\n");
-#endif
-}
-
-static void Wait_5_Seconds(Clock_Template* this) {
-#ifdef TELOS
-	__delay_cycles(20000000);
-#else
-	printf("Waiting 5 Seconds...\n");
-#endif
-}
-
-static void Wait_500_Milli_Seconds(Clock_Template* this) {
-#ifdef TELOS
-	__delay_cycles(2000000);
-#else
-	printf("Waiting 500 Milliseconds...\n");
-#endif
-}
-
-extern Clock_Template* new_Std_Clock_Realiz_for_Clock_Template() {
-	Clock_Template* this = salloc(sizeof(Clock_Template));
-	this->Wait_5_Seconds = Wait_5_Seconds;
-	this->Wait_1_Second = Wait_1_Second;
-	this->Wait_500_Milli_Seconds = Wait_500_Milli_Seconds;
-
-	return this;	
-}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Clock_Template/Std_Clock_Realiz.h

@@ -1,13 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __STD_CLOCK_REALIZ_H
-#define __STD_CLOCK_REALIZ_H
-
-#include "Clock_Template.h"
-
-extern Clock_Template* new_Std_Clock_Realiz_for_Clock_Template();
-extern void free_Std_Clock_Realiz_for_Clock_Template(Clock_Template* toFree);
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Leds_Template/Leds_Template.h

@@ -1,21 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __LEDS_TEMPLATE_H
-#define __LEDS_TEMPLATE_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-
-typedef struct Leds_Template Leds_Template;
-struct Leds_Template {
-    r_type_ptr Strip_Length;
-    void* Realization_Specific;
-    type_info* Led;
-    void (*Set) (r_type_ptr, r_type_ptr, r_type_ptr, Leds_Template*);
-    r_type_ptr (*Status) (r_type_ptr, r_type_ptr, Leds_Template*);
-    r_type_ptr (*Length) (r_type_ptr, Leds_Template*);
-};
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Leds_Template/Std_Leds_Realiz.c

@@ -1,113 +1,0 @@
-#ifdef TELOS
-#include <msp430.h>
-#include <legacymsp430.h>
-#endif
-#include "Std_Leds_Realiz.h"
-#include "naive_malloc.h"
-
-#define LED0 (0x0010)
-#define LED1 (0x0020)
-#define LED2 (0x0040)
-
-#ifdef TELOS
-#define LED_DIR P5DIR
-#define LED_OUT P5OUT
-#else
-int LED_OUT = 0;
-#endif
-
-static r_type_ptr createLed(type_info* LedType) {
-	Leds_Template* this = salloc(sizeof(Leds_Template));
-	return (r_type_ptr)this;
-}
-
-static void destroyLed(r_type_ptr r, type_info* LedType) {
-	sfree(*r);
-	sfree(r);
-}
-
-static void Set(r_type_ptr r, r_type_ptr b, r_type_ptr i, Leds_Template* this) {
-	int hex = 0x00;
-	int out = **(int**)i;
-	int led0, led1, led2;
-	if(**(int**)b == 0) {
-		hex = LED0 << out;
-	}
-
-	if(out == 0) {
-		led1 = LED_OUT & LED1;
-		led2 = LED_OUT & LED2;
-		LED_OUT = (hex & LED0) + led1 + led2;
-	}	
-	else if(out == 1) {
-		led0 = LED_OUT & LED0;
-		led2 = LED_OUT & LED2;
-		LED_OUT = (hex & LED1) + led0 + led2;
-	}
-	else {
-		led0 = LED_OUT & LED0;
-		led1 = LED_OUT & LED1;
-		LED_OUT = (hex & LED2) + led0 + led1;
-	}
-}
-
-static r_type_ptr Status(r_type_ptr r, r_type_ptr i, Leds_Template* this) {
-	int *mask = scalloc(1, sizeof(int));
-
-	if(**(int**)i == 0) {
-		*mask = LED_OUT & LED0;
-		*mask = *mask ^ LED0;
-		*mask = *mask >> 3;
-	}
-	else if(**(int**)i == 1) {
-		*mask = LED_OUT & LED1;
-		*mask = *mask ^ LED1;
-	}
-	else {
-		*mask = LED_OUT & LED2;
-		*mask = *mask ^ LED2;
-	}
-
-	int **ret = salloc(sizeof(int*));
-	*ret = mask;
-	return (r_type_ptr)(ret);
-}
-
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Leds_Template/Std_Leds_Realiz.h

@@ -1,12 +1,0 @@
-#ifndef __STD_LEDS_REALIZ_H
-#define __STD_LEDS_REALIZ_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Concepts/Leds_Template/Leds_Template.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-
-extern Leds_Template* new_Std_Leds_Realiz_for_Leds_Template(r_type_ptr Strip_Length);
-extern void free_Std_Leds_Realiz_for_Leds_Template(Leds_Template* toFree);
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Leds_Template/Toggling_Capability.h

@@ -1,19 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __TOGGLING_CAPABILITY_H
-#define __TOGGLING_CAPABILITY_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Concepts/Leds_Template/Leds_Template.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-
-typedef struct Toggling_Capability_for_Leds_Template Toggling_Capability_for_Leds_Template;
-struct Toggling_Capability_for_Leds_Template {
-    Leds_Template* core;
-    void* Realization_Specific;
-    void (*Toggle) (r_type_ptr, r_type_ptr, Toggling_Capability_for_Leds_Template*);
-};
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Leds_Template/Toggling_Realiz.c

@@ -1,34 +1,0 @@
-#include "Toggling_Realiz.h"
-#include "naive_malloc.h"
-
-static void Toggle(r_type_ptr L, r_type_ptr I, Toggling_Capability_for_Leds_Template* this) {
-		r_type_ptr Content = Std_Boolean_Fac_Var.core->Boolean->create(Std_Boolean_Fac_Var.core->Boolean);
-		r_type_ptr Index = Std_Integer_Fac_Var.core->Integer->create(Std_Integer_Fac_Var.core->Integer);
-
-		r_type_ptr tmp_exp_1;
-		r_type_ptr tmp_exp_2;
-		r_type_ptr tmp_exp_3;
-
-		tmp_exp_1 = Std_Integer_Fac_Var.core->Replica(I, Std_Integer_Fac_Var.core);
-		Std_Integer_Fac_Var.core->assign(Index, tmp_exp_1, Std_Integer_Fac_Var.core);
-
-		tmp_exp_2 = this->core->Status(L, Index, this->core);
-		Std_Boolean_Fac_Var.core->assign(Content, tmp_exp_2, Std_Boolean_Fac_Var.core);
-
-		tmp_exp_3 = Std_Boolean_Fac_Var.core->Not(Content, Std_Boolean_Fac_Var.core);
-		this->core->Set(L, tmp_exp_3, I, this->core);
-
-		Std_Integer_Fac_Var.core->Integer->destroy(Index, Std_Integer_Fac_Var.core->Integer);
-		Std_Boolean_Fac_Var.core->Boolean->destroy(Content, Std_Boolean_Fac_Var.core->Boolean);
-		Std_Integer_Fac_Var.core->Integer->destroy(tmp_exp_1, Std_Integer_Fac_Var.core->Integer);
-		Std_Integer_Fac_Var.core->Integer->destroy(tmp_exp_2, Std_Integer_Fac_Var.core->Integer);
-		Std_Boolean_Fac_Var.core->Boolean->destroy(tmp_exp_3, Std_Boolean_Fac_Var.core->Boolean);
-}
-
-extern Toggling_Capability_for_Leds_Template* new_Toggling_Realiz_for_Toggling_Capability_of_Leds_Template(Leds_Template* core) {
-    Toggling_Capability_for_Leds_Template* this = scalloc(1, sizeof(Toggling_Capability_for_Leds_Template));
-    this->Toggle = Toggle;
-    this->core = core;
-
-    return this;
-}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Leds_Template/Toggling_Realiz.h

@@ -1,17 +1,0 @@
-/*
- *  * Generated by the RESOLVE to C translator. This file
- *   * should not be modified.
- *    */
-#ifndef __TOGGLING_REALIZ_H
-#define __TOGGLING_REALIZ_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Concepts/Leds_Template/Leds_Template.h"
-#include "../../../Main/Concepts/Leds_Template/Toggling_Capability.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-
-extern Toggling_Capability_for_Leds_Template*
-new_Toggling_Realiz_for_Toggling_Capability_of_Leds_Template(Leds_Template*);
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Circular_Array_Realiz.rb

@@ -1,86 +1,0 @@
-(*
- * This softare is released under the new BSD 2006 license.
- * 
- * Note the new BSD license is equivalent to the MIT License, except for the
- * no-endorsement final clause.
- * 
- * Copyright (c) 2007, Clemson University
- * 
- * All rights reserved.
- * 
- * Redistribution and use in source and binary forms, with or without
- * modification, are permitted provided that the following conditions are met:
- * 
- *   * Redistributions of source code must retain the above copyright notice,
- *     this list of conditions and the following disclaimer. 
- *   * Redistributions in binary form must reproduce the above copyright
- *     notice, this list of conditions and the following disclaimer in the
- *     documentation and/or other materials provided with the distribution. 
- *   * Neither the name of the Clemson University nor the names of its
- *     contributors may be used to endorse or promote products derived from
- *     this software without specific prior written permission. 
- * 
- * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
- * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
- * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
- * A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER
- * OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
- * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO,
- * PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
- * PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
- * LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
- * NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
- * SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
- * 
- * This sofware has been developed by past and present members of the
- * Reusable Sofware Research Groups (RSRG) at Clemson University and
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Combined_Merge_Sort_Realiz.rb

@@ -1,64 +1,0 @@
-Realization Combined_Merge_Sort_Realiz(
-		Operation Are_Ordered(restores x,y: Entry): Boolean;
-			ensures Are_Ordered = (LEQV(x,y));
-	) for Merge_and_Sort_Capabilities of Queue_Template;
- 
-	Procedure Merge_Q(clears Q: Queue; updates R: Queue);
-		Var Merger: Queue; 
-		Var Q_Min, R_Min: Entry;
- 
-		If ( Greater(Length(Q), 0) ) then
-			Dequeue(Q_Min, Q);
-			While( Greater(Length(R), 0) )
-				changing Q, R, Merger, Q_Min, R_Min;
-				maintaining Is_Conformal_With(LEQV, Merger o R) and
-					Is_Conformal_With(LEQV, Merger o <Q_Min> o Q) and
-					Is_Permutation(#Q o #R, Merger o <Q_Min> o Q o R);
-				decreasing |Q o R|;
-			do
-				Dequeue(R_Min, R);
-				if ( Are_Equal(Are_Ordered(Q_Min, R_Min), True()) ) then
-					Enqueue(Q_Min, Merger);
-					Q_Min :=: R_Min; 
-					Q :=: R;
-				else
-					Enqueue(R_Min, Merger);
-				end;
-			end;
-			Enqueue(Q_Min, Merger);
-			While( Greater(Length(Q), 0) )
-				changing Q, Merger, Q_Min;
-				maintaining Is_Conformal_With(LEQV, Merger o Q) and
-					Is_Permutation(#Q o #R, Merger o Q);
-				decreasing |Q|;
-			do
-				Dequeue(Q_Min, Q);
-				Enqueue(Q_Min, Merger);
-			end;
-			R :=: Merger;
-		end;
-	end Merge_Q;
-
-	Recursive Procedure Sort_Q(updates Q: Queue);
-		decreasing |Q|;
- 
-		Var First_Q: Queue;
-		Var Next_Entry: Entry;
-		Var Temp: Integer;
- 
-		If ( Greater(Length(Q), 1) ) then
-			Temp := Length(Q) - 1;
-			While( Less(Length(First_Q), Temp) )
-				changing Q, First_Q, Next_Entry;
-				maintaining #Q = First_Q o Q and |First_Q| <= |Q|;
-				decreasing |Q|;
-			do
-				Dequeue(Next_Entry, Q);
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Folding_Average_Realization.rb

@@ -1,55 +1,0 @@
-Realization Folding_Average_Realization(
-			Operation MapEntry(restores E : Entry; replaces I : Integer);
-				ensures I = AsInteger(E) and 
-					0 <= AsInteger(E) <= max_int;)
-		for Averaging_Capability of Queue_Template;
-		
-    (* Note: Under Construction! *)
-
-	Procedure Average(restores Q : Queue) : Integer;
-		Var Cur_Entry : Entry;
-		Var Cur_Entry_As_Integer : Integer;
-		Var Included : Queue;
-		Var Running_Average : Integer;
-		Var Running_Remainder : Integer;
-		Var Remainder_Adjust : Integer;
-		Var Weighted_Cur_Entry : Integer;
-		Var Cur_Entry_Remainder : Integer;
-		Var Q_Length : Integer;
-
-		Q_Length := Length(Q);
-
-		While (Length(Q) > 0)
-			changing Cur_Entry, Included, Q, Running_Average, Running_Remainder,
-				Weighted_Cur_Entry, Cur_Entry_Remainder, Remainder_Adjust;
-			maintaining Included o Q = #Q and
-				Running_Average = 
-					Fold_String_Right(Sum, 0, Map(Included, AsInteger)) /
-						|#Q| and
-				Running_Remainder =
-					Fold_String_Right(Sum, 0, Map(Included, AsInteger)) mod
-						|#Q| and
-				0 <= Running_Average <= max_int / |#Q| * |Included|;
-			decreasing |Q|;
-		do
-			Dequeue(Cur_Entry, Q);
-			MapEntry(Cur_Entry, Cur_Entry_As_Integer);
-
-			Weighted_Cur_Entry := Div(Cur_Entry_As_Integer, Q_Length);
-			Cur_Entry_Remainder := Mod(Cur_Entry_As_Integer, Q_Length);
-
-			Running_Average := Running_Average + Weighted_Cur_Entry;
-
-			Running_Remainder := Running_Remainder + Cur_Entry_Remainder;
-			Remainder_Adjust := Div(Running_Remainder, Q_Length);
-			Running_Remainder := Mod(Running_Remainder, Q_Length);
-
-			Enqueue(Cur_Entry, Included);
-		end;
-
-		Q :=: Included;
-
-		Average := Running_Average;
-	end;
-
-end Folding_Average_Realization;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Inject_Front_Realiz.rb

@@ -1,17 +1,0 @@
-Realization Inject_Front_Realiz for Inject_Front_Capability of Queue_Template;
-
-	Procedure Inject_at_Front(alters E: Entry; updates Q: Queue);
-		Var T: Queue;
-		
-		Enqueue (E, T);
-		While ( Is_Not_Zero(Length(Q)) )
-			changing Q,T,E;
-			maintaining T o Q = <#E> o #Q;
-			decreasing |Q|;
-		do
-			Dequeue(E,Q);
-			Enqueue(E,T);
-		end;
-		Q :=: T;
-	end Inject_at_Front;
-end Inject_Front_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Iterative_Append_Realiz.rb

@@ -1,12 +1,0 @@
-Realization Iterative_Append_Realiz for Append_Capability of Queue_Template;
-    Procedure Append(updates P: Queue; clears Q: Queue);
-        Var E: Entry;
-        While ( Is_Not_Zero(Length(Q)) )
-          maintaining (P o Q = #P o #Q);
-          decreasing |Q|;
-        do
-          Dequeue(E,Q);
-          Enqueue(E,P);
-        end;
-    end Append;
-end Iterative_Append_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Iterative_Fold_Realization.rb

@@ -1,34 +1,0 @@
-Realization Iterative_Fold_Realization(
-			Operation FoldIn(updates soFar : T; 
-					restores next : Entry);
-				ensures soFar = Combined(#soFar, next);) 
-		for Fold_Capability of Queue_Template;
-
-    (* Note: Under Construction! *)
-
-	Procedure Fold_Right(updates Accumulator : T; restores List : Queue);
-		Var Included : Queue;
-		Var Cur_Entry : Entry;
-
-		While (Length(List) > 0)
-			changing List, Included, Cur_Entry, Accumulator;
-			maintaining Accumulator = 
-				Fold_String_Right(
-					Combined, #Accumulator, Included) and
-				#List = Included o List;
-			decreasing |List|;
-		do
-			Dequeue(Cur_Entry, List);
-			FoldIn(Accumulator, Cur_Entry);
-			Enqueue(Cur_Entry, Included);
-		end;
-
-		Included :=: List;
-
-	end Fold_Right;
-
-	Procedure Fold_Left(restores List : Queue; updates Accumulator : T);
-		
-	end Fold_Left;
-
-end Iterative_Fold_Realization;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Iterative_Inverting_Realiz.rb

@@ -1,26 +1,0 @@
-Realization Iterative_Inverting_Realiz for Inverting_Capability of Queue_Template;
-
-	Facility SF is Stack_Template(Entry, Max_Length)
-		realized by Array_Realiz;
-
-	Procedure Invert (updates Q: Queue);
-		Var S: SF.Stack;
-		Var Next_Entry: Entry;
-
-		While ( Is_Not_Zero(Length(Q)) )
-			maintaining Reverse(Q) o S = Reverse(#Q);
-			decreasing |Q|;
-		do
-			Dequeue(Next_Entry, Q);
-			Push(Next_Entry, S);
-		end;
-
-		While ( Is_Not_Zero(Depth(S)) )
-			maintaining Q o S = Reverse(#Q);
-			decreasing |S|;
-		do
-			Pop(Next_Entry, S);
-			Enqueue(Next_Entry, Q);
-		end;
-	end Invert;
-end Iterative_Inverting_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Multi_Set_Based_Selection_Sort_Realization.rb

@@ -1,60 +1,0 @@
-
-Realization Multi_Set_Based_Selection_Sort_Realization(
-			Operation Compare(restores E1, E2 : Entry) 
-				: Boolean;
-				requires Is_Total_Preordering(LEQV);
-				ensures Compare = LEQV(E1, E2);)
-		for Multi_Set_Based_Sorting_Capability of Queue_Template;
-	uses String_Theory, Multi_Set_Theory;
-	
-	(* Note: Under Construction! *)
-
-	Operation Remove_Min(updates Q : Queue; replaces Min : Entry);
-		requires |Q| /= 0;
-		ensures StringToMultiSet(Q o <Min>) = StringToMultiSet(#Q) and
-			Is_Universally_Related(LEQV, <Min>, Q) and
-			|Q| = |#Q| - 1;
-	Procedure
-		Var Considered_Entry : Entry;
-		Var New_Queue : Queue;
-
-		Dequeue(Min, Q);		
-		While (Length(Q) > 0)
-			changing Q, New_Queue, Min, Considered_Entry;
-			maintaining StringToMultiSet(New_Queue o Q o <Min>) =
-					StringToMultiSet(#Q) and
-				Is_Universally_Related(LEQV, <Min>, New_Queue);
-			decreasing |Q|;
-		do
-			Dequeue(Considered_Entry, Q);
-
-			if (Compare(Considered_Entry, Min)) then
-				Min :=: Considered_Entry;
-			end;
-	
-			Enqueue(Considered_Entry, New_Queue);
-		end;
-
-		New_Queue :=: Q;
-	end Remove_Min;
-
-	Procedure Sort(updates Q : Queue);
-		Var Sorted_Queue : Queue;
-		Var Lowest_Remaining : Entry;
-
-		While (Length(Q) > 0)
-			changing Q, Sorted_Queue, Lowest_Remaining;
-			maintaining StringToMultiSet(Q o Sorted_Queue) =
-					StringToMultiSet(#Q) and
-				Is_Conformal_With(LEQV, Sorted_Queue) and 
-				Is_Universally_Related(LEQV, Sorted_Queue, Q);
-			decreasing |Q|;
-		do
-			Remove_Min(Q, Lowest_Remaining);
-			Enqueue(Lowest_Remaining, Sorted_Queue);
-		end;
-
-		Q :=: Sorted_Queue;
-	end Sort;
-
-end Multi_Set_Based_Selection_Sort_Realization;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Recursive_Append_Realiz.rb

@@ -1,13 +1,0 @@
-Realization Recursive_Append_Realiz for Append_Capability of Queue_Template;
-    Recursive Procedure Append(updates P: Queue; clears Q: Queue);
-        decreasing |Q|;
-
-      Var E: Entry;
-      If ( Is_Not_Zero(Length(Q)) ) then
-          Dequeue(E,Q);
-          Enqueue(E,P);
-          Append(P,Q);
-      end;
-    end Append;
-
-end Recursive_Append_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Recursive_Inverting_Realiz.rb

@@ -1,12 +1,0 @@
-Realization Recursive_Inverting_Realiz for Inverting_Capability of Queue_Template;
-    Recursive Procedure Invert(updates Q: Queue);
-        decreasing |Q|;
-
-        Var E: Entry;
-        If ( Is_Not_Zero(Length(Q)) ) then
-            Dequeue(E, Q);
-            Invert(Q);
-            Enqueue(E, Q);
-        end;
-    end Invert;
-end Recursive_Inverting_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Remove_Last_Realiz.rb

@@ -1,16 +1,0 @@
-Realization Remove_Last_Realiz for Remove_Last_Capability of Queue_Template;
-    Procedure Remove_Last(updates Q: Queue; replaces E: Entry);
-        Var T: Queue;
-
-	  Dequeue (E, Q);
-        While (Length(Q) /= 0)
-          changing Q,T,E;
-          maintaining #Q = T o <E> o Q;
-          decreasing |Q|;
-        do
-          Enqueue(E,T);
-          Dequeue(E,Q);
-        end;
-	  Q :=: T;
-    end Remove_Last;
-end Remove_Last_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Selection_Sort_Realization.rb

@@ -1,51 +1,0 @@
-
-Realization Selection_Sort_Realization(
-			Operation Compare(restores E1, E2 : Entry) 
-				: Boolean;
-				ensures Compare = LEQV(E1, E2);)
-		for Sorting_Capability of Queue_Template;
-	uses String_Theory;
-
-	Procedure Sort(updates Q : Queue);
-		Var Sorted_Queue : Queue;
-		Var Lowest_Remaining : Entry;
-
-		While (Length(Q) > 0)
-			changing Q, Sorted_Queue, Lowest_Remaining;
-			maintaining Is_Permutation(Q o Sorted_Queue, #Q) and
-				Is_Conformal_With(LEQV, Sorted_Queue) and 
-				Is_Universally_Related(Sorted_Queue, Q, LEQV);
-			decreasing |Q|;
-		do
-			Remove_Min(Q, Lowest_Remaining);
-			Enqueue(Lowest_Remaining, Sorted_Queue);
-		end;
-		Q :=: Sorted_Queue;
-	end Sort;
-
-	Operation Remove_Min(updates Q : Queue; replaces Min : Entry);
-		requires |Q| /= 0;
-		ensures Is_Permutation(Q o <Min>, #Q) and
-			Is_Universally_Related(<Min>, Q, LEQV) and
-			|Q| = |#Q| - 1;
-	Procedure
-		Var Considered_Entry : Entry;
-		Var New_Queue : Queue;
-		Dequeue(Min, Q);		
-		While (Length(Q) > 0)
-			changing Q, New_Queue, Min, Considered_Entry;
-			maintaining Is_Permutation(
-					New_Queue o Q o <Min>, #Q) and
-				Is_Universally_Related(<Min>, New_Queue, LEQV);
-			decreasing |Q|;
-		do
-			Dequeue(Considered_Entry, Q);
-			if (Compare(Considered_Entry, Min)) then
-				Min :=: Considered_Entry;
-			end;	
-			Enqueue(Considered_Entry, New_Queue);
-		end;
-		New_Queue :=: Q;
-	end Remove_Min;
-
-end Selection_Sort_Realization;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Short_Queue_Reversal_Realiz.rb

@@ -1,8 +1,0 @@
-Realization Short_Queue_Reversal_Realiz for Short_Queue_Reversal_Capability of Queue_Template;
-    Procedure SQ_Reverse(updates Q: Queue);
-        Var Temp: Entry;
-
-        Dequeue(Temp, Q);
-        Enqueue(Temp, Q);
-    end SQ_Reverse;
-end Short_Queue_Reversal_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/SI_Stack_Template/SI_Array_Realiz.rb

@@ -1,33 +1,0 @@
-Realization SI_Array_Realiz for SI_Stack_Template;
-
-        Var Contents: Array 1..Max_Depth of Entry;
-        Var Top: Integer;
-        conventions
-            0 <= Top <= Max_Depth;
-        correspondence
-            Self = Reverse(Concatenation i: Integer
-            where 1 <= i <= Top, <Contents(i)>);
-
-    Procedure Push(alters E: Entry);
-        Top := Top + 1;
-        E :=: Contents[Top];
-    end Push;
-
-    Procedure Pop(replaces R: Entry); 
-        R :=: Contents[Top];
-        Top := Top - 1;
-    end Pop;
-
-    Procedure Depth(): Integer;
-        Depth := Top;
-    end Depth;
-
-    Procedure Rem_Capacity(): Integer;
-        Rem_Capacity := Max_Depth - Top;
-    end Rem_Capacity;
-
-    Procedure Clear();
-        Top := 0;
-    end Clear;
-
-end SI_Array_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Array_Realiz.c

@@ -1,87 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#include "Array_Realiz.h"
-
-typedef struct _Contents_Array_Fac_1 _Contents_Array_Fac_1;
-struct _Contents_Array_Fac_1 {
-    Static_Array_Template* core;
-};
-
-typedef struct Realization_Specific Realization_Specific;
-struct Realization_Specific {
-    _Contents_Array_Fac_1 _Contents_Array_Fac_1_Var;
-};
-
-typedef struct Stack_Instance Stack_Instance;
-struct Stack_Instance {
-    r_type_ptr Contents;
-    r_type_ptr Top;
-};
-
-static r_type_ptr createStack(type_info* StackType) {
-    Stack_Template* this = StackType->PointerToFacility;
-    Stack_Instance* Stack_i = calloc(1, sizeof(Stack_Instance));
-
-    _Contents_Array_Fac_1 _Contents_Array_Fac_1_Var = ((Realization_Specific*)
-        this->Realization_Specific)->_Contents_Array_Fac_1_Var;
-
-    Stack_i->Contents = _Contents_Array_Fac_1_Var.core->Static_Array->create(_Contents_Array_Fac_1_Var.core->Static_Array); 
-    Stack_i->Top = Std_Integer_Fac_Var.core->Integer->create(Std_Integer_Fac_Var.core->Integer); 
-    Stack_Instance** t = malloc(sizeof(Stack_Instance*));
-
-    *t = si;
-    return (r_type_ptr)t;
-}
-
-static void destroyStack(r_type_ptr r, type_info* StackType) {
-    Stack_Instance* Stack_i = *r;
-    Stack_Template* this = StackType->PointerToFacility;
-
-    _Contents_Array_Fac_1 _Contents_Array_Fac_1_Var = ((Realization_Specific*)
-            this->Realization_Specific)->_Contents_Array_Fac_1_Var;
-
-    _Contents_Array_Fac_1_Var.core->Static_Array->destroy(Stack_i->Contents,
-        _Contents_Array_Fac_1_Var.core->Static_Array); 
-    Std_Integer_Fac_Var.core->Integer->destroy(Stack_i->Top,
-        Std_Integer_Fac_Var.core->Integer); 
-    free(*r);
-    free(r);
-}
-static void Pop(r_type_ptr R, r_type_ptr S, Stack_Template* this) {
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Array_Realiz.h

@@ -1,16 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __ARRAY_REALIZ_H
-#define __ARRAY_REALIZ_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Concepts/Stack_Template/Stack_Template.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-
-extern Stack_Template* new_Array_Realiz_for_Stack_Template(type_info* Entry, r_type_ptr Max_Depth);
-extern void free_Array_Realiz_for_Stack_Template(Stack_Template* toFree);
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Array_Realiz.rb

@@ -1,65 +1,0 @@
-(*
- * This softare is released under the new BSD 2006 license.
- *
- * Note the new BSD license is equivalent to the MIT License, except for the
- * no-endorsement final clause.
- *
- * Copyright (c) 2007, Clemson University
- *
- * All rights reserved.
- *
- * Redistribution and use in source and binary forms, with or without
- * modification, are permitted provided that the following conditions are met:
- *
- *   * Redistributions of source code must retain the above copyright notice,
- *     this list of conditions and the following disclaimer.
- *   * Redistributions in binary form must reproduce the above copyright
- *     notice, this list of conditions and the following disclaimer in the
- *     documentation and/or other materials provided with the distribution.
- *   * Neither the name of the Clemson University nor the names of its
- *     contributors may be used to endorse or promote products derived from
- *     this software without specific prior written permission.
- *
- * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
- * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
- * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
- * A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER
- * OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
- * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO,
- * PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
- * PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
- * LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
- * NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
- * SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
- *
- * This sofware has been developed by past and present members of the
- * Reusable Sofware Research Groups (RSRG) at Clemson University and
- * The Ohio State University.
- *)
-
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Clean_Array_Realiz.rb

@@ -1,58 +1,0 @@
-Realization Clean_Array_Realiz for Stack_Template;
-
-    (* Note: Under Construction! *)
-
-    Definition Array_is_Clean(SR: Stack): B =
-        For all i: Integer, if SR.Top < i <= Max_Depth
-        then Entry.Is_Initial(SR.Contents(i));
-
-    Type Stack is represented by Record
-            Contents: Array 1..Max_Depth of Entry;
-            Top: Integer;
-        end;
-        convention
-            0 <= S.Top <= Max_Depth and Array_is_Clean(S);
-        correspondence
-            Conc.S = Reverse(Concatenation i: Z
-            where 1 <= i <= S.Top, <S.Contents(i)>);
-	end;
-
-    Procedure Push(alters E: Entry; updates S: Stack);
-        S.Top := S.Top + 1;
-        E :=: S.Contents[S.Top];
-    end Push;
-
-    Procedure Pop(replaces R: Entry; updates S: Stack);
-        Var Fresh_Val: Entry;
-
-        R :=: S.Contents[S.Top];
-        S.Contents[S.Top] :=: Fresh_Val;
-        S.Top := S.Top - 1; 
-    end Pop;
-
-    Procedure Depth(preserves S: Stack): Integer;
-        Depth := S.Top;
-    end Depth;
-
-    Procedure Rem_Capacity(preserves S: Stack): Integer;
-        Rem_Capacity := Max_Depth - S.Top;
-    end Rem_Capacity;
-	
-    Operation Clear_Entry(clears E: Entry);
-    Procedure
-		Var Temp: Entry;
-		E :=: Temp;
-    end Clear_Entry;
-	
-    Procedure Clear(clears S: Stack);
-      While (S.Top > 0)  
-		changing S;
-      	maintaining Array_is_Clean(S);
-      	decreasing S.Top;
-      do
-        Clear_Entry(S.Contents[S.Top]);
-        S.Top := S.Top - 1;
-      end;
-    end Clear;
-
-end Clean_Array_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Clear_2_Realiz.rb

@@ -1,9 +1,0 @@
-Realization Clear_2_Realiz for Clear_2_Capability of Stack_Template;
-
-	Procedure Clear_2(updates S: Stack);
-		Var Next_Entry: Entry;
-
-		Pop(Next_Entry, S);
-		Pop(Next_Entry, S);
-	end Clear_2;
-end Clear_2_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Clear_3_Realiz.rb

@@ -1,10 +1,0 @@
-Realization Clear_3_Realiz for Clear_3_Capability of Stack_Template;
-
-	Procedure Clear_3(clears S: Stack);
-		Var Next_Entry: Entry;
-
-		Pop(Next_Entry, S);
-		Pop(Next_Entry, S);
-		Pop(Next_Entry, S);
-	end Clear_3;
-end Clear_3_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Defn_Do_Nothing_Realiz.rb

@@ -1,8 +1,0 @@
-Realization Defn_Do_Nothing_Realiz for Defn_Do_Nothing_Capability of Stack_Template;
-	Procedure Do_Nothing(updates S: Stack);
-		Var Next_Entry: Entry;
-
-		Pop(Next_Entry, S);
-		Push(Next_Entry, S);
-	end Do_Nothing;
-end Defn_Do_Nothing_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Do_Nothing_Realiz.rb

@@ -1,8 +1,0 @@
-Realization Do_Nothing_Realiz for Do_Nothing_Capability of Stack_Template;
-	Procedure Do_Nothing(restores S: Stack);
-		Var Next_Entry: Entry;
-
-		Pop(Next_Entry, S);
-		Push(Next_Entry, S);
-	end Do_Nothing;
-end Do_Nothing_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Init_Array_Realiz.rb

@@ -1,41 +1,0 @@
-Realization Init_Array_Realiz for Stack_Template;
-
-    (* Note: Under Construction! *)
-
-    Type Stack is represented by Record
-            Contents: Array 1..Max_Depth of Entry;
-            Top: Integer;
-        end;
-        convention
-            1 <= S.Top <= Max_Depth+1;
-        correspondence
-            Conc.S = Reverse(Concatenation i: Integer
-            where 1 <= i <= S.Top-1, <S.Contents(i)>);
-        initialization
-           S.Top := 1;
-        end;
-	end;
-	
-    Procedure Push(alters E: Entry; updates S: Stack);
-        E :=: S.Contents[S.Top];
-        S.Top := S.Top + 1;
-    end Push;
-
-    Procedure Pop(replaces R: Entry; updates S: Stack); 
-        S.Top := S.Top - 1;
-        R :=: S.Contents[S.Top];
-    end Pop;
-
-    Procedure Depth(preserves S: Stack): Integer;
-        Depth := S.Top-1;
-    end Depth;
-
-    Procedure Rem_Capacity(preserves S: Stack): Integer;
-        Rem_Capacity := Max_Depth + 1 - S.Top;
-    end Rem_Capacity;
-
-    Procedure Clear(clears S: Stack);
-        S.Top := 1;
-    end Clear;
-
-end Init_Array_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Int_Assign_Clear_2_Realiz.rb

@@ -1,18 +1,0 @@
-Realization Int_Assign_Clear_2_Realiz for Clear_2_Capability of Stack_Template;
-
-	Procedure Clear_2(updates S: Stack);
-		Var Next_Entry: Entry;
-		Var D, I: Integer;
-
-		I := 1;
-		D := Sum(Depth(S), I);
-		While (Are_Not_Equal(I, D))
-			changing I, Next_Entry, S;
-			maintaining (|S| = (D - I));
-			decreasing D - I;
-		do
-			Pop(Next_Entry, S);
-			Increment(I);
-		end;
-	end Clear_2;
-end Int_Assign_Clear_2_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Obvious_CC_Realiz.rb

@@ -1,35 +1,0 @@
-Realization Obvious_CC_Realiz
-(
-    operation Copy_Entry(replaces Copy: Entry; restores Orig: Entry);
-        ensures Copy = Orig;
-
-    ) 
-for Copying_Capability of Stack_Template;
-
-    Procedure Copy_Stack(replaces S_Copy: Stack; restores S_Orig: Stack);
-        Var Next_Entry, Entry_Copy: Entry;
-        Var S_Reversed: Stack;
-
-        While (Depth(S_Orig) /= 0)
-		changing Next_Entry, S_Orig, S_Reversed;
-            maintaining #S_Orig = Reverse(S_Reversed) o S_Orig;
-            decreasing |S_Orig|;
-        do
-            Pop(Next_Entry, S_Orig);
-            Push(Next_Entry, S_Reversed);
-        end;
-        Clear(S_Copy);
-        While (Depth(S_Reversed) /= 0)
-		changing Entry_Copy, Next_Entry, S_Copy, S_Orig, S_Reversed;
-            maintaining S_Copy = S_Orig and
-                        #S_Orig = Reverse(S_Reversed) o S_Orig;
-            decreasing |S_Reversed|;
-        do
-            Pop(Next_Entry, S_Reversed);
-            Copy_Entry(Entry_Copy, Next_Entry);
-            Push(Next_Entry, S_Orig);
-            Push(Entry_Copy, S_Copy);
-        end;
-    end Copy_Stack;
-
-end Obvious_CC_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Obvious_Flipping_Realiz.rb

@@ -1,15 +1,0 @@
-Realization Obvious_Flipping_Realiz for Flipping_Capability of Stack_Template;
-	Procedure Flip(updates S: Stack);
-		Var Temp: Stack;
-		Var Next_Entry: Entry;
-
-		While (Depth(S) /= 0)
-			maintaining #S = Reverse(Temp) o S;
-			decreasing |S|;
-		do
-			Pop(Next_Entry, S);
-			Push(Next_Entry, Temp);
-		end;
-		Temp :=: S;
-	end Flip;
-end Obvious_Flipping_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Obvious_Reading_Realiz.rb

@@ -1,21 +1,0 @@
-Realization Obvious_Reading_Realiz (Operation Read_Entry(replaces E: Entry);)
-		for Reading_Capability of Stack_Template;
-
-	Procedure Read_upto(replaces S: Stack; preserves Count: Integer);
-		Var Next_Entry: Entry;
-
-		Clear(S);
-		While (Depth(S) /= Count)
-			changing S, Next_Entry;
-			maintaining |S| <= Count;
-			decreasing (Count - |S|);
-		do
-			Read_Entry(Next_Entry);
-			Push(Next_Entry, S);
-		end;
-	end Read_upto;
-
-	Procedure Read(replaces S: Stack);
-		Read_upto(S, Max_Depth);
-	end Read;
-end Obvious_Reading_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Obvious_Writing_Realiz.rb

@@ -1,16 +1,0 @@
-Realization Obvious_Writing_Realiz (Operation Write_Entry(evaluates E: Entry);)
-		for Writing_Capability of Stack_Template;
-
-	Procedure Write(clears S: Stack);
-		Var Next_Entry: Entry;
-
-		While (Depth(S) /= 0)
-			changing S, Next_Entry;
-			maintaining true;
-			decreasing |S|;
-		do
-			Pop(Next_Entry, S);
-			Write_Entry(Next_Entry);
-		end;
-	end Write;
-end Obvious_Writing_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Stack_Template.h

@@ -1,22 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __STACK_TEMPLATE_H
-#define __STACK_TEMPLATE_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-
-typedef struct Stack_Template Stack_Template;
-struct Stack_Template {
-    void* Realization_Specific;
-    type_info* Stack;
-    void (*Push) (r_type_ptr, r_type_ptr, Stack_Template*);
-    void (*Pop) (r_type_ptr, r_type_ptr, Stack_Template*);
-    r_type_ptr (*Depth) (r_type_ptr, Stack_Template*);
-    r_type_ptr (*Rem_Capacity) (r_type_ptr, Stack_Template*);
-    void (*Clear) (r_type_ptr, Stack_Template*);
-};
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Boolean_Template/Boolean_Template.h

@@ -1,29 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __BOOLEAN_TEMPLATE_H
-#define __BOOLEAN_TEMPLATE_H
-
-#include "../../../../RESOLVE.h"
-
-typedef struct Boolean_Template Boolean_Template;
-struct Boolean_Template {
-    void* Realization_Specific;
-    type_info* Boolean;
-    r_type_ptr (*True) (Boolean_Template*);
-    r_type_ptr (*False) (Boolean_Template*);
-    r_type_ptr (*And) (r_type_ptr, r_type_ptr, Boolean_Template*);
-    r_type_ptr (*Or) (r_type_ptr, r_type_ptr, Boolean_Template*);
-    r_type_ptr (*Not) (r_type_ptr, Boolean_Template*);
-    r_type_ptr (*Are_Equal) (r_type_ptr, r_type_ptr, Boolean_Template*);
-    r_type_ptr (*Are_Not_Equal) (r_type_ptr, r_type_ptr, Boolean_Template*);
-    r_type_ptr (*Replica) (r_type_ptr, Boolean_Template*);
-	void (*assign) (r_type_ptr, r_type_ptr, Boolean_Template*);
-	void (*Read) (r_type_ptr, Boolean_Template*);
-    void (*Write) (r_type_ptr, Boolean_Template*);
-    void (*Write_Line) (r_type_ptr, Boolean_Template*);
-    r_type_ptr (*createFromBoolean) (int, type_info*);
-	r_type_ptr (*createBoolean) (type_info*);
-};
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Boolean_Template/Std_Boolean_Realiz.c

@@ -1,144 +1,0 @@
-#include "Boolean_Template.h"
-
-static int ValueOf(r_type_ptr r) {
-    return **(int**)r;
-}
-
-static r_type_ptr createFromBoolean(int I, type_info* ti) {
-	int *space = scalloc(1, sizeof(int));
-	*space = I;
-	int** ret = salloc(sizeof(int*));
-	*ret = space;
-	return (r_type_ptr)ret;
-}
-
-static r_type_ptr createBoolean(type_info* ti) {
-    int* t = scalloc(1, sizeof(int));
-	*t = 0;
-    int** ret = salloc(sizeof(int*));
-    *ret = t;
-    return (r_type_ptr)ret;
-}
-
-static void destroyBoolean (r_type_ptr r, type_info* ti) {
-    sfree(*r);
-    sfree(r);
-}
-
-static type_info* newBoolean() {
-    type_info* pc = scalloc(1, sizeof(type_info));
-    pc->create = createBoolean;
-    pc->destroy = destroyBoolean;
-    return pc;
-}
-
-static r_type_ptr True(Boolean_Template* this) {
-	int *space = scalloc(1, sizeof(int));
-	*space = 1;
-	int** ret = salloc(sizeof(int*));
-	*ret = space;
-	return (r_type_ptr)ret;
-}
-
-static r_type_ptr False(Boolean_Template* this) {
-	int *space = scalloc(1, sizeof(int));
-	*space = 0;
-	int** ret = salloc(sizeof(int*));
-	*ret = space;
-	return (r_type_ptr)ret;
-}
-
-static r_type_ptr And(r_type_ptr b1, r_type_ptr b2, Boolean_Template* this) {
-	int *space = scalloc(1, sizeof(int));
-	*space = ((**(int**)b1 == 1) && (**(int**)b2 == 1));
-
-	int** ret = salloc(sizeof(int*));
-	*ret = space;
-	return (r_type_ptr)ret;
-}
-
-static r_type_ptr Or(r_type_ptr b1, r_type_ptr b2, Boolean_Template* this) {
-	int *space = scalloc(1, sizeof(int));
-	*space = ((**(int**)b1 == 1) || (**(int**)b2 == 1));
-
-	int** ret = salloc(sizeof(int*));
-	*ret = space;
-	return (r_type_ptr)ret;
-}
-
-static r_type_ptr Not(r_type_ptr b1, Boolean_Template* this) {
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Boolean_Template/Std_Boolean_Realiz.h

@@ -1,9 +1,0 @@
-#ifndef __STD_BOOLEAN_REALIZ_H
-#define __STD_BOOLEAN_REALIZ_H
-
-#include "Boolean_Template.h"
-
-extern Boolean_Template* new_Std_Boolean_Realiz_for_Boolean_Template();
-extern void free_Std_Boolean_Realiz_for_Boolean_Template(Boolean_Template* toFree);
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Integer_Template/Integer_Template.h

@@ -1,47 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __INTEGER_TEMPLATE_H
-#define __INTEGER_TEMPLATE_H
-
-#include "../../../../RESOLVE.h"
-#include "../../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-
-typedef struct Integer_Template Integer_Template;
-struct Integer_Template {
-
-    void* Realization_Specific;
-    type_info* Integer;
-    r_type_ptr (*Is_Zero) (r_type_ptr, Integer_Template*);
-    r_type_ptr (*Is_Not_Zero) (r_type_ptr, Integer_Template*);
-    void (*Increment) (r_type_ptr, Integer_Template*);
-    void (*Decrement) (r_type_ptr, Integer_Template*);
-    r_type_ptr (*Less_Or_Equal) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Less) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Greater) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Greater_Or_Equal) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Sum) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Negate) (r_type_ptr, Integer_Template*);
-    r_type_ptr (*Difference) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Product) (r_type_ptr, r_type_ptr, Integer_Template*);
-/*    r_type_ptr (*Power) (r_type_ptr, r_type_ptr, Integer_Template*);
-    void (*Divide) (r_type_ptr, r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Mod) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Rem) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Quotient) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Div) (r_type_ptr, r_type_ptr, Integer_Template*);
-    r_type_ptr (*Are_Equal) (r_type_ptr, r_type_ptr, Integer_Template*);
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Integer_Template/Std_Integer_Realiz.c

@@ -1,214 +1,0 @@
-#include <limits.h>
-#include "Integer_Template.h"
-
-static int ValueOf(r_type_ptr r) {
-    return **((int**)r);
-}
-
-static r_type_ptr createFromInteger(int I, type_info* ti) {
-	int *space = scalloc(1, sizeof(int));
-	*space = I;
-	int** ret = salloc(sizeof(int*));
-	*ret = space;
-	return (r_type_ptr)ret;
-}
-
-static r_type_ptr createInteger(type_info* ti) {
-    int* t = scalloc(1, sizeof(int));
-    *t = 0;
-    int** ret = salloc(sizeof(int*));
-    *ret = t;
-    return (r_type_ptr)ret;
-}
-
-static void destroyInteger (r_type_ptr r, type_info* ti) {
-	sfree(*r);
-    sfree(r);
-}
-
-static type_info* newInteger() {
-    type_info* pc = scalloc(1, sizeof(type_info));
-    pc->create = createInteger;
-    pc->destroy = destroyInteger;
-    return pc;
-}
-
-static r_type_ptr Is_Zero(r_type_ptr i, Integer_Template* this) {
-	int *space = scalloc(1, sizeof(int));
-	*space = (**(int**)i == 0);
-
-	int** ret = salloc(sizeof(int*));
-	*ret = space;
-	return (r_type_ptr)ret;
-}
-
-static r_type_ptr Is_Not_Zero(r_type_ptr i, Integer_Template* this) {
-	int *space = scalloc(1, sizeof(int));
-	*space = (**(int**)i != 0);
-
-	int** ret = salloc(sizeof(int*));
-	*ret = space;
-	return (r_type_ptr)ret;
-}
-
-static void Increment(r_type_ptr i, Integer_Template* this) {
-	**(int**)i = **(int**)i + 1;
-}
-
-static void Decrement(r_type_ptr i, Integer_Template* this) {
-	**(int**)i = **(int**)i - 1;
-}
-
-static r_type_ptr Less_Or_Equal(r_type_ptr i1, r_type_ptr i2, Integer_Template* this) {
-	int *space = scalloc(1, sizeof(int));
-	*space = ((**(int**)i1 <= (**(int**)i2)));
-
-	int** ret = salloc(sizeof(int*));
-	*ret = space;
-	return (r_type_ptr)ret;
-}
-
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Integer_Template/Std_Integer_Realiz.h

@@ -1,9 +1,0 @@
-#ifndef __STD_INTEGER_REALIZ_H
-#define __STD_INTEGER_REALIZ_H
-
-#include "Integer_Template.h"
-
-extern Integer_Template* new_Std_Integer_Realiz_for_Integer_Template();
-extern void free_Std_Integer_Realiz_for_Integer_Template(Integer_Template* toFree);
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Static_Array_Template/Alt_Bin_Search_Realiz.rb

@@ -1,65 +1,0 @@
-Realization Alt_Bin_Search_Realiz (
-	Operation Are_Ordered(restores x,y: Entry): Boolean;
-		ensures Are_Ordered = true;
-) for Alt_Search_Capability of Static_Array_Template;
-
-(*
-    Operation Are_Ordered(restores x,y: Entry): Boolean;
-         ensures Are_Ordered = true;
-    Procedure 
-	Are_Ordered := True();
-    end; 
-
-
-    Operation Are_Equal(restores x, y: Entry): Boolean;
-	ensures Are_Equal = (x = y);
-    Procedure 
-	Are_Equal := And(Are_Ordered(x, y), Are_Ordered(y, x));
-    end; 
-*)
-
-    Procedure binarySearch(restores key: Entry; restores A: Static_Array; replaces result: Integer);
-	Var one, two: Integer;
-	Var low, mid, high: Integer;
-	Var midVal: Entry;
-	Var found: Boolean;
-(*
-	Increment(one);
-	Increment(two);
-	Increment(two);
-*)
-	found := False();
-	low := Replica(Lower_Bound);
-	high := Replica(Upper_Bound);
-
-	While (low <= high and not found)
-		changing low, mid, high, A, midVal, found;
-		maintaining true;
-		decreasing (high - low);
-	do
-		mid := Sum(low, high);
-		mid := Div(mid, 2);
-(*
-		Divide(Difference(high, low), two, mid);	-- this is really the quotient
-		mid := Sum(low, mid);
-*)
-		Swap_Entry(A, midVal, mid);
-		if (Are_Ordered(midVal, key) and Are_Ordered(key, midVal)) then
-			found := True();
-			Increment(low);				-- this is to satisfy the progress metric
-		else
-			if (Are_Ordered(midVal, key)) then
-				low := Sum(mid, 1);
-			else
-				high := Difference(mid, 1);
-			end;
-		end;
-		Swap_Entry(A, midVal, mid);
-	end;
-	If (found) then
-		result := Replica(mid);
-	else
-		result := Negate(Sum(Lower_Bound, 1));
-	end;	
-    end binarySearch;
-end Alt_Bin_Search_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Static_Array_Template/Bin_Search_Realiz.rb

@@ -1,45 +1,0 @@
-Realization Bin_Search_Realiz(
-      operation Are_Ordered(restores x,y: Entry): Boolean;
-         ensures Are_Ordered = (LEQ(x,y));
-      )for Search_Capability of Static_Array_Template;
-
-    Operation Are_Equal(restores x, y: Entry): Boolean;
-	ensures Are_Equal = (x = y);
-    Procedure 
-	Are_Equal := And(Are_Ordered(x, y), Are_Ordered(y, x));
-    end; 
-
-    Procedure Is_Present(restores key: Entry; restores A: Static_Array): Boolean;
-	Var low, mid, high, one, two: Integer;
-	Var midVal: Entry;
-
-	Increment(one);
-	Increment(two);
-	Increment(two);
-
-	Is_Present := False();
-	low := Replica(Lower_Bound);
-	high := Replica(Upper_Bound);
-
-	While (low <= high)
-		changing low, mid, high, A, midVal, Is_Present;
-		maintaining true;
-		decreasing (high - low);
-	do
-		Divide(Difference(high, low), two, mid);	-- this is really the quotient
-		mid := Sum(low, mid);
-		Swap_Entry(A, midVal, mid);
-		if (Are_Equal(midVal, key)) then
-			Is_Present := True();
-			low := Sum(high, one);
-		else
-			if (Are_Ordered(midVal, key)) then
-				low := Sum(mid, one);
-			else
-				high := Difference(mid, one);
-			end;
-		end;
-		Swap_Entry(A, midVal, mid);
-	end;	
-    end Is_Present;
-end Bin_Search_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Static_Array_Template/Bool_Bin_Search_Realiz.rb

@@ -1,59 +1,0 @@
-Realization Bool_Bin_Search_Realiz (
-	Operation Are_Ordered(restores x,y: Entry): Boolean;
-		ensures Are_Ordered = true;
-) for Bool_Search_Capability of Static_Array_Template;
-
-(*
-    Operation Are_Ordered(restores x,y: Entry): Boolean;
-         ensures Are_Ordered = True;
-    Procedure 
-	Are_Ordered := True();
-    end; 
-
-
-    Operation Are_Equal(restores x, y: Entry): Boolean;
-	ensures Are_Equal = (x = y);
-    Procedure 
-	Are_Equal := And(Are_Ordered(x, y), Are_Ordered(y, x));
-    end; 
-*)
-
-    Procedure binarySearch(restores key: Entry; restores A: Static_Array; replaces result: Boolean);
-	Var one, two: Integer;
-	Var low, mid, high: Integer;
-	Var midVal: Entry;
-(*
-	Increment(one);
-	Increment(two);
-	Increment(two);
-*)
-	result := False();
-	low := Replica(Lower_Bound);
-	high := Replica(Upper_Bound);
-
-	While (low <= high and not result)
-		changing low, mid, high, A, midVal, result;
-		maintaining true;
-		decreasing (high - low);
-	do
-		mid := Sum(low, high);
-		mid := Div(mid, 2);
-(*
-		Divide(Difference(high, low), two, mid);	-- this is really the quotient
-		mid := Sum(low, mid);
-*)
-		Swap_Entry(A, midVal, mid);
-		if (Are_Ordered(midVal, key) and Are_Ordered(key, midVal)) then
-			result := True();
---			Increment(low);				-- this is to satisfy the progress metric
-		else
-			if (Are_Ordered(midVal, key)) then
-				low := Sum(mid, 1);
-			else
-				high := Difference(mid, 1);
-			end;
-		end;
-		Swap_Entry(A, midVal, mid);
-	end;
-    end binarySearch;
-end Bool_Bin_Search_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Static_Array_Template/Shifting_Realiz.rb

@@ -1,20 +1,0 @@
-Realization Shifting_Realiz for Shifting_Capability of Static_Array_Template;
-
-    Procedure Shift_All(updates A: Static_Array);
-	Var Temp: Entry;
-	Var i, one: Integer;
-
-	Increment(one);
---	i := Replica(Lower_Bound);
-	While (i < Upper_Bound)
-		changing A, i, Temp;
-		maintaining Lower_Bound <= i;
-		decreasing (Upper_Bound - i);
-	do
-		Swap_Entry(A, Temp, i);
-		Swap_Entry(A, Temp, Sum(i, one));
-		Swap_Entry(A, Temp, i);
-		Increment(i);
-	end;	
-    end Shift_All;
-end Shifting_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Text_Template/Queue_Based_Realiz.rb

@@ -1,28 +1,0 @@
-Realization Queue_Based_Realiz for Text_Template;
-    uses Queue_Template;
-
-    -- the bound below is not right, so this implementation won't verify
-    Facility QF is Queue_Template(Character, 100)
-        realized by Circular_Array_Realiz;
-
-    Type Text = Record
-			Contents: QF. Queue;
-		end;
-		correspondence Conc.S = S.Contents;
-	end;
- 
-    Procedure Add(restores C: Character; updates S: Text);
-        Var Temp: Character;
-
-        Temp := Replica(C);
-        Enqueue(Temp, S.Contents);
-    end Add;
-
-    Procedure Remove(updates C: Character; updates S: Text);
-        Dequeue(C, S.Contents);
-    end Remove;
-
-    Procedure Is_Empty(restores S: Text): Boolean;
-        Is_Empty := Length(S.Contents);
-    end Is_Empty;
-end Queue_Based_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/General_Examples/Int_Do_Nothing_Exercise.c

@@ -1,31 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#include "Int_Do_Nothing_Exercise.h"
-
-void Int_Do_Nothing_Exercise_create() {
-	Std_Boolean_Fac_create();
-	Std_Integer_Fac_create();
-}
-
-void Int_Do_Nothing_Exercise_destroy() {
-    Std_Boolean_Fac_destroy();
-    Std_Integer_Fac_destroy();
-}
-
-void Do_Nothing(r_type_ptr I) {
-
-}
-
-void Main() {
-	r_type_ptr X = Std_Integer_Fac_Var.core->Integer->create(Std_Integer_Fac_Var.core->Integer);
-
-}
-
-int main() {
-    Int_Do_Nothing_Exercise_create();
-    Main();
-    Int_Do_Nothing_Exercise_destroy();
-    return 0;
-}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/General_Examples/Int_Do_Nothing_Exercise.h

@@ -1,17 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __INT_DO_NOTHING_EXERCISE_H
-#define __INT_DO_NOTHING_EXERCISE_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Concepts/Standard/Static_Array_Template/Static_Array_Template.h"
-#include "../../../Main/Concepts/Standard/Location_Linking_Template_1/Location_Linking_Template_1.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-
-void Int_Do_Nothing_Exercise_create();
-void Int_Do_Nothing_Exercise_destroy();
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Led_Examples/Leds_Test.c

@@ -1,51 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#include "Leds_Test.h"
-void Leds_Test_create() {
-	Std_Boolean_Fac_create();
-	Std_Integer_Fac_create();
- 	Std_Clock_Fac_create();
- 	r_type_ptr __arg_0 = Std_Integer_Fac_Var.core->createFromInteger(4,Std_Integer_Fac_Var.core->Integer);
-	Led_Facility_Var.core = new_Std_Leds_Realiz_for_Leds_Template(__arg_0);
-	Led_Facility_Var.Toggling_Capability = new_Toggling_Realiz_for_Toggling_Capability_of_Leds_Template(
-											Led_Facility_Var.core);
-	Std_Integer_Fac_Var.core->Integer->destroy(__arg_0, Std_Integer_Fac_Var.core->Integer);
-}
-
-void Leds_Test_destroy() {
-    free_Std_Leds_Realiz_for_Leds_Template(Led_Facility_Var.core);
-    Std_Boolean_Fac_destroy();
-    Std_Integer_Fac_destroy();
-}
-
-void Main() {
-	r_type_ptr this = Led_Facility_Var.core->Led->create(Led_Facility_Var.core->Led);
-	r_type_ptr b = Std_Boolean_Fac_Var.core->createFromBoolean(1, Std_Boolean_Fac_Var.core->Boolean);
-	r_type_ptr i = Std_Integer_Fac_Var.core->createFromInteger(0, Std_Integer_Fac_Var.core->Integer);
-	r_type_ptr i2 = Std_Integer_Fac_Var.core->createFromInteger(1, Std_Integer_Fac_Var.core->Integer);
-	r_type_ptr i3 = Std_Integer_Fac_Var.core->createFromInteger(2, Std_Integer_Fac_Var.core->Integer);
-	
-	while(**(int**)b) {
-		Led_Facility_Var.Toggling_Capability->Toggle(this, i, Led_Facility_Var.Toggling_Capability);
-		Std_Clock_Fac_Var.core->Wait_500_Milli_Seconds(Std_Clock_Fac_Var.core);
-		Led_Facility_Var.Toggling_Capability->Toggle(this, i2, Led_Facility_Var.Toggling_Capability);
-		Std_Clock_Fac_Var.core->Wait_500_Milli_Seconds(Std_Clock_Fac_Var.core);
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Led_Examples/Leds_Test.h

@@ -1,25 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __LEDS_TEST_H
-#define __LEDS_TEST_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Clock_Fac.h"
-#include "../../../Main/Concepts/Leds_Template/Leds_Template.h"
-#include "../../../Main/Concepts/Leds_Template/Std_Leds_Realiz.h"
-#include "../../../Main/Concepts/Leds_Template/Toggling_Realiz.h"
-
-typedef struct Led_Facility Led_Facility;
-struct Led_Facility {
-    Leds_Template* core;
-	Toggling_Capability_for_Leds_Template* Toggling_Capability;
-};
-Led_Facility Led_Facility_Var;
-void Leds_Test_create();
-void Leds_Test_destroy();
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Led_Examples/naive_malloc.c

@@ -1,220 +1,0 @@
-#ifdef DEBUG
-#include <stdio.h>
-#endif
-
-#include "naive_malloc.h"
-
-#define MAX_MEM 4096
-#define align4(x) (((((x)-1)>>2)<<2)+4)
-
-static void *stack[MAX_MEM];
-static void *base = NULL;
-static void *cur_brk = (void*)&stack[0];
-
-typedef struct block_t *block;
-
-struct block_t
-{
-	size_t size;
-	block next;
-	block prev;
-	int free;
-	int pad;
-	void *ptr;
-	char data[1];
-};
-
-
-#define BLOCK_SIZE (sizeof(struct block_t)-sizeof(char*))
-
-block get_block(void *p);
-int valid_addr(void *p);
-block fusion(block b);
-
-void split_block(block b, size_t size) 
-{
-	block new_block;
-	new_block = (void*)b->data + size;
-	new_block->size = b->size - size - BLOCK_SIZE;
-	new_block->free = 1;
-	b->size = size;
-	b->next = new_block;	
-	new_block->next = b->next;
-	new_block->prev = b;
-	new_block->ptr = new_block->data;
-}
-
-block find_block(block *last, size_t size) 
-{
-	block b = base;
-	while(b && !(b->free && b->size >= (size))) {
-		*last = b;
-		b = b->next;
-	}
-
-	return b;
-}
-
-void *stack_sbrk(int n)
-{
-	cur_brk += n;
-	if(cur_brk > (void*)&stack[MAX_MEM-1]) {
-		return (void*)-1;
-	}
-	return (void*)(cur_brk);		
-}
-
-void stack_brk(void *ptr)
-{
-	cur_brk = ptr;
-}
-
-block extend_stack(block last, size_t size)
-{
-	block b;
-	b = stack_sbrk(0);
-	if(stack_sbrk(BLOCK_SIZE + size) == (void*)-1) {
-		return NULL;
-	}
-	b->size = size;
-	b->next = NULL;
-	b->ptr = b->data;
-	if(last) {
-		last->next = b;
-		b->prev = last;
-	}
-	b->free = 0;
-	return b;
-}
-
-void *scalloc(int n, size_t size) {
-	size_t *new;
-	size_t s4, i;
-	new = salloc(n * size);
-	if(new) {
-		s4 = align4(n * size) << 2;
-		for(i = 0; i < s4; i++) {
-			new[i] = 0;
-		}
-	}
-	return (void*)new;
-}
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Led_Examples/naive_malloc.h

@@ -1,11 +1,0 @@
-#ifndef __NAIVE_MALLOC_H__
-#define __NAIVE_MALLOC_H__
-
-#include <stdlib.h>
-
-void *salloc(size_t size);
-void *scalloc(int n, size_t size);
-void sfree(void *ptr);
-void examine_blocks();
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Stack_Examples/Alt_Rev_Stack.c

@@ -1,36 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#include "Alt_Rev_Stack.h"
-
-void Alt_Rev_Stack_create() {
-	Std_Boolean_Fac_create();
-	Std_Integer_Fac_create();
-    Stack_Fac.core = new_Array_Realiz_for_Stack_Template();
-    Stack_Fac.Writing_Capability = new_Obvious_Writing_Realiz_for_Writing_Capability_for_Stack_Template(Stack_Fac.core);
-    Stack_Fac.Reading_Capability = new_Obvious_Reading_Realiz_for_Reading_Capability_for_Stack_Template(Stack_Fac.core);
-}
-
-void Alt_Rev_Stack_destroy() {
-    free_Array_Realiz_for_Stack_Template(Stack_Fac.core);
-    free(Stack_Fac.Writing_Capability);
-    free(Stack_Fac.Reading_Capability);
-    Std_Boolean_Fac_destroy();
-    Std_Integer_Fac_destroy();
-}
-
-void Main() {
-	r_type_ptr S1 = Stack_Fac.core->Stack->create(Stack_Fac.core->Stack);
-	r_type_ptr S2 = Stack_Fac.core->Stack->create(Stack_Fac.core->Stack);
-
-	Stack_Fac.core->Stack->destroy(S1, Stack_Fac.core->Stack); 
-	Stack_Fac.core->Stack->destroy(S2, Stack_Fac.core->Stack); 
-}
-
-int main() {
-    Alt_Rev_Stack_create();
-    Main();
-    Alt_Rev_Stack_destroy();
-    return 0;
-}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Stack_Examples/Alt_Rev_Stack.h

@@ -1,22 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __ALT_REV_STACK_H
-#define __ALT_REV_STACK_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-
-typedef struct Stack_Fac Stack_Fac;
-struct Stack_Fac {
-    Stack_Template* core;
-    Reading_Capability_for_Stack_Template* Reading_Capability;
-    Writing_Capability_for_Stack_Template* Writing_Capability;
-};
-Stack_Fac __Stack_Fac_Var;
-void Alt_Rev_Stack_create();
-void Alt_Rev_Stack_destroy();
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Standard/Std_Boolean_Fac.c

@@ -1,18 +1,0 @@
-#include "Std_Boolean_Fac.h"
-
-int Std_Boolean_Fac_INSTANCE = 0;
-
-//If our facility has already been created, we don't want a new copy.
-void Std_Boolean_Fac_create() {
-	if (Std_Boolean_Fac_INSTANCE == 0) {
-		Std_Boolean_Fac_Var.core = new_Std_Boolean_Realiz_for_Boolean_Template();
-		Std_Boolean_Fac_INSTANCE = 1;
-	}
-}
-
-void Std_Boolean_Fac_destroy() {
-	if (Std_Boolean_Fac_INSTANCE == 1) {
-		free_Std_Boolean_Realiz_for_Boolean_Template(Std_Boolean_Fac_Var.core);
-		Std_Boolean_Fac_INSTANCE = 0;
-	}
-}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Standard/Std_Boolean_Fac.h

@@ -1,16 +1,0 @@
-#ifndef __STD_BOOLEAN_FAC_H
-#define __STD_BOOLEAN_FAC_H
-
-#include "../../../RESOLVE.h"
-#include "../../Concepts/Standard/Boolean_Template/Std_Boolean_Realiz.h"
-
-typedef struct Std_Boolean_Fac Std_Boolean_Fac;
-struct Std_Boolean_Fac {
-	Boolean_Template* core;
-};
-Std_Boolean_Fac Std_Boolean_Fac_Var;
-
-void Std_Boolean_Fac_create();
-void Std_Boolean_Fac_destroy();
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Standard/Std_Clock_Fac.c

@@ -1,20 +1,0 @@
-#include "Std_Clock_Fac.h"
-
-int Std_Clock_Fac_INSTANCE = 0;
-
-//If our facility has already been created, we don't want a new copy.
-void Std_Clock_Fac_create() {
-	if (Std_Clock_Fac_INSTANCE == 0) {
-		Std_Clock_Fac_Var.core = new_Std_Clock_Realiz_for_Clock_Template();
-		Std_Clock_Fac_INSTANCE = 1;
-	}
-}
-
-void Std_Clock_Fac_destroy() {
-	if (Std_Clock_Fac_INSTANCE == 1) {
-		free_Std_Clock_Realiz_for_Clock_Template(Std_Clock_Fac_Var.core);
-		Std_Clock_Fac_INSTANCE = 0;
-	}
-}
-
-

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Standard/Std_Clock_Fac.h

@@ -1,22 +1,0 @@
-/*
- * Generated by the RESOLVE to C translator. This file
- * should not be modified.
- */
-#ifndef __STD_CLOCK_FAC_H
-#define __STD_CLOCK_FAC_H
-
-#include "../../../RESOLVE.h"
-#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
-#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
-#include "../../../Main/Concepts/Clock_Template/Clock_Template.h"
-#include "../../../Main/Concepts/Clock_Template/Std_Clock_Realiz.h"
-
-typedef struct Std_Clock_Fac Std_Clock_Fac;
-struct Std_Clock_Fac {
-    Clock_Template* core;
-};
-Std_Clock_Fac Std_Clock_Fac_Var;
-void Std_Clock_Fac_create();
-void Std_Clock_Fac_destroy();
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Standard/Std_Integer_Fac.c

@@ -1,18 +1,0 @@
-#include "Std_Integer_Fac.h"
-
-int Std_Integer_Fac_INSTANCE = 0;
-
-//If our facility has already been created, we don't want a new copy.
-void Std_Integer_Fac_create() {
-	if (Std_Integer_Fac_INSTANCE == 0) {
-		Std_Integer_Fac_Var.core = new_Std_Integer_Realiz_for_Integer_Template();
-		Std_Integer_Fac_INSTANCE = 1;
-	}
-}
-
-void Std_Integer_Fac_destroy() {
-	if (Std_Integer_Fac_INSTANCE == 1) {
-		free_Std_Integer_Realiz_for_Integer_Template(Std_Integer_Fac_Var.core);
-		Std_Integer_Fac_INSTANCE = 0;
-	}
-}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Standard/Std_Integer_Fac.h

@@ -1,16 +1,0 @@
-#ifndef __STD_INTEGER_FAC_H
-#define __STD_INTEGER_FAC_H
-
-#include "../../../RESOLVE.h"
-#include "../../Concepts/Standard/Integer_Template/Std_Integer_Realiz.h"
-
-typedef struct Std_Integer_Fac Std_Integer_Fac;
-struct Std_Integer_Fac {
-	Integer_Template* core;
-};
-Std_Integer_Fac Std_Integer_Fac_Var;
-
-void Std_Integer_Fac_create();
-void Std_Integer_Fac_destroy();
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/RESOLVE.c

@@ -1,9 +1,0 @@
-#include "RESOLVE.h"
-
-// Global functions
-extern void swap(r_type_ptr A, r_type_ptr B){
-	void* temp = *A;
-
-	*A = *B;
-	*B = temp;
-}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/RESOLVE.h

@@ -1,41 +1,0 @@
-#ifndef __RESOLVE_H
-#define __RESOLVE_H
-
-#include <stdlib.h>
-#include <string.h>
-#include <stdio.h>
-#include <stdarg.h>
-
-#include "naive_malloc.h"
-
-typedef void* rtype;
-typedef rtype* r_type_ptr;
-typedef struct type_info type_info;
-
-/*	Universal interface for resolve types.  This interface allows
-    initalization and finalization of objects without requiring those
-    objects to have any method pointers.  Of course this requires matching
-    type_info's to objects of their type.  Type_info pointers are passed
-    as parameters to methods when generic type manipulation is needed.
-    The fields are assigned values when realizations are created.  The
-    type_info is itself a field of a particular realization.
-
-    Inside the init function the PointerToFacility element can be properly
-    cast to the correct type.  For example..
-
-    static r_type_ptr init_Stack(type_info* stackType)
-    {
-        Stack_Template* ar = stackType->PointerToFacility;
-        .....
-    }*/
-
-struct type_info {
-    r_type_ptr (*create)(type_info* thisType);
-    void (*destroy)(r_type_ptr, type_info* thisType);
-    void* PointerToFacility;
-};
-
-// Globally accesible methods
-extern void swap(r_type_ptr A, r_type_ptr B);
-
-#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/naive_malloc.h

@@ -1,10 +1,0 @@
-#ifndef __NAIVE_MALLOC_H__
-#define __NAIVE_MALLOC_H__
-
-#include <stdlib.h>
-
-void *salloc(size_t size);
-void *scalloc(int n, size_t size);
-void sfree(void *ptr);
-
-#endif

### 2014-04-25 tech-project/abstract.tex
new files

--- 2014-04-25 tech-project/paper.tex
@@
-% CpSc 855 - Final paper
-% Takumi Bolte & Dan Welch - Spring 2014.
-\documentclass{sig-alternate}
-
-\usepackage{mathrsfs}
-\usepackage{booktabs}
-\usepackage{placeins}
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{listings}
-\begin{document}
-\conferenceinfo{Clemson 2014}{7th Clemson University Mini-Conference on Embedded Network Systems}
-\title{An Extensible Approach to Verification of Embedded Network Systems*}
-
-%Re-evaluating Verification of Embedded Network Systems:
-%An Extensible Approach to Verification of Embedded Network Systems*}
-\numberofauthors{2}
-\author{
-\alignauthor
-%author
-Daniel Welch\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{dtwelch\}@clemson.edu}}}
-%author
-\alignauthor
-Takumi Bolte\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{tbolte\}@clemson.edu}}}
-}
-
-\maketitle
 \begin{abstract}
@@
 \end{abstract}
-
-\category{D.2.8}{Software Engineering and Data Communication}{Verification}[VCs, automated proving, modular software]
-\terms{Reliability, Verification, Languages, Networks}
-\keywords{automation, components, formal methods, specification, verifying compiler, embedded networks, wireless sensing}
-
-\section{Introduction}
-\label{sec:intro}
-Within little more than a decade, the area of embedded network systems and wireless sensing has exploded in popularity within industry and academia alike.
-Tempering however this extremely quick rise in popularity is the inherent difficulties in developing applications that function as intended in low power, event-driven environments.
-In response to these difficulties, a variety of tools and languages have been put forth  to help ease the burden on developers.
-On one end of this effort are languages such as NesC, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
-The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Arora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
-Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed in the field.
-
-We approach this problem by using RESOLVE (Reusable SOftware Language with VErification) as means of authoring, specifying, and ultimately verifying code for embedded network systems.
-Our decision to use RESOLVE as a language frontend -- as opposed to verifying C code directly -- ultimately stems from a verification amenability standpoint: Not only does RESOLVE prohibit verification crippling operations such as uncontrolled referencing and aliasing (prevalent in C and many other current languages)\cite{kulczycki:2004}, but also embodies a number of other characteristics ideal for embedded platforms including:
-
-\begin{itemize}
-\item \textbf{Modularity} RESOLVE enforces a strict separation of concerns between module specifications and client implementations.
-As a result, for any one particular specification, there can be any number of interchangeable implementations.
-This separation is ideal considering that many embedded applications happen to fit this pattern nicely: Various drivers oftentimes provide a common set of functionality, but in general have many distinct implementations that vary arbitrarily from platform to platform, vendor to vendor.
-
-\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
-This is ideal in a setting where drivers might encompass a wide spectrum possible applications wherein the need for new mathematical developments may arise.% reword this to be less vague.
-
-\end{itemize}
-
-The paper is organized as follows: First, we open with a brief overview of the Telos mote platform.
-Next, we present revised specifications of an LED driver component that is accompanied by a small enhancement.
-This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used.
-The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code.
-We conclude with a review of related works and suggestions for future research and tool improvements.
-
-\section{The Telos Platform}
-
-The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley.
-Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory.
-A cc2420 radio stack provides broadcast and receiving capabilities, while optional sensing capabilities may be added to the mote in the form of light, humidity, and temperature sensors.
-The mote also contains three onboard LEDs: One blue, one red, and one green.
-
-%Additionally, the Telos board contains a total of three LEDs -- one red, one green, and one blue.
-\section{Specifiying LED behavior in Resolve}
-\label{sec:specifiying}
-
-In this section, we provide mathematical and programmatic elements of an LED strip component to give readers both a concrete look at the language, and introduce some new features aimed at making it more amenable to the development of embedded applications.
-Note that while we provide the level of detail necessary to understand the current example, readers interested in gaining a more complete, in depth knowledge of the language are encouraged to refer to \cite{sitaraman:2011, kulczycki:2008}.
-
-\subsection{Concepts}
-\label{ssec:concepts}
-In RESOLVE, programs are composed of several different modules that range from interfaces and realizations, to client (facility) modules.
-A \textit{concept} module in RESOLVE defines a specification for a mathematical, abstract type.
-Similar to an interface in Java, a concept provides a number of operation signatures that implementors are expected to realize.
-Shown below is a \texttt{LED\_Template} concept that provides a light strip abstraction.
-
-\begin{verbatim}
-Concept LED_Template(eval Strip_Length: Integer);
-    uses Boolean_Theory, String_Theory;
-    requires 0 < Strip_Length <= 4;
-
-    Type Family LED is modeled by Str(B);
-        exemplar L;
-        constraint |L| = Strip_Length;
-        initialization ensures 
-            ...
-
-    Oper Set(updates L : LED; eval b : Boolean; 
-                             eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures |L| = |#L| and 
-                   Element_At(i, L) = b;
-
-    Oper Status(preserves L : LED; 
-                   eval i : Integer) : Boolean;
-        requires 0 <= i < |L|;
-        ensures Status = Element_At(i, L);
-
-end LEDs_Template;
-\end{verbatim}
-
-We model our conceptual LED strip using a mathematical string (finite sequence) of booleans, denoted \texttt{Str(B)}, where each boolean within the string indicates the status of that particular LED: On (true) or off (false).
-The \texttt{exemplar} clause located immediately below provides a handle to this abstract model, and is used throughout the remainder of the specification.
-
-%The \texttt{Type Family} clause introduces an abstract type for the LED strip which we mathematically model using strings of booleans, denoted \texttt{Str(B)}, while the \texttt{exemplar} declared immediately after provides a handle to this type family.
-Use of the \texttt{exemplar} can be observed in the \texttt{constraint} clause, where it is used to assert that length of the strip is fixed to be whatever the user has specified via the \texttt{Strip\_Length} parameter.
-Finally, the \texttt{initialization} \texttt{ensures} clause makes explicit the state of the structure at the time it is initialized.
-We omit this verification specific clause, as it has little bearing on verification due to the fact that the realization we provide is \textit{externally} realized -- a point discussed in the next section\footnote{This clause, if it were provided, would need to communicate the following: ``For each position $i$ within the strip, the LED (or, value) at position $i$ is initially false."}
-
-It's worth noting that unlike the \texttt{LED\_Template} presented in \cite{regula:2010} which models an LED as the \textit{cartesian product} of booleans $b_0$, $b_1$, \ldots , $b_4$, the strip model we present here instead uses strings for the following reasons:
-\begin{itemize}
-\item Strings are indexible, and thus do not require separate \texttt{Set} and \texttt{Status} operations for each individual LED.
-\item This approach demonstrates the benefits of reusable mathematical theories.
-The specifications listed here are based (almost) entirely in \texttt{String\_Theory} and are therefore able to make use of RESOLVE's pre-existing math libraries.
-\end{itemize}
-
-Finally, the concept provides two operations.
-The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} two things upon completion: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
-The \texttt{Status} operation is specified similarly.
-
-%Each operation carries with it a pre and post condition in the form of \texttt{requires} and \texttt{ensures} clause, which make explicit what must be true coming into the function, and what must be true after.
-For instance, the requires clause to \texttt{Status} states that \texttt{i} must fall somewhere within the bounds of the string which models our LED strip, while the \texttt{ensures} clause makes use of a \texttt{String\_Theory} definition, \texttt{Element\_At}, to assert that the boolean returned from \texttt{Status} is indeed the value occupying position \texttt{i} of \texttt{L}.
-It's important to note that the variables appearing in the \texttt{requires} and \texttt{ensures} clauses are strictly mathematical values.
-Thus, the \texttt{L} parameter of operation \texttt{Status} is referring to the mathematical value of an \texttt{LED}, as opposed to a programmatic one (typically defined in a realization).
-
-\subsection{Enhancements}
-
-RESOLVE also allows users to extend the functionality provided by the base concept through \textit{enhancements} -- a form of specification inheritance.
-The enhancement we provide here, \texttt{Toggling\_Capability}, allows users to flip a specific LED to its complement.
-
-Shown below is a specification for \texttt{Toggling\_Capability} and one particular realization of it.
-
-\begin{verbatim}
-Enhancement Toggling_Capability for LEDs_Template;
-
-    Oper Toggle(upd L : LED; eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures Element_At(i, L) = 
-                        not(Element_At(i, #L));
-end Toggling_Capability;
-
-Realization Toggling_Realiz for
-            Toggling_Capability of LEDs_Template;
-
-    Proc Toggle(upd L : LED; eval i : Integer);
-        Var Content : Boolean;
-
-        Content := Status(L, Replica(i));
-        Set(L, Not(Content), Replica(i));
-    end Toggle;
-
-end Toggling_Realiz;
-\end{verbatim}
-
-The enhancement specifies a single operation, \texttt{Toggle}, which states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
-
-Note that the enhancement specifications themselves look and function largely the same as a normal concept: Each specifies a purely conceptual module, and hence is implementation neutral.
-
-Enhancement realizations are neutral as well since any method called within the context of an enhancement realization refers to the operation specified in the concept -- meaning no knowledge of implementation details is required.
-
-\subsection{Verification}
-
-We now turn to the task of verifying our small toggling enhancement.
-The first step in doing so is to generate Verification Conditions (VCs) for \texttt{Toggle\_Realiz}, which, if proven, will establish the correctness of this particular implementation.
-One thing to note about the VCs themselves is that they are generated from specific lines of a realization, and exist to ensure that the content of the realization is consistent with its specification: This entails checking for things such as array access boundary violations, etc.
-
-\begin{figure}[!htb]
-\centering
-\begin{tabular}{lccc}
-	\toprule
-	Condition \# & Time (ms)	& Steps	& Search \\
-	\midrule
-	VC 0\_1	& 4426	& 5	& 0	\\
-	VC 0\_2	& 5039	& 5	& 0	\\
-	VC 0\_3	& 6324	& 6	& 0	\\
-	\bottomrule
-\end{tabular}
-\caption{Verification results for operation \texttt{Toggle}}
-\label{fig:results}
-\end{figure}
-
-As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness.
-In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety.
-Readers interested however in learning more about the steps and specific actions the prover takes in transforming givens and dispatching similar (and more complex) VCs should refer to \cite{smith:2013}.
-
-\subsection{Facilities}
-\label{sec:facilities}
-
-With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now turn to a small embedded application that combines these elements to iteratively toggle the lights within an LED strip.
-
-Shown below is a RESOLVE facility module that implements the client logic of this embedded application.
-\begin{verbatim}
-Facility LED_Telos_Demo;
-    uses Std_Clock_Fac, Std_Boolean_Fac, 
-            Std_Integer_Fac;
-
-    Facility Leds_Fac is LED_Template(3)
-        externally realized by Std_Led_Realiz
-     enhanced by Toggling_Capability
-        realized by Toggling_Realiz;
-
-    Operation Main(); Procedure
-
-        (* Declare LED strip indices *)
-        Var I1, I2, I3 : Integer;
-        Var Loop : Boolean;
-
-        (* Declare an LED strip *)
-        Var L : Led;
-
-        I1 := 1; I2 := 2; I3 := 3;
-
-        Loop := True();
-        While(Loop)
-            changing Loop;
-            maintaining ...
-        do
-            Leds_Fac.Toggle(L, I1);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I2);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I3);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-        end;
-    end Main;
-
-end LED_Telos_Demo;
-\end{verbatim}
-%smaller file sizes
-%reusable code
-%only have to translate a file once
-% be able to say that the code we have is the code that was verified.
-% our approach takes less ROM. Its not less efficient, it is differently efficient.
-Prior to using the LED component developed in the previous sections, we first must bind our \texttt{LED\_Template} specification with an appropriate realization.
-This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
-Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
-The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
-
-\subsection{``External'' Realization Support}
-\label{ssec:external}
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/component_graph.pdf}
-\caption{A diagram illustrating inter-component relationships for the example in Section \ref{sec:specifying}}
-\end{figure*}
-\label{fig:imp}
-
-Readers might note that we never presented a realization of \texttt{LED\_Template}.
-Indeed, after having written the concept, the RESOLVE programmer would ideally provide it with a verifiable, native RESOLVE implementation.
-However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by directly manipulating hardware pins provided by msp430's chipset.
-
-RESOLVE, however, in its current state is too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
-In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
-
-The \texttt{LED\_Telos\_Demo} facility above demonstrates these developments through its use of the ``\texttt{externally realized}" phrase.
-This signals to the RESOLVE compiler that the user is providing a non-native realization of the \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.
-
-% Applies to base types in resolve as well
-
-% Similar to NesC, the towers of abstraction idea...
-eventually, similar to nesc, we get enough abstraction  through machinery such as enhancements, etc to with pieces built on top of these externally realized components.
-
-% gives flexibility to those wishing to write other drivers and new
-
-We feel this new keyword is beneficial for the following reasons:
-\begin{itemize}
-\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code.
-The ``externally" keyword now transparently indicates this.
-\item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
-\end{itemize}
-
-In the terms of embedded systems, these developments are especially as it allows us to write custom low level of the sort required for most embedded applications (e.g.
-LED strip drivers) while still providing formally specified interfaces that might later form the foundation .
-It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstract where we can concern ourselves exclusively with verified, native RESOLVE components.
-
-%In a very real sense, gives the language the capability of specifying its foundational components flexibly, and transparently which can later have all native RESOLVE components added on top.
-
-%More than givingHaving the freedom to use RESOLVE's specificational capabilities
-
-%mention performance stuff in future work section.
-
-\begin{figure*}
-\centering
-\includegraphics[scale=.55]{figs/ast_traversal.pdf}
-\caption{A RESOLVE operation AST, the walk call sequence, and sample translation output.}
-\end{figure*}
-\label{fig:ast}
-
-% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE...
-AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE.
-BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
-\section{Implementation}
-Development of our C translation tool can be logically partitioned into three distinct pieces: 
-\begin{enumerate}
-\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
-\item Implementing reusable mechanisms for carrying out the C code generation process.
-\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
-\end{enumerate}
-In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.
-
-\subsection{C Translation Model}
-One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each.
-Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source.
-In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
-Another such consideration includes memory, and decisions on dynamic or static allocation.
-RESOLVE does not currently provide specifications towards a memory model but is in aspirations of providing a dynamically allocatable system.
-Following suit, we will introduce a stack based memory allocator in section \#.
-
-The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
-Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
-Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
-Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
-RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
-
-%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
-
-\subsection{Translator Implementation}
-
-\subsubsection{AST Traversal}
-Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
-The traversal mechanism used is a dervivative of the visitor pattern that provides a SAX-dom style pre-post traversal over all nodes in the tree.
-Thus, for any given node present, a total of two visits occur: One corresponding to the node being `hit' during the pre traversal stage, and one for the post.
-
-To make this more concrete, consider the following dummy operation.
-
-\begin{verbatim}
-Operation Nothing(); Procedure
-        Var X : Integer;
-        X := 3;
-end Nothing;
-\end{verbatim}
-
-Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
-Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack.
-Each of these calls are received in the translator in the order in which they are visited within the tree.
-It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
-
-We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
-
-\begin{itemize}
-\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
-
-\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.
-
-\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
-This makes it easy to tweak and optimize the size of the translator's codebase, implementing only visit method for language constructs that explicitly require translation.
-\end{itemize}
-
-\subsubsection{Translation output}
-Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
-Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.
-
-An example C function definition template is shown below.
-
-\begin{verbatim}
-function_def(modifier, type, name, params, 
-                               vars, stmts) ::= <<
-<modifier> <type> <name> (<params; sep = ", ">) {
-    <vars; sep = "\n">
-    <stmts; sep = "\n">
-}>>
-\end{verbatim}
-
-User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
-It is entirely up to the user to define which attributes to fill in, and how complex they want them to be.
-For example, the user might choose to fill the \texttt{params} attribute with a simple string, or a separately defined \texttt{parameter} template, which in turn might use another separately defined \texttt{type} template.
-
-\begin{verbatim}
-parameter(type, name) ::= "<type> <name>"
-\end{verbatim}
-
-In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
-For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in.
-As \texttt{preOperationDec}'s children are visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the nodes being walked.
-Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in with the appropriate templates -- assuming the user has implemented the children's visit methods.
-
-Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
-This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).
-
-%One of the primary allures of this approach to translation is that that adheres to strict MVC design principles -- meaning that all output logic is distinctly separated from translation related logic.
-
-%We take advantage of these pre post methods using templates and simple stack to implement
-
-%Going even further, we demonstrate this by showing the steps taken to translate a simple operation declaration \texttt{nothing} to C.
-
-% for each construct to remain encapsulated within that method, and (almost) completely eliminates the need for complex loop or iteration mechanisms.
-
-%This particular traversal pattern lends itself well to the language translation challenge (specifically source to source) where the pre methods align naturally with beginning of a construct, and conclude with its corresponding post method.
-For instance, in the case above, this allows us, upon receiving a callback for In an effort to keep logic implementing our translator distinct and separate from the output language, we used a model view controller framework for implementing
-
-%To illustrate this, consider once again facility \texttt{DoNothing}.
-
-\subsection{Memory Allocation}
-
-Dynamic memory allocation does not lend itself well with an embedded programming paradigm.
-With hardware constraints, embedded systems have limited capacities on RAM.
-The telos motes are limited to 128 bytes of RAM.
-Many programs, however, require dynamic memory allocation to be used, including RESOLVE, in order to make it extensible.
-Previous RESOVE translations to C required static memory allocation \cite{regula:2010}.
-In this section a stack based dynamic memory allocator is introduced.
-
-\subsubsection{Allocation using \texttt{salloc}}
-
-The \texttt{salloc()} is a first fit memory allocator.
-Rather than allocating on the heap, \texttt{salloc()} uses the stack.
-At compilation, the allocator provisions a fixed size of memory.
-It requires a small section of meta-data called a block which contains information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
-A sample representation of the stack shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/stack.pdf}
-\caption{Representation of memory stack}
-\end{figure}
-\label{fig:stack}
-
-\subsubsection{Deallocation using \texttt{sfree}}
-
-A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated for something else.
-The \texttt{sfree()} operation is an analogous implementation to the standard C \texttt{free()} function for the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/sfree.pdf}
-\caption{sfree to free memory}
-\end{figure}
-\label{fig:free}
-
-\subsubsection{Optimizations}
-
-A common problem that can occur in memory allocation is fragmentation.
-As shown in figure \ref{fig:fragmentation}, fragmentation can lead to inefficient and increased memory usage.
-This problem is magnified on embedded systems with limited memory capabilities.
-Simple optimizations can be made however to reduce fragmentation.
-Splitting is one optimization that \texttt{salloc()} to maximize memory usage.
-Shown in figure \ref{fig:split}, blocks can be split to the size that is required.
-Another means of optimizing memory usage is joining together freed blocks.
-When a call to \texttt{sfree()} is made, neighboring blocks are coalesced together, as shown in figure \ref{fig:fuse}.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fragmentation.pdf}
-\caption{fragmentation}
-\end{figure}
-\label{fig:fragmentation}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/split.pdf}
-\caption{block splitting}
-\end{figure}
-\label{fig:split}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fuse.pdf}
-\caption{block fusing}
-\end{figure}
-\label{fig:fuse}
-%A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.
-
-%To date there have been very few practical applications of verifiable code on physical media.
-
-\section{Acknowledgements}
-
-Special thanks to Mike Kabanni, Mark Todd, and Bruce Weide whose suggestions and initial contributions in constructing the current model of RESOLVE to C translation made this work possible.
-
-%Open up the .tex file and compile it using Latex (Shift+Apple+L) then compile it using Bibtex (Shift+Apple+B)
-\bibliographystyle{unsrt}
-\bibliography{sigproc}
-\end{document}

### 2014-04-25 tech-project/introduction.tex
new files

--- 2014-04-25 tech-project/paper.tex
@@
-% CpSc 855 - Final paper
-% Takumi Bolte & Dan Welch - Spring 2014.
-\documentclass{sig-alternate}
-
-\usepackage{mathrsfs}
-\usepackage{booktabs}
-\usepackage{placeins}
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{listings}
-\begin{document}
-\conferenceinfo{Clemson 2014}{7th Clemson University Mini-Conference on Embedded Network Systems}
-\title{An Extensible Approach to Verification of Embedded Network Systems*}
-
-%Re-evaluating Verification of Embedded Network Systems:
-%An Extensible Approach to Verification of Embedded Network Systems*}
-\numberofauthors{2}
-\author{
-\alignauthor
-%author
-Daniel Welch\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{dtwelch\}@clemson.edu}}}
-%author
-\alignauthor
-Takumi Bolte\\
-\affaddr{School of Computing, Clemson University}\\
-\affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{tbolte\}@clemson.edu}}}
-}
-
-\maketitle
-\begin{abstract}
-
-In this paper we present a flexible means of specifying and verifying the correctness of software for embedded network systems.
-Our approach uses RESOLVE, an imperative, component based programming and mathematical specification language, to verify the functional correctness of embedded applications.
-In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non-native RESOLVE) realizations.
-We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of a toggling capability enhancement that we demonstrate running on a Telos mote.
-\end{abstract}
-
-\category{D.2.8}{Software Engineering and Data Communication}{Verification}[VCs, automated proving, modular software]
-\terms{Reliability, Verification, Languages, Networks}
-\keywords{automation, components, formal methods, specification, verifying compiler, embedded networks, wireless sensing}
-
 \section{Introduction}
@@
 \item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
-This is ideal in a setting where drivers might encompass a wide spectrum possible applications wherein the need for new mathematical developments may arise.% reword this to be less vague.
+This is ideal in a setting where drivers might encompass a wide spectrum possible applications, where each might require unique, new mathematical developments.% reword this to be less vague.
 
@@
 The paper is organized as follows: First, we open with a brief overview of the Telos mote platform.
-Next, we present revised specifications of an LED driver component that is accompanied by a small enhancement.
+Next, we present revised specifications of an LED driver component with a formally verified enhancement.
 This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used.
 The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code.
-We conclude with a review of related works and suggestions for future research and tool improvements.
-
-\section{The Telos Platform}
-
-The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley.
-Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory.
-A cc2420 radio stack provides broadcast and receiving capabilities, while optional sensing capabilities may be added to the mote in the form of light, humidity, and temperature sensors.
-The mote also contains three onboard LEDs: One blue, one red, and one green.
-
-%Additionally, the Telos board contains a total of three LEDs -- one red, one green, and one blue.
-\section{Specifiying LED behavior in Resolve}
-\label{sec:specifiying}
-
-In this section, we provide mathematical and programmatic elements of an LED strip component to give readers both a concrete look at the language, and introduce some new features aimed at making it more amenable to the development of embedded applications.
-Note that while we provide the level of detail necessary to understand the current example, readers interested in gaining a more complete, in depth knowledge of the language are encouraged to refer to \cite{sitaraman:2011, kulczycki:2008}.
-
-\subsection{Concepts}
-\label{ssec:concepts}
-In RESOLVE, programs are composed of several different modules that range from interfaces and realizations, to client (facility) modules.
-A \textit{concept} module in RESOLVE defines a specification for a mathematical, abstract type.
-Similar to an interface in Java, a concept provides a number of operation signatures that implementors are expected to realize.
-Shown below is a \texttt{LED\_Template} concept that provides a light strip abstraction.
-
-\begin{verbatim}
-Concept LED_Template(eval Strip_Length: Integer);
-    uses Boolean_Theory, String_Theory;
-    requires 0 < Strip_Length <= 4;
-
-    Type Family LED is modeled by Str(B);
-        exemplar L;
-        constraint |L| = Strip_Length;
-        initialization ensures 
-            ...
-
-    Oper Set(updates L : LED; eval b : Boolean; 
-                             eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures |L| = |#L| and 
-                   Element_At(i, L) = b;
-
-    Oper Status(preserves L : LED; 
-                   eval i : Integer) : Boolean;
-        requires 0 <= i < |L|;
-        ensures Status = Element_At(i, L);
-
-end LEDs_Template;
-\end{verbatim}
-
-We model our conceptual LED strip using a mathematical string (finite sequence) of booleans, denoted \texttt{Str(B)}, where each boolean within the string indicates the status of that particular LED: On (true) or off (false).
-The \texttt{exemplar} clause located immediately below provides a handle to this abstract model, and is used throughout the remainder of the specification.
-
-%The \texttt{Type Family} clause introduces an abstract type for the LED strip which we mathematically model using strings of booleans, denoted \texttt{Str(B)}, while the \texttt{exemplar} declared immediately after provides a handle to this type family.
-Use of the \texttt{exemplar} can be observed in the \texttt{constraint} clause, where it is used to assert that length of the strip is fixed to be whatever the user has specified via the \texttt{Strip\_Length} parameter.
-Finally, the \texttt{initialization} \texttt{ensures} clause makes explicit the state of the structure at the time it is initialized.
-We omit this verification specific clause, as it has little bearing on verification due to the fact that the realization we provide is \textit{externally} realized -- a point discussed in the next section\footnote{This clause, if it were provided, would need to communicate the following: ``For each position $i$ within the strip, the LED (or, value) at position $i$ is initially false."}
-
-It's worth noting that unlike the \texttt{LED\_Template} presented in \cite{regula:2010} which models an LED as the \textit{cartesian product} of booleans $b_0$, $b_1$, \ldots , $b_4$, the strip model we present here instead uses strings for the following reasons:
-\begin{itemize}
-\item Strings are indexible, and thus do not require separate \texttt{Set} and \texttt{Status} operations for each individual LED.
-\item This approach demonstrates the benefits of reusable mathematical theories.
-The specifications listed here are based (almost) entirely in \texttt{String\_Theory} and are therefore able to make use of RESOLVE's pre-existing math libraries.
-\end{itemize}
-
-Finally, the concept provides two operations.
-The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} two things upon completion: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
-The \texttt{Status} operation is specified similarly.
-
-%Each operation carries with it a pre and post condition in the form of \texttt{requires} and \texttt{ensures} clause, which make explicit what must be true coming into the function, and what must be true after.
-For instance, the requires clause to \texttt{Status} states that \texttt{i} must fall somewhere within the bounds of the string which models our LED strip, while the \texttt{ensures} clause makes use of a \texttt{String\_Theory} definition, \texttt{Element\_At}, to assert that the boolean returned from \texttt{Status} is indeed the value occupying position \texttt{i} of \texttt{L}.
-It's important to note that the variables appearing in the \texttt{requires} and \texttt{ensures} clauses are strictly mathematical values.
-Thus, the \texttt{L} parameter of operation \texttt{Status} is referring to the mathematical value of an \texttt{LED}, as opposed to a programmatic one (typically defined in a realization).
-
-\subsection{Enhancements}
-
-RESOLVE also allows users to extend the functionality provided by the base concept through \textit{enhancements} -- a form of specification inheritance.
-The enhancement we provide here, \texttt{Toggling\_Capability}, allows users to flip a specific LED to its complement.
-
-Shown below is a specification for \texttt{Toggling\_Capability} and one particular realization of it.
-
-\begin{verbatim}
-Enhancement Toggling_Capability for LEDs_Template;
-
-    Oper Toggle(upd L : LED; eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures Element_At(i, L) = 
-                        not(Element_At(i, #L));
-end Toggling_Capability;
-
-Realization Toggling_Realiz for
-            Toggling_Capability of LEDs_Template;
-
-    Proc Toggle(upd L : LED; eval i : Integer);
-        Var Content : Boolean;
-
-        Content := Status(L, Replica(i));
-        Set(L, Not(Content), Replica(i));
-    end Toggle;
-
-end Toggling_Realiz;
-\end{verbatim}
-
-The enhancement specifies a single operation, \texttt{Toggle}, which states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
-
-Note that the enhancement specifications themselves look and function largely the same as a normal concept: Each specifies a purely conceptual module, and hence is implementation neutral.
-
-Enhancement realizations are neutral as well since any method called within the context of an enhancement realization refers to the operation specified in the concept -- meaning no knowledge of implementation details is required.
-
-\subsection{Verification}
-
-We now turn to the task of verifying our small toggling enhancement.
-The first step in doing so is to generate Verification Conditions (VCs) for \texttt{Toggle\_Realiz}, which, if proven, will establish the correctness of this particular implementation.
-One thing to note about the VCs themselves is that they are generated from specific lines of a realization, and exist to ensure that the content of the realization is consistent with its specification: This entails checking for things such as array access boundary violations, etc.
-
-\begin{figure}[!htb]
-\centering
-\begin{tabular}{lccc}
-	\toprule
-	Condition \# & Time (ms)	& Steps	& Search \\
-	\midrule
-	VC 0\_1	& 4426	& 5	& 0	\\
-	VC 0\_2	& 5039	& 5	& 0	\\
-	VC 0\_3	& 6324	& 6	& 0	\\
-	\bottomrule
-\end{tabular}
-\caption{Verification results for operation \texttt{Toggle}}
-\label{fig:results}
-\end{figure}
-
-As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness.
-In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety.
-Readers interested however in learning more about the steps and specific actions the prover takes in transforming givens and dispatching similar (and more complex) VCs should refer to \cite{smith:2013}.
-
-\subsection{Facilities}
-\label{sec:facilities}
-
-With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now turn to a small embedded application that combines these elements to iteratively toggle the lights within an LED strip.
-
-Shown below is a RESOLVE facility module that implements the client logic of this embedded application.
-\begin{verbatim}
-Facility LED_Telos_Demo;
-    uses Std_Clock_Fac, Std_Boolean_Fac, 
-            Std_Integer_Fac;
-
-    Facility Leds_Fac is LED_Template(3)
-        externally realized by Std_Led_Realiz
-     enhanced by Toggling_Capability
-        realized by Toggling_Realiz;
-
-    Operation Main(); Procedure
-
-        (* Declare LED strip indices *)
-        Var I1, I2, I3 : Integer;
-        Var Loop : Boolean;
-
-        (* Declare an LED strip *)
-        Var L : Led;
-
-        I1 := 1; I2 := 2; I3 := 3;
-
-        Loop := True();
-        While(Loop)
-            changing Loop;
-            maintaining ...
-        do
-            Leds_Fac.Toggle(L, I1);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I2);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I3);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-        end;
-    end Main;
-
-end LED_Telos_Demo;
-\end{verbatim}
-%smaller file sizes
-%reusable code
-%only have to translate a file once
-% be able to say that the code we have is the code that was verified.
-% our approach takes less ROM. Its not less efficient, it is differently efficient.
-Prior to using the LED component developed in the previous sections, we first must bind our \texttt{LED\_Template} specification with an appropriate realization.
-This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
-Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
-The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
-
-\subsection{``External'' Realization Support}
-\label{ssec:external}
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/component_graph.pdf}
-\caption{A diagram illustrating inter-component relationships for the example in Section \ref{sec:specifying}}
-\end{figure*}
-\label{fig:imp}
-
-Readers might note that we never presented a realization of \texttt{LED\_Template}.
-Indeed, after having written the concept, the RESOLVE programmer would ideally provide it with a verifiable, native RESOLVE implementation.
-However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by directly manipulating hardware pins provided by msp430's chipset.
-
-RESOLVE, however, in its current state is too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
-In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
-
-The \texttt{LED\_Telos\_Demo} facility above demonstrates these developments through its use of the ``\texttt{externally realized}" phrase.
-This signals to the RESOLVE compiler that the user is providing a non-native realization of the \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.
-
-% Applies to base types in resolve as well
-
-% Similar to NesC, the towers of abstraction idea...
-eventually, similar to nesc, we get enough abstraction  through machinery such as enhancements, etc to with pieces built on top of these externally realized components.
-
-% gives flexibility to those wishing to write other drivers and new
-
-We feel this new keyword is beneficial for the following reasons:
-\begin{itemize}
-\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code.
-The ``externally" keyword now transparently indicates this.
-\item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
-\end{itemize}
-
-In the terms of embedded systems, these developments are especially as it allows us to write custom low level of the sort required for most embedded applications (e.g.
-LED strip drivers) while still providing formally specified interfaces that might later form the foundation .
-It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstract where we can concern ourselves exclusively with verified, native RESOLVE components.
-
-%In a very real sense, gives the language the capability of specifying its foundational components flexibly, and transparently which can later have all native RESOLVE components added on top.
-
-%More than givingHaving the freedom to use RESOLVE's specificational capabilities
-
-%mention performance stuff in future work section.
-
-\begin{figure*}
-\centering
-\includegraphics[scale=.55]{figs/ast_traversal.pdf}
-\caption{A RESOLVE operation AST, the walk call sequence, and sample translation output.}
-\end{figure*}
-\label{fig:ast}
-
-% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE...
-AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE.
-BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
-\section{Implementation}
-Development of our C translation tool can be logically partitioned into three distinct pieces: 
-\begin{enumerate}
-\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
-\item Implementing reusable mechanisms for carrying out the C code generation process.
-\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
-\end{enumerate}
-In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.
-
-\subsection{C Translation Model}
-One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each.
-Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source.
-In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
-Another such consideration includes memory, and decisions on dynamic or static allocation.
-RESOLVE does not currently provide specifications towards a memory model but is in aspirations of providing a dynamically allocatable system.
-Following suit, we will introduce a stack based memory allocator in section \#.
-
-The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
-Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
-Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
-Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
-RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
-
-%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
-
-\subsection{Translator Implementation}
-
-\subsubsection{AST Traversal}
-Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
-The traversal mechanism used is a dervivative of the visitor pattern that provides a SAX-dom style pre-post traversal over all nodes in the tree.
-Thus, for any given node present, a total of two visits occur: One corresponding to the node being `hit' during the pre traversal stage, and one for the post.
-
-To make this more concrete, consider the following dummy operation.
-
-\begin{verbatim}
-Operation Nothing(); Procedure
-        Var X : Integer;
-        X := 3;
-end Nothing;
-\end{verbatim}
-
-Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
-Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack.
-Each of these calls are received in the translator in the order in which they are visited within the tree.
-It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
-
-We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
-
-\begin{itemize}
-\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
-
-\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.
-
-\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
-This makes it easy to tweak and optimize the size of the translator's codebase, implementing only visit method for language constructs that explicitly require translation.
-\end{itemize}
-
-\subsubsection{Translation output}
-Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
-Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.
-
-An example C function definition template is shown below.
-
-\begin{verbatim}
-function_def(modifier, type, name, params, 
-                               vars, stmts) ::= <<
-<modifier> <type> <name> (<params; sep = ", ">) {
-    <vars; sep = "\n">
-    <stmts; sep = "\n">
-}>>
-\end{verbatim}
-
-User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
-It is entirely up to the user to define which attributes to fill in, and how complex they want them to be.
-For example, the user might choose to fill the \texttt{params} attribute with a simple string, or a separately defined \texttt{parameter} template, which in turn might use another separately defined \texttt{type} template.
-
-\begin{verbatim}
-parameter(type, name) ::= "<type> <name>"
-\end{verbatim}
-
-In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
-For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in.
-As \texttt{preOperationDec}'s children are visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the nodes being walked.
-Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in with the appropriate templates -- assuming the user has implemented the children's visit methods.
-
-Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
-This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).
-
-%One of the primary allures of this approach to translation is that that adheres to strict MVC design principles -- meaning that all output logic is distinctly separated from translation related logic.
-
-%We take advantage of these pre post methods using templates and simple stack to implement
-
-%Going even further, we demonstrate this by showing the steps taken to translate a simple operation declaration \texttt{nothing} to C.
-
-% for each construct to remain encapsulated within that method, and (almost) completely eliminates the need for complex loop or iteration mechanisms.
-
-%This particular traversal pattern lends itself well to the language translation challenge (specifically source to source) where the pre methods align naturally with beginning of a construct, and conclude with its corresponding post method.
-For instance, in the case above, this allows us, upon receiving a callback for In an effort to keep logic implementing our translator distinct and separate from the output language, we used a model view controller framework for implementing
-
-%To illustrate this, consider once again facility \texttt{DoNothing}.
-
-\subsection{Memory Allocation}
-
-Dynamic memory allocation does not lend itself well with an embedded programming paradigm.
-With hardware constraints, embedded systems have limited capacities on RAM.
-The telos motes are limited to 128 bytes of RAM.
-Many programs, however, require dynamic memory allocation to be used, including RESOLVE, in order to make it extensible.
-Previous RESOVE translations to C required static memory allocation \cite{regula:2010}.
-In this section a stack based dynamic memory allocator is introduced.
-
-\subsubsection{Allocation using \texttt{salloc}}
-
-The \texttt{salloc()} is a first fit memory allocator.
-Rather than allocating on the heap, \texttt{salloc()} uses the stack.
-At compilation, the allocator provisions a fixed size of memory.
-It requires a small section of meta-data called a block which contains information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
-A sample representation of the stack shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/stack.pdf}
-\caption{Representation of memory stack}
-\end{figure}
-\label{fig:stack}
-
-\subsubsection{Deallocation using \texttt{sfree}}
-
-A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated for something else.
-The \texttt{sfree()} operation is an analogous implementation to the standard C \texttt{free()} function for the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/sfree.pdf}
-\caption{sfree to free memory}
-\end{figure}
-\label{fig:free}
-
-\subsubsection{Optimizations}
-
-A common problem that can occur in memory allocation is fragmentation.
-As shown in figure \ref{fig:fragmentation}, fragmentation can lead to inefficient and increased memory usage.
-This problem is magnified on embedded systems with limited memory capabilities.
-Simple optimizations can be made however to reduce fragmentation.
-Splitting is one optimization that \texttt{salloc()} to maximize memory usage.
-Shown in figure \ref{fig:split}, blocks can be split to the size that is required.
-Another means of optimizing memory usage is joining together freed blocks.
-When a call to \texttt{sfree()} is made, neighboring blocks are coalesced together, as shown in figure \ref{fig:fuse}.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fragmentation.pdf}
-\caption{fragmentation}
-\end{figure}
-\label{fig:fragmentation}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/split.pdf}
-\caption{block splitting}
-\end{figure}
-\label{fig:split}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fuse.pdf}
-\caption{block fusing}
-\end{figure}
-\label{fig:fuse}
-%A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.
-
-%To date there have been very few practical applications of verifiable code on physical media.
-
-\section{Acknowledgements}
-
-Special thanks to Mike Kabanni, Mark Todd, and Bruce Weide whose suggestions and initial contributions in constructing the current model of RESOLVE to C translation made this work possible.
-
-%Open up the .tex file and compile it using Latex (Shift+Apple+L) then compile it using Bibtex (Shift+Apple+B)
-\bibliographystyle{unsrt}
-\bibliography{sigproc}
-\end{document}
+We conclude with suggestions for tool improvements, as well as a review of some longer term research goals.

### 2014-04-25 tech-project/paper.tex
new files

--- 2014-04-25 tech-project/paper.tex
@@
 \usepackage{listings}
+
 \begin{document}
@@
 }
+\maketitle
 
-\maketitle
-\begin{abstract}
-
-In this paper we present a flexible means of specifying and verifying the correctness of software for embedded network systems.
-Our approach uses RESOLVE, an imperative, component based programming and mathematical specification language, to verify the functional correctness of embedded applications.
-In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non-native RESOLVE) realizations.
-We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of a toggling capability enhancement that we demonstrate running on a Telos mote.
-\end{abstract}
-
+\input{abstract.tex}
 \category{D.2.8}{Software Engineering and Data Communication}{Verification}[VCs, automated proving, modular software]
@@
 
-\section{Introduction}
-\label{sec:intro}
-Within little more than a decade, the area of embedded network systems and wireless sensing has exploded in popularity within industry and academia alike.
-Tempering however this extremely quick rise in popularity is the inherent difficulties in developing applications that function as intended in low power, event-driven environments.
-In response to these difficulties, a variety of tools and languages have been put forth  to help ease the burden on developers.
-On one end of this effort are languages such as NesC, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
-The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Arora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
-Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed in the field.
-
-We approach this problem by using RESOLVE (Reusable SOftware Language with VErification) as means of authoring, specifying, and ultimately verifying code for embedded network systems.
-Our decision to use RESOLVE as a language frontend -- as opposed to verifying C code directly -- ultimately stems from a verification amenability standpoint: Not only does RESOLVE prohibit verification crippling operations such as uncontrolled referencing and aliasing (prevalent in C and many other current languages)\cite{kulczycki:2004}, but also embodies a number of other characteristics ideal for embedded platforms including:
-
-\begin{itemize}
-\item \textbf{Modularity} RESOLVE enforces a strict separation of concerns between module specifications and client implementations.
-As a result, for any one particular specification, there can be any number of interchangeable implementations.
-This separation is ideal considering that many embedded applications happen to fit this pattern nicely: Various drivers oftentimes provide a common set of functionality, but in general have many distinct implementations that vary arbitrarily from platform to platform, vendor to vendor.
-
-\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
-This is ideal in a setting where drivers might encompass a wide spectrum possible applications wherein the need for new mathematical developments may arise.% reword this to be less vague.
-
-\end{itemize}
-
-The paper is organized as follows: First, we open with a brief overview of the Telos mote platform.
-Next, we present revised specifications of an LED driver component that is accompanied by a small enhancement.
-This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used.
-The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code.
-We conclude with a review of related works and suggestions for future research and tool improvements.
-
-\section{The Telos Platform}
-
-The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley.
-Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory.
-A cc2420 radio stack provides broadcast and receiving capabilities, while optional sensing capabilities may be added to the mote in the form of light, humidity, and temperature sensors.
-The mote also contains three onboard LEDs: One blue, one red, and one green.
-
-%Additionally, the Telos board contains a total of three LEDs -- one red, one green, and one blue.
-\section{Specifiying LED behavior in Resolve}
-\label{sec:specifiying}
-
-In this section, we provide mathematical and programmatic elements of an LED strip component to give readers both a concrete look at the language, and introduce some new features aimed at making it more amenable to the development of embedded applications.
-Note that while we provide the level of detail necessary to understand the current example, readers interested in gaining a more complete, in depth knowledge of the language are encouraged to refer to \cite{sitaraman:2011, kulczycki:2008}.
-
-\subsection{Concepts}
-\label{ssec:concepts}
-In RESOLVE, programs are composed of several different modules that range from interfaces and realizations, to client (facility) modules.
-A \textit{concept} module in RESOLVE defines a specification for a mathematical, abstract type.
-Similar to an interface in Java, a concept provides a number of operation signatures that implementors are expected to realize.
-Shown below is a \texttt{LED\_Template} concept that provides a light strip abstraction.
-
-\begin{verbatim}
-Concept LED_Template(eval Strip_Length: Integer);
-    uses Boolean_Theory, String_Theory;
-    requires 0 < Strip_Length <= 4;
-
-    Type Family LED is modeled by Str(B);
-        exemplar L;
-        constraint |L| = Strip_Length;
-        initialization ensures 
-            ...
-
-    Oper Set(updates L : LED; eval b : Boolean; 
-                             eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures |L| = |#L| and 
-                   Element_At(i, L) = b;
-
-    Oper Status(preserves L : LED; 
-                   eval i : Integer) : Boolean;
-        requires 0 <= i < |L|;
-        ensures Status = Element_At(i, L);
-
-end LEDs_Template;
-\end{verbatim}
-
-We model our conceptual LED strip using a mathematical string (finite sequence) of booleans, denoted \texttt{Str(B)}, where each boolean within the string indicates the status of that particular LED: On (true) or off (false).
-The \texttt{exemplar} clause located immediately below provides a handle to this abstract model, and is used throughout the remainder of the specification.
-
-%The \texttt{Type Family} clause introduces an abstract type for the LED strip which we mathematically model using strings of booleans, denoted \texttt{Str(B)}, while the \texttt{exemplar} declared immediately after provides a handle to this type family.
-Use of the \texttt{exemplar} can be observed in the \texttt{constraint} clause, where it is used to assert that length of the strip is fixed to be whatever the user has specified via the \texttt{Strip\_Length} parameter.
-Finally, the \texttt{initialization} \texttt{ensures} clause makes explicit the state of the structure at the time it is initialized.
-We omit this verification specific clause, as it has little bearing on verification due to the fact that the realization we provide is \textit{externally} realized -- a point discussed in the next section\footnote{This clause, if it were provided, would need to communicate the following: ``For each position $i$ within the strip, the LED (or, value) at position $i$ is initially false."}
-
-It's worth noting that unlike the \texttt{LED\_Template} presented in \cite{regula:2010} which models an LED as the \textit{cartesian product} of booleans $b_0$, $b_1$, \ldots , $b_4$, the strip model we present here instead uses strings for the following reasons:
-\begin{itemize}
-\item Strings are indexible, and thus do not require separate \texttt{Set} and \texttt{Status} operations for each individual LED.
-\item This approach demonstrates the benefits of reusable mathematical theories.
-The specifications listed here are based (almost) entirely in \texttt{String\_Theory} and are therefore able to make use of RESOLVE's pre-existing math libraries.
-\end{itemize}
-
-Finally, the concept provides two operations.
-The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} two things upon completion: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
-The \texttt{Status} operation is specified similarly.
-
-%Each operation carries with it a pre and post condition in the form of \texttt{requires} and \texttt{ensures} clause, which make explicit what must be true coming into the function, and what must be true after.
-For instance, the requires clause to \texttt{Status} states that \texttt{i} must fall somewhere within the bounds of the string which models our LED strip, while the \texttt{ensures} clause makes use of a \texttt{String\_Theory} definition, \texttt{Element\_At}, to assert that the boolean returned from \texttt{Status} is indeed the value occupying position \texttt{i} of \texttt{L}.
-It's important to note that the variables appearing in the \texttt{requires} and \texttt{ensures} clauses are strictly mathematical values.
-Thus, the \texttt{L} parameter of operation \texttt{Status} is referring to the mathematical value of an \texttt{LED}, as opposed to a programmatic one (typically defined in a realization).
-
-\subsection{Enhancements}
-
-RESOLVE also allows users to extend the functionality provided by the base concept through \textit{enhancements} -- a form of specification inheritance.
-The enhancement we provide here, \texttt{Toggling\_Capability}, allows users to flip a specific LED to its complement.
-
-Shown below is a specification for \texttt{Toggling\_Capability} and one particular realization of it.
-
-\begin{verbatim}
-Enhancement Toggling_Capability for LEDs_Template;
-
-    Oper Toggle(upd L : LED; eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures Element_At(i, L) = 
-                        not(Element_At(i, #L));
-end Toggling_Capability;
-
-Realization Toggling_Realiz for
-            Toggling_Capability of LEDs_Template;
-
-    Proc Toggle(upd L : LED; eval i : Integer);
-        Var Content : Boolean;
-
-        Content := Status(L, Replica(i));
-        Set(L, Not(Content), Replica(i));
-    end Toggle;
-
-end Toggling_Realiz;
-\end{verbatim}
-
-The enhancement specifies a single operation, \texttt{Toggle}, which states that upon termination, the LED located at position \texttt{i} in \texttt{L} is the complement of that same location in the incoming LED, \texttt{\#L}.
-
-Note that the enhancement specifications themselves look and function largely the same as a normal concept: Each specifies a purely conceptual module, and hence is implementation neutral.
-
-Enhancement realizations are neutral as well since any method called within the context of an enhancement realization refers to the operation specified in the concept -- meaning no knowledge of implementation details is required.
-
-\subsection{Verification}
-
-We now turn to the task of verifying our small toggling enhancement.
-The first step in doing so is to generate Verification Conditions (VCs) for \texttt{Toggle\_Realiz}, which, if proven, will establish the correctness of this particular implementation.
-One thing to note about the VCs themselves is that they are generated from specific lines of a realization, and exist to ensure that the content of the realization is consistent with its specification: This entails checking for things such as array access boundary violations, etc.
-
-\begin{figure}[!htb]
-\centering
-\begin{tabular}{lccc}
-	\toprule
-	Condition \# & Time (ms)	& Steps	& Search \\
-	\midrule
-	VC 0\_1	& 4426	& 5	& 0	\\
-	VC 0\_2	& 5039	& 5	& 0	\\
-	VC 0\_3	& 6324	& 6	& 0	\\
-	\bottomrule
-\end{tabular}
-\caption{Verification results for operation \texttt{Toggle}}
-\label{fig:results}
-\end{figure}
-
-As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness.
-In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety.
-Readers interested however in learning more about the steps and specific actions the prover takes in transforming givens and dispatching similar (and more complex) VCs should refer to \cite{smith:2013}.
-
-\subsection{Facilities}
-\label{sec:facilities}
-
-With our formally specified LED strip component in place -- and a verified enhancement on this component -- we now turn to a small embedded application that combines these elements to iteratively toggle the lights within an LED strip.
-
-Shown below is a RESOLVE facility module that implements the client logic of this embedded application.
-\begin{verbatim}
-Facility LED_Telos_Demo;
-    uses Std_Clock_Fac, Std_Boolean_Fac, 
-            Std_Integer_Fac;
-
-    Facility Leds_Fac is LED_Template(3)
-        externally realized by Std_Led_Realiz
-     enhanced by Toggling_Capability
-        realized by Toggling_Realiz;
-
-    Operation Main(); Procedure
-
-        (* Declare LED strip indices *)
-        Var I1, I2, I3 : Integer;
-        Var Loop : Boolean;
-
-        (* Declare an LED strip *)
-        Var L : Led;
-
-        I1 := 1; I2 := 2; I3 := 3;
-
-        Loop := True();
-        While(Loop)
-            changing Loop;
-            maintaining ...
-        do
-            Leds_Fac.Toggle(L, I1);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I2);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I3);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-        end;
-    end Main;
-
-end LED_Telos_Demo;
-\end{verbatim}
-%smaller file sizes
-%reusable code
-%only have to translate a file once
-% be able to say that the code we have is the code that was verified.
-% our approach takes less ROM. Its not less efficient, it is differently efficient.
-Prior to using the LED component developed in the previous sections, we first must bind our \texttt{LED\_Template} specification with an appropriate realization.
-This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
-Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
-The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
-
-\subsection{``External'' Realization Support}
-\label{ssec:external}
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/component_graph.pdf}
-\caption{A diagram illustrating inter-component relationships for the example in Section \ref{sec:specifying}}
-\end{figure*}
-\label{fig:imp}
-
-Readers might note that we never presented a realization of \texttt{LED\_Template}.
-Indeed, after having written the concept, the RESOLVE programmer would ideally provide it with a verifiable, native RESOLVE implementation.
-However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by directly manipulating hardware pins provided by msp430's chipset.
-
-RESOLVE, however, in its current state is too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
-In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
-
-The \texttt{LED\_Telos\_Demo} facility above demonstrates these developments through its use of the ``\texttt{externally realized}" phrase.
-This signals to the RESOLVE compiler that the user is providing a non-native realization of the \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.
-
-% Applies to base types in resolve as well
-
-% Similar to NesC, the towers of abstraction idea...
-eventually, similar to nesc, we get enough abstraction  through machinery such as enhancements, etc to with pieces built on top of these externally realized components.
-
-% gives flexibility to those wishing to write other drivers and new
-
-We feel this new keyword is beneficial for the following reasons:
-\begin{itemize}
-\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code.
-The ``externally" keyword now transparently indicates this.
-\item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
-\end{itemize}
-
-In the terms of embedded systems, these developments are especially as it allows us to write custom low level of the sort required for most embedded applications (e.g.
-LED strip drivers) while still providing formally specified interfaces that might later form the foundation .
-It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstract where we can concern ourselves exclusively with verified, native RESOLVE components.
-
-%In a very real sense, gives the language the capability of specifying its foundational components flexibly, and transparently which can later have all native RESOLVE components added on top.
-
-%More than givingHaving the freedom to use RESOLVE's specificational capabilities
-
-%mention performance stuff in future work section.
-
-\begin{figure*}
-\centering
-\includegraphics[scale=.55]{figs/ast_traversal.pdf}
-\caption{A RESOLVE operation AST, the walk call sequence, and sample translation output.}
-\end{figure*}
-\label{fig:ast}
-
-% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE...
-AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE.
-BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
-\section{Implementation}
-Development of our C translation tool can be logically partitioned into three distinct pieces: 
-\begin{enumerate}
-\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
-\item Implementing reusable mechanisms for carrying out the C code generation process.
-\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
-\end{enumerate}
-In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.
-
-\subsection{C Translation Model}
-One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each.
-Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source.
-In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
-Another such consideration includes memory, and decisions on dynamic or static allocation.
-RESOLVE does not currently provide specifications towards a memory model but is in aspirations of providing a dynamically allocatable system.
-Following suit, we will introduce a stack based memory allocator in section \#.
-
-The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
-Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
-Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
-Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
-RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
-
-%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
-
-\subsection{Translator Implementation}
-
-\subsubsection{AST Traversal}
-Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
-The traversal mechanism used is a dervivative of the visitor pattern that provides a SAX-dom style pre-post traversal over all nodes in the tree.
-Thus, for any given node present, a total of two visits occur: One corresponding to the node being `hit' during the pre traversal stage, and one for the post.
-
-To make this more concrete, consider the following dummy operation.
-
-\begin{verbatim}
-Operation Nothing(); Procedure
-        Var X : Integer;
-        X := 3;
-end Nothing;
-\end{verbatim}
-
-Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
-Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack.
-Each of these calls are received in the translator in the order in which they are visited within the tree.
-It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
-
-We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
-
-\begin{itemize}
-\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
-
-\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.
-
-\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
-This makes it easy to tweak and optimize the size of the translator's codebase, implementing only visit method for language constructs that explicitly require translation.
-\end{itemize}
-
-\subsubsection{Translation output}
-Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
-Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.
-
-An example C function definition template is shown below.
-
-\begin{verbatim}
-function_def(modifier, type, name, params, 
-                               vars, stmts) ::= <<
-<modifier> <type> <name> (<params; sep = ", ">) {
-    <vars; sep = "\n">
-    <stmts; sep = "\n">
-}>>
-\end{verbatim}
-
-User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
-It is entirely up to the user to define which attributes to fill in, and how complex they want them to be.
-For example, the user might choose to fill the \texttt{params} attribute with a simple string, or a separately defined \texttt{parameter} template, which in turn might use another separately defined \texttt{type} template.
-
-\begin{verbatim}
-parameter(type, name) ::= "<type> <name>"
-\end{verbatim}
-
-In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
-For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in.
-As \texttt{preOperationDec}'s children are visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the nodes being walked.
-Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in with the appropriate templates -- assuming the user has implemented the children's visit methods.
-
-Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
-This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).
-
-%One of the primary allures of this approach to translation is that that adheres to strict MVC design principles -- meaning that all output logic is distinctly separated from translation related logic.
-
-%We take advantage of these pre post methods using templates and simple stack to implement
-
-%Going even further, we demonstrate this by showing the steps taken to translate a simple operation declaration \texttt{nothing} to C.
-
-% for each construct to remain encapsulated within that method, and (almost) completely eliminates the need for complex loop or iteration mechanisms.
-
-%This particular traversal pattern lends itself well to the language translation challenge (specifically source to source) where the pre methods align naturally with beginning of a construct, and conclude with its corresponding post method.
-For instance, in the case above, this allows us, upon receiving a callback for In an effort to keep logic implementing our translator distinct and separate from the output language, we used a model view controller framework for implementing
-
-%To illustrate this, consider once again facility \texttt{DoNothing}.
-
-\subsection{Memory Allocation}
-
-Dynamic memory allocation does not lend itself well with an embedded programming paradigm.
-With hardware constraints, embedded systems have limited capacities on RAM.
-The telos motes are limited to 128 bytes of RAM.
-Many programs, however, require dynamic memory allocation to be used, including RESOLVE, in order to make it extensible.
-Previous RESOVE translations to C required static memory allocation \cite{regula:2010}.
-In this section a stack based dynamic memory allocator is introduced.
-
-\subsubsection{Allocation using \texttt{salloc}}
-
-The \texttt{salloc()} is a first fit memory allocator.
-Rather than allocating on the heap, \texttt{salloc()} uses the stack.
-At compilation, the allocator provisions a fixed size of memory.
-It requires a small section of meta-data called a block which contains information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
-A sample representation of the stack shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/stack.pdf}
-\caption{Representation of memory stack}
-\end{figure}
-\label{fig:stack}
-
-\subsubsection{Deallocation using \texttt{sfree}}
-
-A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated for something else.
-The \texttt{sfree()} operation is an analogous implementation to the standard C \texttt{free()} function for the stack.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/sfree.pdf}
-\caption{sfree to free memory}
-\end{figure}
-\label{fig:free}
-
-\subsubsection{Optimizations}
-
-A common problem that can occur in memory allocation is fragmentation.
-As shown in figure \ref{fig:fragmentation}, fragmentation can lead to inefficient and increased memory usage.
-This problem is magnified on embedded systems with limited memory capabilities.
-Simple optimizations can be made however to reduce fragmentation.
-Splitting is one optimization that \texttt{salloc()} to maximize memory usage.
-Shown in figure \ref{fig:split}, blocks can be split to the size that is required.
-Another means of optimizing memory usage is joining together freed blocks.
-When a call to \texttt{sfree()} is made, neighboring blocks are coalesced together, as shown in figure \ref{fig:fuse}.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fragmentation.pdf}
-\caption{fragmentation}
-\end{figure}
-\label{fig:fragmentation}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/split.pdf}
-\caption{block splitting}
-\end{figure}
-\label{fig:split}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=.55]{figs/fuse.pdf}
-\caption{block fusing}
-\end{figure}
-\label{fig:fuse}
-%A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.
-
-%To date there have been very few practical applications of verifiable code on physical media.
-
-\section{Acknowledgements}
-
-Special thanks to Mike Kabanni, Mark Todd, and Bruce Weide whose suggestions and initial contributions in constructing the current model of RESOLVE to C translation made this work possible.
+\input{introduction.tex}
+\input{telos_platform.tex}
+\input{specify_led.tex}
+\input{implementation.tex}
+\input{acknowledge.tex}
 

### 2014-04-25 tech-project/specify_led.tex
new files

@@
 
-In this section we give a short overview of the verification results of \texttt{Toggling\_Realiz}.
-The first step in proving this particular realization correct is to generate verification conditions (VCs), which, if proven, will establish the correctness of this particular realization\footnote{Note: VCs themselves are typically generated from specific lines of a realization to ensure that the overall content of a realization is consistent with its specification.}.
+We now turn to the task of verifying our small toggling enhancement.
+The first step in doing so is to generate Verification Conditions (VCs) for \texttt{Toggle\_Realiz}, which, if proven, will establish the correctness of this particular implementation.
+One thing to note about the VCs themselves is that they are generated from specific lines of a realization, and exist to ensure that the content of the realization is consistent with its specification: This entails checking for things such as array access boundary violations, etc.
 
@@
 % our approach takes less ROM. Its not less efficient, it is differently efficient.
-Prior to using the LED component developed in the previous sections, we first must associate our \texttt{LED\_Template} specification with an appropriate realization.
+Prior to using the LED component developed in the previous sections, we first must bind our \texttt{LED\_Template} specification with an appropriate realization.
 This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
 Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
-
-The bulk of the logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
+The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
 
@@
 
-RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
+RESOLVE, however, in its current state is too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so.
 In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing.
-In the case of \texttt{LED\_Template}, we chose to provide a hand written \texttt{Std\_Leds\_Realiz} C realization, that matches as closely as possible the conventions and model of translation later detailed in Section \#.
 
-The \texttt{LED\_Telos\_Demo} facility showcased above demonstrates this through its use of the ``\texttt{externally realized}" phrase.
-This signals to the RESOLVE compiler that the user is providing a non-native realization, with the expectation that it conforms to the specifications dictated in the concept.
+The \texttt{LED\_Telos\_Demo} facility above demonstrates these developments through its use of the ``\texttt{externally realized}" phrase.
+This signals to the RESOLVE compiler that the user is providing a non-native realization of the \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.
 
@@
 
-We feel this new keyword is useful for the following reasons:
+We feel this new keyword is beneficial for the following reasons:
 \begin{itemize}
 \item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code.
-The keyword now transparently indicates this.
+The ``externally" keyword now transparently indicates this.
 \item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
@@
 
-In the context of embedded systems especially, we feel these developments will allow users to flexibly and transparently specify all low level components of the sort required in most embedded applications (e.g.
-LED strip drivers).
-It is our intent that new (native) resolve components are layered on top of these low level drivers to provide a system (not unlike NesC) that deals with verified component graphs of ..
+In the terms of embedded systems, these developments are especially as it allows us to write custom low level of the sort required for most embedded applications (e.g.
+LED strip drivers) while still providing formally specified interfaces that might later form the foundation .
+It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstract where we can concern ourselves exclusively with verified, native RESOLVE components.
 
@@
 
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=.45]{figs/implementation.pdf}
-\caption{RESOLVE module types and their corresponding C representation}
-\end{figure*}
-\label{fig:imp}
-
 \begin{figure*}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Bdd_Spiral_Template/Array_Realiz.rb

@@ -1,0 +1,21 @@
+Realization Array_Realiz for Bdd_Spiral_Template;
+	
+	Facility Ceramic_Array_Fac is 
+		Static_Array_Template(Label, 1, Max_Length)
+		externally realized by Std_Array_Realiz;
+		
+	Type Spiral_Pos is represented by Record
+			Labl : Ceramic_Array_Fac.Static_Array;
+			Length, Curr : Integer;
+		end;
+		convention 0 <= P.Curr <= P.Length and 
+				   P.Length <= Max_Length;
+		correspondence true;
+	end;
+	
+	Proc Lengthen(upd P : Spiral_Pos; alt New_Lab : Label);
+		Ceramic_Array_Fac.Swap_Entry(P.Labl, New_Lab, P.Length);
+		P.Length := P.Length + 1;
+	end Lengthen;
+	
+end Array_Realiz;	

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Clock_Template/Std_Clock_Realiz.c

@@ -1,0 +1,47 @@
+/*
+ * Generated by the RESOLVE to C translator. This file
+ * should not be modified.
+ */
+#include "Std_Clock_Realiz.h"
+#include "Clock_Template.h"
+#ifdef TELOS
+#include <msp430.h>
+#include <legacymsp430.h>
+#endif
+
+extern void free_Std_Clock_Realiz_for_Clock_Template(Clock_Template* toFree) {
+	sfree(toFree);
+}
+
+static void Wait_1_Second(Clock_Template* this) {
+#ifdef TELOS
+	__delay_cycles(40000000);	
+#else
+	printf("Waiting 1 Second...\n");
+#endif
+}
+
+static void Wait_5_Seconds(Clock_Template* this) {
+#ifdef TELOS
+	__delay_cycles(20000000);
+#else
+	printf("Waiting 5 Seconds...\n");
+#endif
+}
+
+static void Wait_500_Milli_Seconds(Clock_Template* this) {
+#ifdef TELOS
+	__delay_cycles(2000000);
+#else
+	printf("Waiting 500 Milliseconds...\n");
+#endif
+}
+
+extern Clock_Template* new_Std_Clock_Realiz_for_Clock_Template() {
+	Clock_Template* this = salloc(sizeof(Clock_Template));
+	this->Wait_5_Seconds = Wait_5_Seconds;
+	this->Wait_1_Second = Wait_1_Second;
+	this->Wait_500_Milli_Seconds = Wait_500_Milli_Seconds;
+
+	return this;	
+}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Leds_Template/Std_Leds_Realiz.h

@@ -1,0 +1,12 @@
+#ifndef __STD_LEDS_REALIZ_H
+#define __STD_LEDS_REALIZ_H
+
+#include "../../../RESOLVE.h"
+#include "../../../Main/Concepts/Leds_Template/Leds_Template.h"
+#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
+#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
+
+extern Leds_Template* new_Std_Leds_Realiz_for_Leds_Template(r_type_ptr Strip_Length);
+extern void free_Std_Leds_Realiz_for_Leds_Template(Leds_Template* toFree);
+
+#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Queue_Template/Iterative_Append_Realiz.rb

@@ -1,0 +1,12 @@
+Realization Iterative_Append_Realiz for Append_Capability of Queue_Template;
+    Procedure Append(updates P: Queue; clears Q: Queue);
+        Var E: Entry;
+        While ( Is_Not_Zero(Length(Q)) )
+          maintaining (P o Q = #P o #Q);
+          decreasing |Q|;
+        do
+          Dequeue(E,Q);
+          Enqueue(E,P);
+        end;
+    end Append;
+end Iterative_Append_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Array_Realiz.c

@@ -1,0 +1,87 @@
+/*
+ * Generated by the RESOLVE to C translator. This file
+ * should not be modified.
+ */
+#include "Array_Realiz.h"
+
+typedef struct _Contents_Array_Fac_1 _Contents_Array_Fac_1;
+struct _Contents_Array_Fac_1 {
+    Static_Array_Template* core;
+};
+
+typedef struct Realization_Specific Realization_Specific;
+struct Realization_Specific {
+    _Contents_Array_Fac_1 _Contents_Array_Fac_1_Var;
+};
+
+typedef struct Stack_Instance Stack_Instance;
+struct Stack_Instance {
+    r_type_ptr Contents;
+    r_type_ptr Top;
+};
+
+static r_type_ptr createStack(type_info* StackType) {
+    Stack_Template* this = StackType->PointerToFacility;
+    Stack_Instance* Stack_i = calloc(1, sizeof(Stack_Instance));
+
+    _Contents_Array_Fac_1 _Contents_Array_Fac_1_Var = ((Realization_Specific*)
+        this->Realization_Specific)->_Contents_Array_Fac_1_Var;
+
+    Stack_i->Contents = _Contents_Array_Fac_1_Var.core->Static_Array->create(_Contents_Array_Fac_1_Var.core->Static_Array); 
+    Stack_i->Top = Std_Integer_Fac_Var.core->Integer->create(Std_Integer_Fac_Var.core->Integer); 
+    Stack_Instance** t = malloc(sizeof(Stack_Instance*));
+
+    *t = si;
+    return (r_type_ptr)t;
+}
+
+static void destroyStack(r_type_ptr r, type_info* StackType) {
+    Stack_Instance* Stack_i = *r;
+    Stack_Template* this = StackType->PointerToFacility;
+
+    _Contents_Array_Fac_1 _Contents_Array_Fac_1_Var = ((Realization_Specific*)
+            this->Realization_Specific)->_Contents_Array_Fac_1_Var;
+
+    _Contents_Array_Fac_1_Var.core->Static_Array->destroy(Stack_i->Contents,
+        _Contents_Array_Fac_1_Var.core->Static_Array); 
+    Std_Integer_Fac_Var.core->Integer->destroy(Stack_i->Top,
+        Std_Integer_Fac_Var.core->Integer); 
+    free(*r);
+    free(r);
+}
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Array_Realiz.rb

@@ -1,0 +1,65 @@
+(*
+ * This softare is released under the new BSD 2006 license.
+ *
+ * Note the new BSD license is equivalent to the MIT License, except for the
+ * no-endorsement final clause.
+ *
+ * Copyright (c) 2007, Clemson University
+ *
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions are met:
+ *
+ *   * Redistributions of source code must retain the above copyright notice,
+ *     this list of conditions and the following disclaimer.
+ *   * Redistributions in binary form must reproduce the above copyright
+ *     notice, this list of conditions and the following disclaimer in the
+ *     documentation and/or other materials provided with the distribution.
+ *   * Neither the name of the Clemson University nor the names of its
+ *     contributors may be used to endorse or promote products derived from
+ *     this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+ * A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER
+ * OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO,
+ * PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+ * PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+ * LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+ * NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+ * SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+ *
+ * This sofware has been developed by past and present members of the
+ * Reusable Sofware Research Groups (RSRG) at Clemson University and
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Clear_3_Realiz.rb

@@ -1,0 +1,10 @@
+Realization Clear_3_Realiz for Clear_3_Capability of Stack_Template;
+
+	Procedure Clear_3(clears S: Stack);
+		Var Next_Entry: Entry;
+
+		Pop(Next_Entry, S);
+		Pop(Next_Entry, S);
+		Pop(Next_Entry, S);
+	end Clear_3;
+end Clear_3_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Stack_Template/Init_Array_Realiz.rb

@@ -1,0 +1,41 @@
+Realization Init_Array_Realiz for Stack_Template;
+
+    (* Note: Under Construction! *)
+
+    Type Stack is represented by Record
+            Contents: Array 1..Max_Depth of Entry;
+            Top: Integer;
+        end;
+        convention
+            1 <= S.Top <= Max_Depth+1;
+        correspondence
+            Conc.S = Reverse(Concatenation i: Integer
+            where 1 <= i <= S.Top-1, <S.Contents(i)>);
+        initialization
+           S.Top := 1;
+        end;
+	end;
+	
+    Procedure Push(alters E: Entry; updates S: Stack);
+        E :=: S.Contents[S.Top];
+        S.Top := S.Top + 1;
+    end Push;
+
+    Procedure Pop(replaces R: Entry; updates S: Stack); 
+        S.Top := S.Top - 1;
+        R :=: S.Contents[S.Top];
+    end Pop;
+
+    Procedure Depth(preserves S: Stack): Integer;
+        Depth := S.Top-1;
+    end Depth;
+
+    Procedure Rem_Capacity(preserves S: Stack): Integer;
+        Rem_Capacity := Max_Depth + 1 - S.Top;
+    end Rem_Capacity;
+
+    Procedure Clear(clears S: Stack);
+        S.Top := 1;
+    end Clear;
+
+end Init_Array_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Boolean_Template/Boolean_Template.h

@@ -1,0 +1,29 @@
+/*
+ * Generated by the RESOLVE to C translator. This file
+ * should not be modified.
+ */
+#ifndef __BOOLEAN_TEMPLATE_H
+#define __BOOLEAN_TEMPLATE_H
+
+#include "../../../../RESOLVE.h"
+
+typedef struct Boolean_Template Boolean_Template;
+struct Boolean_Template {
+    void* Realization_Specific;
+    type_info* Boolean;
+    r_type_ptr (*True) (Boolean_Template*);
+    r_type_ptr (*False) (Boolean_Template*);
+    r_type_ptr (*And) (r_type_ptr, r_type_ptr, Boolean_Template*);
+    r_type_ptr (*Or) (r_type_ptr, r_type_ptr, Boolean_Template*);
+    r_type_ptr (*Not) (r_type_ptr, Boolean_Template*);
+    r_type_ptr (*Are_Equal) (r_type_ptr, r_type_ptr, Boolean_Template*);
+    r_type_ptr (*Are_Not_Equal) (r_type_ptr, r_type_ptr, Boolean_Template*);
+    r_type_ptr (*Replica) (r_type_ptr, Boolean_Template*);
+	void (*assign) (r_type_ptr, r_type_ptr, Boolean_Template*);
+	void (*Read) (r_type_ptr, Boolean_Template*);
+    void (*Write) (r_type_ptr, Boolean_Template*);
+    void (*Write_Line) (r_type_ptr, Boolean_Template*);
+    r_type_ptr (*createFromBoolean) (int, type_info*);
+	r_type_ptr (*createBoolean) (type_info*);
+};
+#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Boolean_Template/Std_Boolean_Realiz.c

@@ -1,0 +1,144 @@
+#include "Boolean_Template.h"
+
+static int ValueOf(r_type_ptr r) {
+    return **(int**)r;
+}
+
+static r_type_ptr createFromBoolean(int I, type_info* ti) {
+	int *space = scalloc(1, sizeof(int));
+	*space = I;
+	int** ret = salloc(sizeof(int*));
+	*ret = space;
+	return (r_type_ptr)ret;
+}
+
+static r_type_ptr createBoolean(type_info* ti) {
+    int* t = scalloc(1, sizeof(int));
+	*t = 0;
+    int** ret = salloc(sizeof(int*));
+    *ret = t;
+    return (r_type_ptr)ret;
+}
+
+static void destroyBoolean (r_type_ptr r, type_info* ti) {
+    sfree(*r);
+    sfree(r);
+}
+
+static type_info* newBoolean() {
+    type_info* pc = scalloc(1, sizeof(type_info));
+    pc->create = createBoolean;
+    pc->destroy = destroyBoolean;
+    return pc;
+}
+
+static r_type_ptr True(Boolean_Template* this) {
+	int *space = scalloc(1, sizeof(int));
+	*space = 1;
+	int** ret = salloc(sizeof(int*));
+	*ret = space;
+	return (r_type_ptr)ret;
+}
+
+static r_type_ptr False(Boolean_Template* this) {
+	int *space = scalloc(1, sizeof(int));
+	*space = 0;
+	int** ret = salloc(sizeof(int*));
+	*ret = space;
+	return (r_type_ptr)ret;
+}
+
+static r_type_ptr And(r_type_ptr b1, r_type_ptr b2, Boolean_Template* this) {
+	int *space = scalloc(1, sizeof(int));
+	*space = ((**(int**)b1 == 1) && (**(int**)b2 == 1));
+
+	int** ret = salloc(sizeof(int*));
+	*ret = space;
+	return (r_type_ptr)ret;
+}
+
+static r_type_ptr Or(r_type_ptr b1, r_type_ptr b2, Boolean_Template* this) {
+	int *space = scalloc(1, sizeof(int));
+	*space = ((**(int**)b1 == 1) || (**(int**)b2 == 1));
+
+	int** ret = salloc(sizeof(int*));
+	*ret = space;
+	return (r_type_ptr)ret;
+}
+
+static r_type_ptr Not(r_type_ptr b1, Boolean_Template* this) {
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Integer_Template/Integer_Template.h

@@ -1,0 +1,47 @@
+/*
+ * Generated by the RESOLVE to C translator. This file
+ * should not be modified.
+ */
+#ifndef __INTEGER_TEMPLATE_H
+#define __INTEGER_TEMPLATE_H
+
+#include "../../../../RESOLVE.h"
+#include "../../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
+
+typedef struct Integer_Template Integer_Template;
+struct Integer_Template {
+
+    void* Realization_Specific;
+    type_info* Integer;
+    r_type_ptr (*Is_Zero) (r_type_ptr, Integer_Template*);
+    r_type_ptr (*Is_Not_Zero) (r_type_ptr, Integer_Template*);
+    void (*Increment) (r_type_ptr, Integer_Template*);
+    void (*Decrement) (r_type_ptr, Integer_Template*);
+    r_type_ptr (*Less_Or_Equal) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Less) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Greater) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Greater_Or_Equal) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Sum) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Negate) (r_type_ptr, Integer_Template*);
+    r_type_ptr (*Difference) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Product) (r_type_ptr, r_type_ptr, Integer_Template*);
+/*    r_type_ptr (*Power) (r_type_ptr, r_type_ptr, Integer_Template*);
+    void (*Divide) (r_type_ptr, r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Mod) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Rem) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Quotient) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Div) (r_type_ptr, r_type_ptr, Integer_Template*);
+    r_type_ptr (*Are_Equal) (r_type_ptr, r_type_ptr, Integer_Template*);
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Integer_Template/Std_Integer_Realiz.c

@@ -1,0 +1,214 @@
+#include <limits.h>
+#include "Integer_Template.h"
+
+static int ValueOf(r_type_ptr r) {
+    return **((int**)r);
+}
+
+static r_type_ptr createFromInteger(int I, type_info* ti) {
+	int *space = scalloc(1, sizeof(int));
+	*space = I;
+	int** ret = salloc(sizeof(int*));
+	*ret = space;
+	return (r_type_ptr)ret;
+}
+
+static r_type_ptr createInteger(type_info* ti) {
+    int* t = scalloc(1, sizeof(int));
+    *t = 0;
+    int** ret = salloc(sizeof(int*));
+    *ret = t;
+    return (r_type_ptr)ret;
+}
+
+static void destroyInteger (r_type_ptr r, type_info* ti) {
+	sfree(*r);
+    sfree(r);
+}
+
+static type_info* newInteger() {
+    type_info* pc = scalloc(1, sizeof(type_info));
+    pc->create = createInteger;
+    pc->destroy = destroyInteger;
+    return pc;
+}
+
+static r_type_ptr Is_Zero(r_type_ptr i, Integer_Template* this) {
+	int *space = scalloc(1, sizeof(int));
+	*space = (**(int**)i == 0);
+
+	int** ret = salloc(sizeof(int*));
+	*ret = space;
+	return (r_type_ptr)ret;
+}
+
+static r_type_ptr Is_Not_Zero(r_type_ptr i, Integer_Template* this) {
+	int *space = scalloc(1, sizeof(int));
+	*space = (**(int**)i != 0);
+
+	int** ret = salloc(sizeof(int*));
+	*ret = space;
+	return (r_type_ptr)ret;
+}
+
+static void Increment(r_type_ptr i, Integer_Template* this) {
+	**(int**)i = **(int**)i + 1;
+}
+
+static void Decrement(r_type_ptr i, Integer_Template* this) {
+	**(int**)i = **(int**)i - 1;
+}
+
+static r_type_ptr Less_Or_Equal(r_type_ptr i1, r_type_ptr i2, Integer_Template* this) {
+	int *space = scalloc(1, sizeof(int));
+	*space = ((**(int**)i1 <= (**(int**)i2)));
+
+	int** ret = salloc(sizeof(int*));
+	*ret = space;
+	return (r_type_ptr)ret;
+}
+
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Static_Array_Template/Alt_Bin_Search_Realiz.rb

@@ -1,0 +1,65 @@
+Realization Alt_Bin_Search_Realiz (
+	Operation Are_Ordered(restores x,y: Entry): Boolean;
+		ensures Are_Ordered = true;
+) for Alt_Search_Capability of Static_Array_Template;
+
+(*
+    Operation Are_Ordered(restores x,y: Entry): Boolean;
+         ensures Are_Ordered = true;
+    Procedure 
+	Are_Ordered := True();
+    end; 
+
+
+    Operation Are_Equal(restores x, y: Entry): Boolean;
+	ensures Are_Equal = (x = y);
+    Procedure 
+	Are_Equal := And(Are_Ordered(x, y), Are_Ordered(y, x));
+    end; 
+*)
+
+    Procedure binarySearch(restores key: Entry; restores A: Static_Array; replaces result: Integer);
+	Var one, two: Integer;
+	Var low, mid, high: Integer;
+	Var midVal: Entry;
+	Var found: Boolean;
+(*
+	Increment(one);
+	Increment(two);
+	Increment(two);
+*)
+	found := False();
+	low := Replica(Lower_Bound);
+	high := Replica(Upper_Bound);
+
+	While (low <= high and not found)
+		changing low, mid, high, A, midVal, found;
+		maintaining true;
+		decreasing (high - low);
+	do
+		mid := Sum(low, high);
+		mid := Div(mid, 2);
+(*
+		Divide(Difference(high, low), two, mid);	-- this is really the quotient
+		mid := Sum(low, mid);
+*)
+		Swap_Entry(A, midVal, mid);
+		if (Are_Ordered(midVal, key) and Are_Ordered(key, midVal)) then
+			found := True();
+			Increment(low);				-- this is to satisfy the progress metric
+		else
+			if (Are_Ordered(midVal, key)) then
+				low := Sum(mid, 1);
+			else
+				high := Difference(mid, 1);
+			end;
+		end;
+		Swap_Entry(A, midVal, mid);
+	end;
+	If (found) then
+		result := Replica(mid);
+	else
+		result := Negate(Sum(Lower_Bound, 1));
+	end;	
+    end binarySearch;
+end Alt_Bin_Search_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Standard/Static_Array_Template/Bool_Bin_Search_Realiz.rb

@@ -1,0 +1,59 @@
+Realization Bool_Bin_Search_Realiz (
+	Operation Are_Ordered(restores x,y: Entry): Boolean;
+		ensures Are_Ordered = true;
+) for Bool_Search_Capability of Static_Array_Template;
+
+(*
+    Operation Are_Ordered(restores x,y: Entry): Boolean;
+         ensures Are_Ordered = True;
+    Procedure 
+	Are_Ordered := True();
+    end; 
+
+
+    Operation Are_Equal(restores x, y: Entry): Boolean;
+	ensures Are_Equal = (x = y);
+    Procedure 
+	Are_Equal := And(Are_Ordered(x, y), Are_Ordered(y, x));
+    end; 
+*)
+
+    Procedure binarySearch(restores key: Entry; restores A: Static_Array; replaces result: Boolean);
+	Var one, two: Integer;
+	Var low, mid, high: Integer;
+	Var midVal: Entry;
+(*
+	Increment(one);
+	Increment(two);
+	Increment(two);
+*)
+	result := False();
+	low := Replica(Lower_Bound);
+	high := Replica(Upper_Bound);
+
+	While (low <= high and not result)
+		changing low, mid, high, A, midVal, result;
+		maintaining true;
+		decreasing (high - low);
+	do
+		mid := Sum(low, high);
+		mid := Div(mid, 2);
+(*
+		Divide(Difference(high, low), two, mid);	-- this is really the quotient
+		mid := Sum(low, mid);
+*)
+		Swap_Entry(A, midVal, mid);
+		if (Are_Ordered(midVal, key) and Are_Ordered(key, midVal)) then
+			result := True();
+--			Increment(low);				-- this is to satisfy the progress metric
+		else
+			if (Are_Ordered(midVal, key)) then
+				low := Sum(mid, 1);
+			else
+				high := Difference(mid, 1);
+			end;
+		end;
+		Swap_Entry(A, midVal, mid);
+	end;
+    end binarySearch;
+end Bool_Bin_Search_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Concepts/Text_Template/Queue_Based_Realiz.rb

@@ -1,0 +1,28 @@
+Realization Queue_Based_Realiz for Text_Template;
+    uses Queue_Template;
+
+    -- the bound below is not right, so this implementation won't verify
+    Facility QF is Queue_Template(Character, 100)
+        realized by Circular_Array_Realiz;
+
+    Type Text = Record
+			Contents: QF. Queue;
+		end;
+		correspondence Conc.S = S.Contents;
+	end;
+ 
+    Procedure Add(restores C: Character; updates S: Text);
+        Var Temp: Character;
+
+        Temp := Replica(C);
+        Enqueue(Temp, S.Contents);
+    end Add;
+
+    Procedure Remove(updates C: Character; updates S: Text);
+        Dequeue(C, S.Contents);
+    end Remove;
+
+    Procedure Is_Empty(restores S: Text): Boolean;
+        Is_Empty := Length(S.Contents);
+    end Is_Empty;
+end Queue_Based_Realiz;

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Led_Examples/Leds_Test.h

@@ -1,0 +1,25 @@
+/*
+ * Generated by the RESOLVE to C translator. This file
+ * should not be modified.
+ */
+#ifndef __LEDS_TEST_H
+#define __LEDS_TEST_H
+
+#include "../../../RESOLVE.h"
+#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
+#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
+#include "../../../Main/Facilities/Standard/Std_Clock_Fac.h"
+#include "../../../Main/Concepts/Leds_Template/Leds_Template.h"
+#include "../../../Main/Concepts/Leds_Template/Std_Leds_Realiz.h"
+#include "../../../Main/Concepts/Leds_Template/Toggling_Realiz.h"
+
+typedef struct Led_Facility Led_Facility;
+struct Led_Facility {
+    Leds_Template* core;
+	Toggling_Capability_for_Leds_Template* Toggling_Capability;
+};
+Led_Facility Led_Facility_Var;
+void Leds_Test_create();
+void Leds_Test_destroy();
+
+#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Led_Examples/naive_malloc.c

@@ -1,0 +1,220 @@
+#ifdef DEBUG
+#include <stdio.h>
+#endif
+
+#include "naive_malloc.h"
+
+#define MAX_MEM 4096
+#define align4(x) (((((x)-1)>>2)<<2)+4)
+
+static void *stack[MAX_MEM];
+static void *base = NULL;
+static void *cur_brk = (void*)&stack[0];
+
+typedef struct block_t *block;
+
+struct block_t
+{
+	size_t size;
+	block next;
+	block prev;
+	int free;
+	int pad;
+	void *ptr;
+	char data[1];
+};
+
+
+#define BLOCK_SIZE (sizeof(struct block_t)-sizeof(char*))
+
+block get_block(void *p);
+int valid_addr(void *p);
+block fusion(block b);
+
+void split_block(block b, size_t size) 
+{
+	block new_block;
+	new_block = (void*)b->data + size;
+	new_block->size = b->size - size - BLOCK_SIZE;
+	new_block->free = 1;
+	b->size = size;
+	b->next = new_block;	
+	new_block->next = b->next;
+	new_block->prev = b;
+	new_block->ptr = new_block->data;
+}
+
+block find_block(block *last, size_t size) 
+{
+	block b = base;
+	while(b && !(b->free && b->size >= (size))) {
+		*last = b;
+		b = b->next;
+	}
+
+	return b;
+}
+
+void *stack_sbrk(int n)
+{
+	cur_brk += n;
+	if(cur_brk > (void*)&stack[MAX_MEM-1]) {
+		return (void*)-1;
+	}
+	return (void*)(cur_brk);		
+}
+
+void stack_brk(void *ptr)
+{
+	cur_brk = ptr;
+}
+
+block extend_stack(block last, size_t size)
+{
+	block b;
+	b = stack_sbrk(0);
+	if(stack_sbrk(BLOCK_SIZE + size) == (void*)-1) {
+		return NULL;
+	}
+	b->size = size;
+	b->next = NULL;
+	b->ptr = b->data;
+	if(last) {
+		last->next = b;
+		b->prev = last;
+	}
+	b->free = 0;
+	return b;
+}
+
+void *scalloc(int n, size_t size) {
+	size_t *new;
+	size_t s4, i;
+	new = salloc(n * size);
+	if(new) {
+		s4 = align4(n * size) << 2;
+		for(i = 0; i < s4; i++) {
+			new[i] = 0;
+		}
+	}
+	return (void*)new;
+}
[…]

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Standard/Std_Clock_Fac.c

@@ -1,0 +1,20 @@
+#include "Std_Clock_Fac.h"
+
+int Std_Clock_Fac_INSTANCE = 0;
+
+//If our facility has already been created, we don't want a new copy.
+void Std_Clock_Fac_create() {
+	if (Std_Clock_Fac_INSTANCE == 0) {
+		Std_Clock_Fac_Var.core = new_Std_Clock_Realiz_for_Clock_Template();
+		Std_Clock_Fac_INSTANCE = 1;
+	}
+}
+
+void Std_Clock_Fac_destroy() {
+	if (Std_Clock_Fac_INSTANCE == 1) {
+		free_Std_Clock_Realiz_for_Clock_Template(Std_Clock_Fac_Var.core);
+		Std_Clock_Fac_INSTANCE = 0;
+	}
+}
+
+

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Standard/Std_Clock_Fac.h

@@ -1,0 +1,22 @@
+/*
+ * Generated by the RESOLVE to C translator. This file
+ * should not be modified.
+ */
+#ifndef __STD_CLOCK_FAC_H
+#define __STD_CLOCK_FAC_H
+
+#include "../../../RESOLVE.h"
+#include "../../../Main/Facilities/Standard/Std_Boolean_Fac.h"
+#include "../../../Main/Facilities/Standard/Std_Integer_Fac.h"
+#include "../../../Main/Concepts/Clock_Template/Clock_Template.h"
+#include "../../../Main/Concepts/Clock_Template/Std_Clock_Realiz.h"
+
+typedef struct Std_Clock_Fac Std_Clock_Fac;
+struct Std_Clock_Fac {
+    Clock_Template* core;
+};
+Std_Clock_Fac Std_Clock_Fac_Var;
+void Std_Clock_Fac_create();
+void Std_Clock_Fac_destroy();
+
+#endif

### 2014-04-25 RESOLVE-Workspace/RESOLVE/Main/Facilities/Standard/Std_Integer_Fac.c

@@ -1,0 +1,18 @@
+#include "Std_Integer_Fac.h"
+
+int Std_Integer_Fac_INSTANCE = 0;
+
+//If our facility has already been created, we don't want a new copy.
+void Std_Integer_Fac_create() {
+	if (Std_Integer_Fac_INSTANCE == 0) {
+		Std_Integer_Fac_Var.core = new_Std_Integer_Realiz_for_Integer_Template();
+		Std_Integer_Fac_INSTANCE = 1;
+	}
+}
+
+void Std_Integer_Fac_destroy() {
+	if (Std_Integer_Fac_INSTANCE == 1) {
+		free_Std_Integer_Realiz_for_Integer_Template(Std_Integer_Fac_Var.core);
+		Std_Integer_Fac_INSTANCE = 0;
+	}
+}

### 2014-04-25 RESOLVE-Workspace/RESOLVE/RESOLVE.h

@@ -1,0 +1,41 @@
+#ifndef __RESOLVE_H
+#define __RESOLVE_H
+
+#include <stdlib.h>
+#include <string.h>
+#include <stdio.h>
+#include <stdarg.h>
+
+#include "naive_malloc.h"
+
+typedef void* rtype;
+typedef rtype* r_type_ptr;
+typedef struct type_info type_info;
+
+/*	Universal interface for resolve types.  This interface allows
+    initalization and finalization of objects without requiring those
+    objects to have any method pointers.  Of course this requires matching
+    type_info's to objects of their type.  Type_info pointers are passed
+    as parameters to methods when generic type manipulation is needed.
+    The fields are assigned values when realizations are created.  The
+    type_info is itself a field of a particular realization.
+
+    Inside the init function the PointerToFacility element can be properly
+    cast to the correct type.  For example..
+
+    static r_type_ptr init_Stack(type_info* stackType)
+    {
+        Stack_Template* ar = stackType->PointerToFacility;
+        .....
+    }*/
+
+struct type_info {
+    r_type_ptr (*create)(type_info* thisType);
+    void (*destroy)(r_type_ptr, type_info* thisType);
+    void* PointerToFacility;
+};
+
+// Globally accesible methods
+extern void swap(r_type_ptr A, r_type_ptr B);
+
+#endif

### 2014-04-25 tech-project/implementation.tex
added the smith reference back in and added the relationship diagram.

@@
 \begin{enumerate}
-\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
+\item Arriving at a translation model (or, strategy) for a relatively efficient, accurate C representation of RESOLVE.
 \item Implementing reusable mechanisms for carrying out the C code generation process.
@@
 
+The relationship between the RESOLVE module type and C code generated by our tools depicted at a high level in Figure \ref{fig:relationship}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=.55]{figs/relationship.pdf}
+\end{center}
+\caption{Native RESOLVE module files (left) and C files each produces (right).}
+\label{fig:relationship}
+\end{figure}
+
+Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
+Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
+Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
+RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
+
 The memory model must also be considered as an additional verifiable component.
@@
 To provide a straight forward translation from RESOLVE to C, we provide a dynamically-based memory allocator for use on embedded systems.
-
-The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
-Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
-Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
-Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
-RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
 

### 2014-04-25 tech-project/specify_led.tex
added the smith reference back in and added the relationship diagram.

@@
 This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
-Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
+Note that the ability to toggle is added \textit{on top} of this facility declaration in a similar fashion.
 The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
@@
 The \texttt{LED\_Telos\_Demo} facility above demonstrates these developments through its use of the ``\texttt{externally realized}" phrase.
-This signals to the RESOLVE compiler that the user is providing a non-native realization of the \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.
+This signals to the RESOLVE compiler that the user is providing a non-native realization of \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.
 
@@
 
-In the terms of embedded systems, these developments are especially as it allows us to write custom low level of the sort required for most embedded applications (e.g.
-LED strip drivers) while still providing formally specified interfaces that might later form the foundation .
-It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstract where we can concern ourselves exclusively with verified, native RESOLVE components.
+In the context of embedded systems, these developments are especially useful as we can now write custom, low level  drivers of the sort required for most embedded applications (e.g.
+LED strip drivers) while still providing extensible, formally specified interfaces.
+It is our hope and intention that new (native) RESOLVE components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstraction where we can concern ourselves exclusively with verified, native RESOLVE components.
 

### 2014-04-25 tech-project/implementation.tex
added work on the model of c translation

--- 2014-04-25 tech-project/implementation.tex
@@
 \section{Implementation}
-Development of our C translation tool can be logically partitioned into three distinct pieces: 
+Development of our C translation tool can be logically partitioned into three distinct phases: 
 \begin{enumerate}
-\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
+\item Arriving at a translation model (or, strategy) for an accurate C representation of RESOLVE.
 \item Implementing reusable mechanisms for carrying out the C code generation process.
@@
 \end{enumerate}
-In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.
+We illustrate each of these phases working in tandem on the LED component discussed in Section \ref{sec:specifiying}.
+
+%In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.
 
@@
 Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source.
-In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.
+In an effort to make such considerations, at the highest level, the C code we generate makes special considerations for facilities, concepts, and realizations.
 
-The memory model must also be considered as an additional verifiable component.
+\begin{figure}
+\begin{center}
+\includegraphics[scale=.55]{figs/relationship.pdf}
+\end{center}
+\caption{Relationship between RESOLVE module types and the C code generated from each.}
+\label{fig:relationship}
+\end{figure}
+
+\subsubsection{Concepts}
+Concepts produce a single .h that provide function pointers for each operation specified by the original concept, as well as structs for each user defined type.
+
+\subsubsection{Facilities}
+Facilities produce an .h/.c pair: The header .h declares methods that are intended to manage the creation and destruction of all global variables used within the facility, while the .c provides an implementation of these methods.
+Note that the create and destroy methods are only responsible for freeing \textit{global} variables, all other translated, local functions are responsible for deallocating their own variables.
+
+\subsubsection{Realizations}
+We treat realizations of concepts and enhancements slightly different than facility modules.
+While a .h/.c pair is still produced, the create method for realizations is designed to create instances of all types specified by the concept, while the destroy method deallocates these types.
+
+%The .h/.c pair generated for realizations include
+
+%While facilities, concept realizations, and enhancement realizations in general produce an .h/.c pair, the .h produced for facility modules differs slightly from the others: Whereas realizations of concepts and enhancements provide
+
+% concept realizations provides methods for creating and destroying a single instance of the type declared by the concept it realizes.
+However, header files for realizations of facility modules provide methods creating and destroying all global variables within the facility.
+Common global variables include the set of standard facilities provided to every module in addition to any locally defined within the scope of the facility.
+
+% responsible for declaring functions that create and destroy the objects used
+
+%The memory model must also be considered as an additional verifiable component.
 Currently, RESOLVE is not capable of creating a complete specification of memory\footnote{RESOLVE is an object based language and has variable sized structures.
@@
 
-The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.
-Unsurprisingly, concepts are represented in C by a single header \texttt{.h}.
-Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE.
-Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept.
-RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.
-
 %Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
@@
 
-\subsubsection{AST Traversal}
-Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
+Translation itself is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
+The traversal mechanism used is a derivative of the visitor patter that provides a pre post traversal over all nodes in the tree.
+
+%\subsubsection{AST Traversal}
+%Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
 The traversal mechanism used is a dervivative of the visitor pattern that provides a SAX-dom style pre-post traversal over all nodes in the tree.
@@
 
-To make this more concrete, consider the following dummy operation.
+%To make this more concrete, consider the following dummy operation.
 
-\begin{verbatim}
-Operation Nothing(); Procedure
-        Var X : Integer;
-        X := 3;
-end Nothing;
-\end{verbatim}
+%\begin{verbatim}
+%Operation Nothing(); Procedure
+%        Var X : Integer;
+%        X := 3;
+%end Nothing;
+%\end{verbatim}
 
-Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
+%Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
 Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack.
@@
 
-We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
+%We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
 
-\begin{itemize}
-\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
+%\begin{itemize}
+%\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
 
-\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.
+%\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.
 
-\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
+%\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
 This makes it easy to tweak and optimize the size of the translator's codebase, implementing only visit method for language constructs that explicitly require translation.
-\end{itemize}
+%\end{itemize}
 
-\subsubsection{Translation output}
-Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
+%\subsubsection{Translation output}
+%Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
 Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.
 
-An example C function definition template is shown below.
+%An example C function definition template is shown below.
 
-\begin{verbatim}
-function_def(modifier, type, name, params, 
-                               vars, stmts) ::= <<
-<modifier> <type> <name> (<params; sep = ", ">) {
-    <vars; sep = "\n">
-    <stmts; sep = "\n">
-}>>
-\end{verbatim}
+%\begin{verbatim}
+%function_def(modifier, type, name, params, 
+%                               vars, stmts) ::= <<
+%<modifier> <type> <name> (<params; sep = ", ">) {
+%    <vars; sep = "\n">
+%    <stmts; sep = "\n">
+%}>>
+%\end{verbatim}
 
-User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
+%User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
 It is entirely up to the user to define which attributes to fill in, and how complex they want them to be.
@@
 
-\begin{verbatim}
-parameter(type, name) ::= "<type> <name>"
-\end{verbatim}
+%\begin{verbatim}
+%parameter(type, name) ::= "<type> <name>"
+%\end{verbatim}
 
-In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
+%In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
 For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in.
@@
 
-Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
+%Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
 This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).

### 2014-04-25 tech-project/specify_led.tex
added work on the model of c translation

@@
 Indeed, after having written the concept, the RESOLVE programmer would ideally provide it with a verifiable, native RESOLVE implementation.
-However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by directly manipulating hardware pins provided by msp430's chipset.
+However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by directly manipulating hardware pins provided by the msp430's chipset.
 

### 2014-04-25 tech-project/implementation.tex
working on memory allocation

--- 2014-04-25 tech-project/implementation.tex
@@
 
-\subsection{Memory Allocation}
+%%%%%%%%%%%%%%%%%%%%%%%
+%           Memory Allocation Section              %
+%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Memory Allocation}\label{sec:mem}
 
@@
 
-The \texttt{salloc()} is a first fit memory allocator.
-Rather than allocating on the heap, \texttt{salloc()} uses the stack.
-At compilation, the allocator provisions a fixed size of memory.
-It requires a small section of meta-data called a block which contains information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
-A sample representation of the stack shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
+The function \texttt{salloc()}, uses a first fit approach for allocation on the stack, rather than conventional, heap-based allocators.
+This approach requires that a fixed size of memory is chosen at compilation.
+In addition, \texttt{salloc()}, requires a section of meta-data, which is denoted as a \texttt{block}, for each record in the memory pool.
+A \texttt{block} holds referential information of neighboring blocks, the size of the record the block maintains, and if the block is free or is in use.
+Figure~\ref{fig:stack} is an example of the stack after several calls to \texttt{salloc()}.
 
@@
 \caption{Representation of memory stack}
+\label{fig:stack}
 \end{figure}
-\label{fig:stack}
 
@@
 
-A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated for something else.
-The \texttt{sfree()} operation is an analogous implementation to the standard C \texttt{free()} function for the stack.
+A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated.
+The \texttt{sfree()} function provides deallocation for memory allocated with \texttt{salloc()}.
+Figure~\ref{fig:free} shows an example set of memory before and after calling \texttt{sfree()}.
 
@@
 \caption{sfree to free memory}
+\label{fig:free}
 \end{figure}
-\label{fig:free}
 
-\subsubsection{Optimizations}
+\subsubsection{Optimizing Memory Usage}
+
+A common problem that can occur in memory allocation is fragmentation.
+During execution, a program can allocate and deallocate an arbitrary number of times.
+Figure~\ref{fig:fragmentation} shows problems that result from this.
+This problem is magnified on embedded systems due to their limited memory capacities.
+There are simple optimizations that can reduce fragmentation.
+
+Block splitting, as shown in Figure~\ref{fig:split}, occurs during allocation. It allows blocks of greater size to be partitioned into the size requested by the allocator.
 
@@
 \caption{fragmentation}
+\label{fig:fragmentation}
 \end{figure}
-\label{fig:fragmentation}
 
@@
 \caption{block splitting}
+\label{fig:split}
 \end{figure}
-\label{fig:split}
 

### 2014-04-25 tech-project/implementation.tex
redid the translation implementation section

--- 2014-04-25 tech-project/implementation.tex
@@
 
-%In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.
-
 \subsection{C Translation Model}
@@
 In an effort to make such considerations, at the highest level, the C code we generate makes special considerations for facilities, concepts, and realizations.
+This scheme is depicted in Figure \ref{fig:relationship} and briefly summarized in Sections \ref{sec:conceptoverview} - \ref{sec:facilitiesrealizations}.
 
@@
 \begin{center}
-\includegraphics[scale=.55]{figs/relationship.pdf}
+\includegraphics[scale=.60]{figs/relationship.pdf}
 \end{center}
@@
 \subsubsection{Concepts}
-Concepts produce a single .h that provide function pointers for each operation specified by the original concept, as well as structs for each user defined type.
+\label{sec:conceptoverview}
+Concept modules produce a single .h file, which provides function pointers for the operations specified in the original concept, as well as structs representing each user defined type.
 
 \subsubsection{Facilities}
+\label{sec:facilitiesoverview}
 Facilities produce an .h/.c pair: The header .h declares methods that are intended to manage the creation and destruction of all global variables used within the facility, while the .c provides an implementation of these methods.
-Note that the create and destroy methods are only responsible for freeing \textit{global} variables, all other translated, local functions are responsible for deallocating their own variables.
+Note that these create and destroy methods are only responsible for freeing \textit{global} variables.
+All other translated local functions are responsible for deallocating their own local variables.
 
 \subsubsection{Realizations}
+\label{sec:facilitiesrealizations}
 We treat realizations of concepts and enhancements slightly different than facility modules.
-While a .h/.c pair is still produced, the create method for realizations is designed to create instances of all types specified by the concept, while the destroy method deallocates these types.
-
-%The .h/.c pair generated for realizations include
-
-%While facilities, concept realizations, and enhancement realizations in general produce an .h/.c pair, the .h produced for facility modules differs slightly from the others: Whereas realizations of concepts and enhancements provide
-
-% concept realizations provides methods for creating and destroying a single instance of the type declared by the concept it realizes.
-However, header files for realizations of facility modules provide methods creating and destroying all global variables within the facility.
-Common global variables include the set of standard facilities provided to every module in addition to any locally defined within the scope of the facility.
-
-% responsible for declaring functions that create and destroy the objects used
+While a .h/.c pair is still produced, the create method designated in the header for realizations is designed to create instances of all types specified by the concept, while the destroy method deallocates these types -- as opposed to simply destroying user created globals.
 
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=.55]{figs/ast_traversal2.pdf}
+\end{center}
+\caption{The general flow of information from C translators walk of the AST (first), to user defined templates (middle), ending with formed output (last).}
+\label{fig:ast}
+\end{figure*}
+
 \subsection{Translator Implementation}
 
-Translation itself is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
-The traversal mechanism used is a derivative of the visitor patter that provides a pre post traversal over all nodes in the tree.
+The C code generation process takes place over the course of a traversal of RESOLVE's abstract syntax tree (AST).
+The traversal mechanism used is a derivative of the visitor pattern that provides a pre post traversal over all nodes in the tree.
 
@@
 
-%To make this more concrete, consider the following dummy operation.
+To illustrate the general process of producing runnable C from RESOLVE code, consider the following dummy operation:
 
-%\begin{verbatim}
-%Operation Nothing(); Procedure
-%        Var X : Integer;
-%        X := 3;
-%end Nothing;
-%\end{verbatim}
+\begin{verbatim}
+Operation Nothing(); Procedure
+        Var X : Integer;
+        X := 3;
+end Nothing;
+\end{verbatim}
 
-%Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
-Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack.
-Each of these calls are received in the translator in the order in which they are visited within the tree.
+%%LOOK AT ME
+%This separation between the RESOLVE source tree and the view, allows us to easily modify and tweak the code produced by our tool and allows us easily represent arbitrarily complicated output
+
+Shown in Figure \ref{fig:ast} is a high level depiction of steps taken in translating this operation to C.
+The first box depicts the AST of \texttt{Nothing}, where nodes are represented with boxes labeled by the constructs they contain.
+Throughout the walk of this tree, useful information (such as the operation's name, ``Nothing") are extracted from the nodes containing these constructs, and added to the externally defined string-template\footnote{A template can simply be thought of as a ``document with holes" which the user choses when and how to fill}, \texttt{c\_function\_def} template.
+
+In the context of RESOLVE to C translation, these templates, when filled during the aforementioned pre-post visitor traversal of RESOLVE's AST, help simplify the task of producing complicated, arbitrarily nested blocks of structured C output by keeping translation logic strictly within the C translator, and output logic strictly within the templates.
+
+That is, the only actual work being performed within the C translator is forwarding information gathered from individual treenodes, to a series of externally defined templates.
+This allows us to exploit (in design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates which shape our output (view).
+
+We feel this approach lends itself the challenge discussed in this paper, as this separation allows us to easily iterate changes to our generated C code without needing to concern ourselves with a line of Java inside the compiler itself.
+This allows us to easily tweak code and make arbitrarily complicated changes and optimizations to the code -- some of which are detailed later in Section \#.
+
+% general flow Each of these calls are received in the translator in the order in which they are visited within the tree.
 It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
-
-%We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
-
-%\begin{itemize}
-%\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
-
-%\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.
-
-%\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
-This makes it easy to tweak and optimize the size of the translator's codebase, implementing only visit method for language constructs that explicitly require translation.
-%\end{itemize}
 
@@
 
-%One of the primary allures of this approach to translation is that that adheres to strict MVC design principles -- meaning that all output logic is distinctly separated from translation related logic.
-
-%We take advantage of these pre post methods using templates and simple stack to implement
-
-%Going even further, we demonstrate this by showing the steps taken to translate a simple operation declaration \texttt{nothing} to C.
-
-% for each construct to remain encapsulated within that method, and (almost) completely eliminates the need for complex loop or iteration mechanisms.
-
-%This particular traversal pattern lends itself well to the language translation challenge (specifically source to source) where the pre methods align naturally with beginning of a construct, and conclude with its corresponding post method.
-For instance, in the case above, this allows us, upon receiving a callback for In an effort to keep logic implementing our translator distinct and separate from the output language, we used a model view controller framework for implementing
-
-%To illustrate this, consider once again facility \texttt{DoNothing}.
-
 \subsection{Memory Allocation}
 
-Dynamic memory allocation does not lend itself well with an embedded programming paradigm.
-With hardware constraints, embedded systems have limited capacities on RAM.
-The telos motes are limited to 128 bytes of RAM.
-Many programs, however, require dynamic memory allocation to be used, including RESOLVE, in order to make it extensible.
+Dynamic memory allocation is not typically the first choice for most embedded applications.
+With the telos mote itself  limited to 128 bytes of RAM, hardware and memory constraints such as these, developers of embedded applications tend to favor static memory allocation over dynamic.
+Many programs, however benefit greatly from dynamic memory allocation not only in terms of clarity and straightforward to be used, including RESOLVE, in order to make it extensible.
 Previous RESOVE translations to C required static memory allocation \cite{regula:2010}.

### 2014-04-25 tech-project/implementation.tex
tweaked and added info to the start of the memory allocation section

@@
 \end{enumerate}
-We illustrate each of these phases working in tandem on the LED component discussed in Section \ref{sec:specifiying}.
+We conclude this section with a demonstration of each of these phases working in tandem on the LED component discussed in Section \ref{sec:specifiying}.
 
@@
 Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source.
-In an effort to make such considerations, at the highest level, the C code we generate makes special considerations for facilities, concepts, and realizations.
+In an effort to make such considerations, at the highest level, the C code we generate makes special considerations for concepts, facilities, and realizations.
 This scheme is depicted in Figure \ref{fig:relationship} and briefly summarized in Sections \ref{sec:conceptoverview} - \ref{sec:facilitiesrealizations}.
@@
 \label{sec:conceptoverview}
-Concept modules produce a single .h file, which provides function pointers for the operations specified in the original concept, as well as structs representing each user defined type.
+Concept modules produce a single .h file, which provide function pointers for the operations specified in the original concept, as well as structs representing each user defined type.
 
@@
 \label{sec:facilitiesoverview}
-Facilities produce an .h/.c pair: The header .h declares methods that are intended to manage the creation and destruction of all global variables used within the facility, while the .c provides an implementation of these methods.
-Note that these create and destroy methods are only responsible for freeing \textit{global} variables.
-All other translated local functions are responsible for deallocating their own local variables.
+Facilities produce an .h/.c pair: The header .h declares both a ``create" and ``destroy" method which, taken together, encapsulates the creation and destruction of all global variables used within the facility.
+The .c provides an implementation of these methods.
+Note that these create and destroy methods are only responsible for freeing \textit{global} variables -- meaning all other translated functions are responsible for deallocating their own local variables.
 
@@
 \end{center}
-\caption{The general flow of information from C translators walk of the AST (first), to user defined templates (middle), ending with formed output (last).}
+\caption{The general flow of information from the AST (first), to user defined templates (middle), ending with formed output (last).}
 \label{fig:ast}
@@
 
-The C code generation process takes place over the course of a traversal of RESOLVE's abstract syntax tree (AST).
-The traversal mechanism used is a derivative of the visitor pattern that provides a pre post traversal over all nodes in the tree.
+Translation itself occurs over the course of a traversal of RESOLVE's abstract syntax tree (AST) -- an intermediate representation of RESOLVE code.
+The traversal mechanism utilized is a derivative of the visitor pattern that provides a pre post traversal over all nodes in the tree.
 
@@
 
-%%LOOK AT ME
-%This separation between the RESOLVE source tree and the view, allows us to easily modify and tweak the code produced by our tool and allows us easily represent arbitrarily complicated output
-
 Shown in Figure \ref{fig:ast} is a high level depiction of steps taken in translating this operation to C.
 The first box depicts the AST of \texttt{Nothing}, where nodes are represented with boxes labeled by the constructs they contain.
-Throughout the walk of this tree, useful information (such as the operation's name, ``Nothing") are extracted from the nodes containing these constructs, and added to the externally defined string-template\footnote{A template can simply be thought of as a ``document with holes" which the user choses when and how to fill}, \texttt{c\_function\_def} template.
+Throughout the walk of this tree, useful information (such as the operation's name, ``Nothing") are extracted from the nodes containing these constructs, and added to a user defined string-template\footnote{A template can simply be thought of as a ``document with holes" which the user choses when and how to fill.}, in this case: \texttt{c\_function\_def}.
 
@@
 
-We feel this approach lends itself the challenge discussed in this paper, as this separation allows us to easily iterate changes to our generated C code without needing to concern ourselves with a line of Java inside the compiler itself.
-This allows us to easily tweak code and make arbitrarily complicated changes and optimizations to the code -- some of which are detailed later in Section \#.
+We feel this approach lends itself well to the challenge discussed in this paper, as this separation allows us to easily iterate changes to our generated C code without needing to concern ourselves with the Java written inside the compiler itself.
+This allows us to easily and iteratively tweak generated code -- making arbitrarily complicated changes and optimizations, some of which are detailed later in Section \#.
 
@@
 
-Dynamic memory allocation is not typically the first choice for most embedded applications.
-With the telos mote itself  limited to 128 bytes of RAM, hardware and memory constraints such as these, developers of embedded applications tend to favor static memory allocation over dynamic.
-Many programs, however benefit greatly from dynamic memory allocation not only in terms of clarity and straightforward to be used, including RESOLVE, in order to make it extensible.
-Previous RESOVE translations to C required static memory allocation \cite{regula:2010}.
-In this section a stack based dynamic memory allocator is introduced.
+Any model seeking to convert RESOLVE to a lower level representation such as C demands a strategy for handling any memory utilized by the generated code.
+While dynamic allocation is typically the norm, it is not however the first choice for embedded applications.
+With the Telos mote constrained to 128 bytes of RAM, developers targeting embedded platforms tend to favor static memory allocation over dynamic, due the memory efficiency it affords.
+
+%Many programs however benefit greatly from dynamic memory allocation not only in terms of clarity and straightforwardness, but in our case: Accurately modeling exactly what the code being executed is doing.
+%NesC, for example, while giving the illusion of dynamic allocation, behind the scenes actually performs static allocation
+
+In spite of this, our reasoning for choosing to pursue dynamic allocation over static, rests in the language itself.
+Being a language that relies heavily on the notion of formally specified objects (components), everything in RESOLVE from the `primitive' types such as booleans and integers, to the more complicated (user defined) ones such as Stacks and Queues, are modeled, specified, and implemented in the same way: Using the standard RESOLVE machinery discussed in Section \ref{sec:specifiying}.
+
+As such, even the simplest RESOLVE programs still rely heavily on the notion of objects coming and going.
+Thus, from a verification perspective, creating a tool that allows our translated code to create and destroy such objects in the manner the language itself uses is an important component to capture in formally verified code.
 
@@
 
-The \texttt{salloc()} is a first fit memory allocator.
-Rather than allocating on the heap, \texttt{salloc()} uses the stack.
+The particular allocation scheme that we chose to use is \texttt{salloc()}: A first fit memory allocator.
+Rather than allocating memory on the heap, \texttt{salloc()} instead uses the stack.
 At compilation, the allocator provisions a fixed size of memory.

### 2014-04-25 tech-project/specify_led.tex
redid the translation implementation section
tweaked and added info to the start of the memory allocation section

@@
 \includegraphics[scale=.55]{figs/component_graph.pdf}
-\caption{A diagram illustrating inter-component relationships for the example in Section \ref{sec:specifying}}
+\caption{A diagram illustrating inter-component relationships for the example in Section 3.
+The files listed in cloud shapes indicate externally realized components, while the dotted line separating these from others indicates the current boundary between the lowest-level, hardcoded components in RESOLVE, and native RESOLVE abstractions sitting on top of these hardcoded components.}
 \end{figure*}
@@
 %mention performance stuff in future work section.
-
-\begin{figure*}
-\centering
-\includegraphics[scale=.55]{figs/ast_traversal.pdf}
-\caption{A RESOLVE operation AST, the walk call sequence, and sample translation output.}
-\end{figure*}
-\label{fig:ast}

### 2014-04-25 tech-project/implementation.tex
adding led demo tex

--- 2014-04-25 tech-project/implementation.tex
@@
 
+%In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.
+
 \subsection{C Translation Model}
@@
 In an effort to make such considerations, at the highest level, the C code we generate makes special considerations for facilities, concepts, and realizations.
-This scheme is depicted in Figure \ref{fig:relationship} and briefly summarized in Sections \ref{sec:conceptoverview} - \ref{sec:facilitiesrealizations}.
 
@@
 \begin{center}
-\includegraphics[scale=.60]{figs/relationship.pdf}
+\includegraphics[scale=.55]{figs/relationship.pdf}
 \end{center}
@@
 \subsubsection{Concepts}
-\label{sec:conceptoverview}
-Concept modules produce a single .h file, which provides function pointers for the operations specified in the original concept, as well as structs representing each user defined type.
+Concepts produce a single .h that provide function pointers for each operation specified by the original concept, as well as structs for each user defined type.
 
 \subsubsection{Facilities}
-\label{sec:facilitiesoverview}
 Facilities produce an .h/.c pair: The header .h declares methods that are intended to manage the creation and destruction of all global variables used within the facility, while the .c provides an implementation of these methods.
-Note that these create and destroy methods are only responsible for freeing \textit{global} variables.
-All other translated local functions are responsible for deallocating their own local variables.
+Note that the create and destroy methods are only responsible for freeing \textit{global} variables, all other translated, local functions are responsible for deallocating their own variables.
 
 \subsubsection{Realizations}
-\label{sec:facilitiesrealizations}
 We treat realizations of concepts and enhancements slightly different than facility modules.
-While a .h/.c pair is still produced, the create method designated in the header for realizations is designed to create instances of all types specified by the concept, while the destroy method deallocates these types -- as opposed to simply destroying user created globals.
+While a .h/.c pair is still produced, the create method for realizations is designed to create instances of all types specified by the concept, while the destroy method deallocates these types.
+
+%The .h/.c pair generated for realizations include
+
+%While facilities, concept realizations, and enhancement realizations in general produce an .h/.c pair, the .h produced for facility modules differs slightly from the others: Whereas realizations of concepts and enhancements provide
+
+% concept realizations provides methods for creating and destroying a single instance of the type declared by the concept it realizes.
+However, header files for realizations of facility modules provide methods creating and destroying all global variables within the facility.
+Common global variables include the set of standard facilities provided to every module in addition to any locally defined within the scope of the facility.
+
+% responsible for declaring functions that create and destroy the objects used
 
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=.55]{figs/ast_traversal2.pdf}
-\end{center}
-\caption{The general flow of information from C translators walk of the AST (first), to user defined templates (middle), ending with formed output (last).}
-\label{fig:ast}
-\end{figure*}
-
 \subsection{Translator Implementation}
 
-The C code generation process takes place over the course of a traversal of RESOLVE's abstract syntax tree (AST).
-The traversal mechanism used is a derivative of the visitor pattern that provides a pre post traversal over all nodes in the tree.
+Translation itself is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
+The traversal mechanism used is a derivative of the visitor patter that provides a pre post traversal over all nodes in the tree.
 
@@
 
-To illustrate the general process of producing runnable C from RESOLVE code, consider the following dummy operation:
+%To make this more concrete, consider the following dummy operation.
 
-\begin{verbatim}
-Operation Nothing(); Procedure
-        Var X : Integer;
-        X := 3;
-end Nothing;
-\end{verbatim}
+%\begin{verbatim}
+%Operation Nothing(); Procedure
+%        Var X : Integer;
+%        X := 3;
+%end Nothing;
+%\end{verbatim}
 
-%%LOOK AT ME
-%This separation between the RESOLVE source tree and the view, allows us to easily modify and tweak the code produced by our tool and allows us easily represent arbitrarily complicated output
+%Shown in Figure \ref{fig:ast} is the AST representation of operation \texttt{Nothing}.
+Here, language constructs are represented as labeled boxes, while the actual traversal over these constructs -- and the order in which it is performed -- is communicated on the right via the call stack.
+Each of these calls are received in the translator in the order in which they are visited within the tree.
+It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
 
-Shown in Figure \ref{fig:ast} is a high level depiction of steps taken in translating this operation to C.
-The first box depicts the AST of \texttt{Nothing}, where nodes are represented with boxes labeled by the constructs they contain.
-Throughout the walk of this tree, useful information (such as the operation's name, ``Nothing") are extracted from the nodes containing these constructs, and added to the externally defined string-template\footnote{A template can simply be thought of as a ``document with holes" which the user choses when and how to fill}, \texttt{c\_function\_def} template.
+%We feel this particular traversal pattern lends itself to task of source to source translation for the following reasons:
 
-In the context of RESOLVE to C translation, these templates, when filled during the aforementioned pre-post visitor traversal of RESOLVE's AST, help simplify the task of producing complicated, arbitrarily nested blocks of structured C output by keeping translation logic strictly within the C translator, and output logic strictly within the templates.
+%\begin{itemize}
+%\item A visit method for a construct provides a convenient encapsulation of all the logic required to translate RESOLVE construct $x$ to appropriate C construct $y$.
 
-That is, the only actual work being performed within the C translator is forwarding information gathered from individual treenodes, to a series of externally defined templates.
-This allows us to exploit (in design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates which shape our output (view).
+%\item Overriden visit methods apply to every instance of a construct -- meaning RESOLVE's C translator requires few (if any) loops, as the walk itself serves as the method of iteration.
 
-We feel this approach lends itself the challenge discussed in this paper, as this separation allows us to easily iterate changes to our generated C code without needing to concern ourselves with a line of Java inside the compiler itself.
-This allows us to easily tweak code and make arbitrarily complicated changes and optimizations to the code -- some of which are detailed later in Section \#.
-
-% general flow Each of these calls are received in the translator in the order in which they are visited within the tree.
-It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
+%\item Finally, only the visit methods for the constructs we currently wish to process need to be overridden.
+This makes it easy to tweak and optimize the size of the translator's codebase, implementing only visit method for language constructs that explicitly require translation.
+%\end{itemize}
 
@@
 
-\subsection{Memory Allocation}
+%One of the primary allures of this approach to translation is that that adheres to strict MVC design principles -- meaning that all output logic is distinctly separated from translation related logic.
 
-Dynamic memory allocation is not typically the first choice for most embedded applications.
-With the telos mote itself  limited to 128 bytes of RAM, hardware and memory constraints such as these, developers of embedded applications tend to favor static memory allocation over dynamic.
-Many programs, however benefit greatly from dynamic memory allocation not only in terms of clarity and straightforward to be used, including RESOLVE, in order to make it extensible.
-Previous RESOVE translations to C required static memory allocation \cite{regula:2010}.
-In this section a stack based dynamic memory allocator is introduced.
+%We take advantage of these pre post methods using templates and simple stack to implement
+
+%Going even further, we demonstrate this by showing the steps taken to translate a simple operation declaration \texttt{nothing} to C.
+
+% for each construct to remain encapsulated within that method, and (almost) completely eliminates the need for complex loop or iteration mechanisms.
+
+%This particular traversal pattern lends itself well to the language translation challenge (specifically source to source) where the pre methods align naturally with beginning of a construct, and conclude with its corresponding post method.
+For instance, in the case above, this allows us, upon receiving a callback for In an effort to keep logic implementing our translator distinct and separate from the output language, we used a model view controller framework for implementing
+
+%To illustrate this, consider once again facility \texttt{DoNothing}.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%           Memory Allocation Section              %
+%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Memory Allocation}\label{sec:mem}
+
+Memory limitations on embedded hardware has made dynamic memory allocation a difficult, or impossible practice.
+Many existing programs, including RESOLVE, however,  inherently use heap-based memory.
+Previous attempts at a RESOLVE to C translation required a constant size for each variable declaration\cite{regula:2010}.
+This approach can provide efficient use of memory for embedded systems, it does not, however, provide a straight forward approach to translation.
+In this section, we introduce a RESOLVE wrapped dynamic memory allocator implemented on the stack.
 
@@
 
-The \texttt{salloc()} is a first fit memory allocator.
-Rather than allocating on the heap, \texttt{salloc()} uses the stack.
-At compilation, the allocator provisions a fixed size of memory.
-It requires a small section of meta-data called a block which contains information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
-A sample representation of the stack shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
+The function \texttt{salloc()}, uses a first fit approach for allocation on the stack, rather than conventional, heap-based allocators.
+This approach requires that a fixed size of memory is chosen at compilation.
+In addition, \texttt{salloc()}, requires a section of meta-data, which is denoted as a \texttt{block}, for each record in the memory pool.
+A \texttt{block} holds referential information of neighboring blocks, the size of the record the block maintains, and if the block is free or is in use.
+Figure~\ref{fig:stack} is an example of the stack after several calls to \texttt{salloc()}.
 
 \begin{figure}[!htb]
-\centering
+%\centering
 \includegraphics[scale=.55]{figs/stack.pdf}
-\caption{Representation of memory stack}
+\caption{Representation of memory using salloc()}
+Memory allocated with salloc() allocates a block in front of data allocated. Blocks point to their immediate neighbors and hold their size and usage.
+\label{fig:stack}
 \end{figure}
-\label{fig:stack}
 
@@
 
-A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated for something else.
-The \texttt{sfree()} operation is an analogous implementation to the standard C \texttt{free()} function for the stack.
+A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated.
+The \texttt{sfree()} function provides deallocation for memory allocated with \texttt{salloc()}.
+Figure~\ref{fig:free} shows an example set of memory before and after calling \texttt{sfree()}.
 
 \begin{figure}[!htb]
-\centering
+%\centering
 \includegraphics[scale=.55]{figs/sfree.pdf}
 \caption{sfree to free memory}
+\label{fig:free}
 \end{figure}
-\label{fig:free}
 
-\subsubsection{Optimizations}
+\subsubsection{Optimizing Memory Usage}
 
 A common problem that can occur in memory allocation is fragmentation.
-As shown in figure \ref{fig:fragmentation}, fragmentation can lead to inefficient and increased memory usage.
-This problem is magnified on embedded systems with limited memory capabilities.
-Simple optimizations can be made however to reduce fragmentation.
-Splitting is one optimization that \texttt{salloc()} to maximize memory usage.
-Shown in figure \ref{fig:split}, blocks can be split to the size that is required.
-Another means of optimizing memory usage is joining together freed blocks.
-When a call to \texttt{sfree()} is made, neighboring blocks are coalesced together, as shown in figure \ref{fig:fuse}.
+During execution, a program can allocate and deallocate an arbitrary number of times.
+Figure~\ref{fig:fragmentation} shows problems that result from this.
+This problem is magnified on embedded systems due to their limited memory capacities.
+There are simple optimizations that can reduce fragmentation.
+
+Block splitting, as shown in Figure~\ref{fig:split}, occurs during allocation. It allows blocks of greater size to be partitioned into the size requested by the allocator.
+
+Fusing blocks is another technique used when \texttt{sfree()} is called.
+When memory is deallocated, neighboring free blocks are coalesced to form a single large block, as shown in Figure~\ref{fig:fuse}.
 
 \begin{figure}[!htb]
-\centering
+%\centering
 \includegraphics[scale=.55]{figs/fragmentation.pdf}
 \caption{fragmentation}
+\label{fig:fragmentation}
+Performing many naive allocation and deallocations, allocatable blocks are restricted to those that match the exact size of memory requested from the allocator.
 \end{figure}
-\label{fig:fragmentation}
 
 \begin{figure}[!htb]
-\centering
+%\centering
 \includegraphics[scale=.55]{figs/split.pdf}
 \caption{block splitting}
+Splitting of a free block creates two new blocks: a block that is the size that the allocator requested, and the other contains the remainder of a new free block with the remainder of memory.
+\label{fig:split}
 \end{figure}
-\label{fig:split}
 
 \begin{figure}[!htb]
-\centering
+%\centering
 \includegraphics[scale=.55]{figs/fuse.pdf}
 \caption{block fusing}
+An example of fusing blocks together. This creates single larger block, decreasing the number of smaller blocks unable to split.
+\label{fig:fuse}
 \end{figure}
-\label{fig:fuse}
-%A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation. 
-%To date there have been very few practical applications of verifiable code on physical media.
 
-\subsection{An LED Implementation}
-
-\begin{verbatim}
-void LED_Telos_create() {
-		Std_Boolean_Fac_create();
-		Std_Integer_Fac_create();
-		Std_Clock_Fac_create();
-		r_type_ptr __arg_0 = Std_Integer_Fac_Var.core->createFromInteger(4, Std_Integer_Fac_Var.core->Integer);
-		LED_Telos_Facility_Var.core = new_Std_LED_Realiz_for_Leds_Template(__arg_0);
-		LED_Telos_Facility_Var.Toggling_Capability = new_Toggling_Capability_of_Leds_Template(LED_Telos_Facility_Var.core);
-		Std_Integer_Fac_Var.core->Integer->destroy(__arg_0, Std_Integer_Fac_Var.core->Integer);
-}
-\end{verbatim}
+%
+%

### 2014-04-25 tech-project/led_trans.tex
adding led demo tex

% An LED Demo Translation
\section{LED Demo}

\begin{figure}
\centering
\begin{verbatim}
/*
 * Generated by the RESOLVE to C translator. 
 * This file should not be modified.
 */
#ifndef __LEDS_TEST_H
#define __LEDS_TEST_H

#include ".../RESOLVE.h"
#include ".../Facilities/.../Std_Boolean_Fac.h"
#include ".../Facilities/.../Std_Integer_Fac.h"
#include ".../Facilities/.../Std_Clock_Fac.h"
#include ".../Concepts/.../Leds_Template.h"
#include ".../Concepts/.../Std_Leds_Realiz.h"
#include ".../Concepts/.../Toggling_Realiz.h"

typedef struct Led_Facility Led_Facility;
struct Led_Facility {
    Leds_Template* core;
    Toggling_Capability_for_Leds_Template* 
                      Toggling_Capability;
};
Led_Facility Led_Facility_Var;
void Leds_Test_create();
void Leds_Test_destroy();

#endif
\end{verbatim}
\caption{LED\_Demo.h}
\end{figure}

\begin{figure}
\centering
\begin{verbatim}
/*
 * Generated by the RESOLVE to C translator. 
 * This file should not be modified.
 */
#include "Leds_Test.h"
void Leds_Test_create() {
  Std_Boolean_Fac_create();
  Std_Integer_Fac_create();
  Std_Clock_Fac_create();
  r_type_ptr __arg_0 = Std_Integer_Fac_Var.core->
  createFromInteger(4, Std_Integer_Fac_Var.core->Integer);
  Led_Facility_Var.core = 
  new_Std_Leds_Realiz_for_Leds_Template(__arg_0);
  Led_Facility_Var.Toggling_Capability = 
  new_Toggling_Realiz_for_Toggling_Capability_of_LED_Template(
								      Led_Facility_Var.core);
  Std_Integer_Fac_Var.core->Integer->
  destroy(__arg_0, Std_Integer_Fac_Var.core->Integer);
}

void Leds_Test_destroy() {
    free_Std_Leds_Realiz_for_Leds_Template(
    				    Led_Facility_Var.core);
    Std_Boolean_Fac_destroy();
    Std_Integer_Fac_destroy();
}
\end{verbatim}
\caption{LED\_Test.c}
\end{figure}

### 2014-04-25 tech-project/specify_led.tex
adding led demo tex

--- 2014-04-25 tech-project/specify_led.tex
@@
 This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}).
-Note that the ability to toggle is added \textit{on top} of this facility declaration in a similar fashion.
+Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.
 The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
@@
 The \texttt{LED\_Telos\_Demo} facility above demonstrates these developments through its use of the ``\texttt{externally realized}" phrase.
-This signals to the RESOLVE compiler that the user is providing a non-native realization of \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.
+This signals to the RESOLVE compiler that the user is providing a non-native realization of the \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.
 
@@
 
-In the context of embedded systems, these developments are especially useful as we can now write custom, low level  drivers of the sort required for most embedded applications (e.g.
-LED strip drivers) while still providing extensible, formally specified interfaces.
-It is our hope and intention that new (native) RESOLVE components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstraction where we can concern ourselves exclusively with verified, native RESOLVE components.
+In the terms of embedded systems, these developments are especially as it allows us to write custom low level of the sort required for most embedded applications (e.g.
+LED strip drivers) while still providing formally specified interfaces that might later form the foundation .
+It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstract where we can concern ourselves exclusively with verified, native RESOLVE components.
 

### 2014-04-25 tech-project/implementation.tex
changed impl section

--- 2014-04-25 tech-project/implementation.tex
@@
 The particular allocation scheme that we chose to use is \texttt{salloc()}: A first fit memory allocator.
-Rather than allocating memory on the heap, \texttt{salloc()} instead uses the stack.
-At compilation, the allocator provisions a fixed size of memory.
-It requires a small section of meta-data called a block which contains information of about the size of memory allocated, neighboring blocks, as well if the block is free or not.
-A sample representation of the stack shown in figure \ref{fig:stack}, is a typical example of allocated memory on the stack.
+Rather than conventional, heap-based allocators, \texttt{salloc()} uses stack memory for allocation.
+This approach requires that a fixed size of memory is chosen at compilation.
+In addition, \texttt{salloc()}, requires a section of meta-data, which is denoted as a \texttt{block}, for each record in the memory pool.
+A \texttt{block} holds referential information of neighboring blocks, the size of the record the block maintains, and if the block is free or is in use.
+Figure~\ref{fig:stack} is an example of the stack after several calls to \texttt{salloc()}.
 
 \begin{figure}[!htb]
-\centering
+%\centering
 \includegraphics[scale=.55]{figs/stack.pdf}
-\caption{Representation of memory stack}
+\caption{Representation of memory using salloc()}
+Memory allocated with salloc() allocates a block in front of data allocated. Blocks point to their immediate neighbors and hold their size and usage.
+\label{fig:stack}
 \end{figure}
-\label{fig:stack}
 

### 2014-04-25 tech-project/figs/implementation.tex
recent changes

--- 2014-04-25 tech-project/implementation.tex
@@
-% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE...
-AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE.
-BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
-\section{Implementation}
-Development of our C translation tool can be logically partitioned into three distinct phases: 
-\begin{enumerate}
-\item Arriving at a translation model (or, strategy) for an accurate C representation of RESOLVE.
-\item Implementing reusable mechanisms for carrying out the C code generation process.
-\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
-\end{enumerate}
-We conclude this section with a demonstration of each of these phases working in tandem on the LED component discussed in Section \ref{sec:specifiying}.
-
-\subsection{C Translation Model}
-One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each.
-Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source.
-In an effort to make such considerations, at the highest level, the C code we generate makes special considerations for concepts, facilities, and realizations.
-This scheme is depicted in Figure \ref{fig:relationship} and briefly summarized in Sections \ref{sec:conceptoverview} - \ref{sec:facilitiesrealizations}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=.60]{figs/relationship.pdf}
-\end{center}
-\caption{Relationship between RESOLVE module types and the C code generated from each.}
-\label{fig:relationship}
-\end{figure}
-
-\subsubsection{Concepts}
-\label{sec:conceptoverview}
-Concept modules produce a single .h file, which provide function pointers for the operations specified in the original concept, as well as structs representing each user defined type.
-
-\subsubsection{Facilities}
-\label{sec:facilitiesoverview}
-Facilities produce an .h/.c pair: The header .h declares both a ``create" and ``destroy" method which, taken together, encapsulates the creation and destruction of all global variables used within the facility.
-The .c provides an implementation of these methods.
-Note that these create and destroy methods are only responsible for freeing \textit{global} variables -- meaning all other translated functions are responsible for deallocating their own local variables.
-
-\subsubsection{Realizations}
-\label{sec:facilitiesrealizations}
-We treat realizations of concepts and enhancements slightly different than facility modules.
-While a .h/.c pair is still produced, the create method designated in the header for realizations is designed to create instances of all types specified by the concept, while the destroy method deallocates these types -- as opposed to simply destroying user created globals.
-
-%The memory model must also be considered as an additional verifiable component.
-Currently, RESOLVE is not capable of creating a complete specification of memory\footnote{RESOLVE is an object based language and has variable sized structures.
-Using dynamically allocatable memory is the favored approach to allow arbitrarily sized data.}.
-Thus, a memory model must be realized without a specification.
-To provide a straight forward translation from RESOLVE to C, we provide a dynamically-based memory allocator for use on embedded systems.
-
-%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=.55]{figs/ast_traversal2.pdf}
-\end{center}
-\caption{The general flow of information from the AST (first), to user defined templates (middle), ending with formed output (last).}
-\label{fig:ast}
-\end{figure*}
-
-\subsection{Translator Implementation}
-
-Translation itself occurs over the course of a traversal of RESOLVE's abstract syntax tree (AST) -- an intermediate representation of RESOLVE code.
-The traversal mechanism utilized is a derivative of the visitor pattern that provides a pre post traversal over all nodes in the tree.
-
-%\subsubsection{AST Traversal}
-%Translation is performed over the course of a traversal of RESOLVE's abstract syntax tree (AST).
-The traversal mechanism used is a dervivative of the visitor pattern that provides a SAX-dom style pre-post traversal over all nodes in the tree.
-Thus, for any given node present, a total of two visits occur: One corresponding to the node being `hit' during the pre traversal stage, and one for the post.
-
-To illustrate the general process of producing runnable C from RESOLVE code, consider the following dummy operation:
-
-\begin{verbatim}
-Operation Nothing(); Procedure
-        Var X : Integer;
-        X := 3;
-end Nothing;
-\end{verbatim}
-
-Shown in Figure \ref{fig:ast} is a high level depiction of steps taken in translating this operation to C.
-The first box depicts the AST of \texttt{Nothing}, where nodes are represented with boxes labeled by the constructs they contain.
-Throughout the walk of this tree, useful information (such as the operation's name, ``Nothing") are extracted from the nodes containing these constructs, and added to a user defined string-template\footnote{A template can simply be thought of as a ``document with holes" which the user choses when and how to fill.}, in this case: \texttt{c\_function\_def}.
-
-In the context of RESOLVE to C translation, these templates, when filled during the aforementioned pre-post visitor traversal of RESOLVE's AST, help simplify the task of producing complicated, arbitrarily nested blocks of structured C output by keeping translation logic strictly within the C translator, and output logic strictly within the templates.
-
-That is, the only actual work being performed within the C translator is forwarding information gathered from individual treenodes, to a series of externally defined templates.
-This allows us to exploit (in design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates which shape our output (view).
-
-We feel this approach lends itself well to the challenge discussed in this paper, as this separation allows us to easily iterate changes to our generated C code without needing to concern ourselves with the Java written inside the compiler itself.
-This allows us to easily and iteratively tweak generated code -- making arbitrarily complicated changes and optimizations, some of which are detailed later in Section \#.
-
-% general flow Each of these calls are received in the translator in the order in which they are visited within the tree.
-It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
-
-%\subsubsection{Translation output}
-%Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
-Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.
-
-%An example C function definition template is shown below.
-
-%\begin{verbatim}
-%function_def(modifier, type, name, params, 
-%                               vars, stmts) ::= <<
-%<modifier> <type> <name> (<params; sep = ", ">) {
-%    <vars; sep = "\n">
-%    <stmts; sep = "\n">
-%}>>
-%\end{verbatim}
-
-%User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
-It is entirely up to the user to define which attributes to fill in, and how complex they want them to be.
-For example, the user might choose to fill the \texttt{params} attribute with a simple string, or a separately defined \texttt{parameter} template, which in turn might use another separately defined \texttt{type} template.
-
-%\begin{verbatim}
-%parameter(type, name) ::= "<type> <name>"
-%\end{verbatim}
-
-%In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
-For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in.
-As \texttt{preOperationDec}'s children are visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the nodes being walked.
-Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in with the appropriate templates -- assuming the user has implemented the children's visit methods.
-
-%Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
-This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).
-
 \subsection{Memory Allocation}

### 2014-04-25 tech-project/implementation.tex
recent changes

@@
 \begin{figure}[!htb]
-%\centering
+\centering
 \includegraphics[scale=.55]{figs/fragmentation.pdf}
-\caption{fragmentation}
+\caption{Performing naive allocation and deallocations, allocatable blocks are restricted to those that match the exact size of memory requested from the allocator}
 \label{fig:fragmentation}
-Performing many naive allocation and deallocations, allocatable blocks are restricted to those that match the exact size of memory requested from the allocator.
 \end{figure}
@@
 \begin{figure}[!htb]
-%\centering
+\centering
 \includegraphics[scale=.55]{figs/split.pdf}
-\caption{block splitting}
-Splitting of a free block creates two new blocks: a block that is the size that the allocator requested, and the other contains the remainder of a new free block with the remainder of memory.
+\caption{Splitting creates a block that is the size that the allocator requested, and a new free block with the remainder of memory.}
 \label{fig:split}
@@
 \begin{figure}[!htb]
-%\centering
+\centering
 \includegraphics[scale=.55]{figs/fuse.pdf}
-\caption{block fusing}
-An example of fusing blocks together. This creates single larger block, decreasing the number of smaller blocks unable to split.
+\caption{Block fusing. This creates single larger block, decreasing the number of smaller blocks unable to split.}
 \label{fig:fuse}

### 2014-04-25 tech-project/implementation.tex
changes

@@
 
-% general flow Each of these calls are received in the translator in the order in which they are visited within the tree.
-It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.
-
-%\subsubsection{Translation output}
-%Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates.
-Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.
-
-%An example C function definition template is shown below.
-
-%\begin{verbatim}
-%function_def(modifier, type, name, params, 
-%                               vars, stmts) ::= <<
-%<modifier> <type> <name> (<params; sep = ", ">) {
-%    <vars; sep = "\n">
-%    <stmts; sep = "\n">
-%}>>
-%\end{verbatim}
-
-%User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others.
-It is entirely up to the user to define which attributes to fill in, and how complex they want them to be.
-For example, the user might choose to fill the \texttt{params} attribute with a simple string, or a separately defined \texttt{parameter} template, which in turn might use another separately defined \texttt{type} template.
-
-%\begin{verbatim}
-%parameter(type, name) ::= "<type> <name>"
-%\end{verbatim}
-
-%In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output.
-For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in.
-As \texttt{preOperationDec}'s children are visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the nodes being walked.
-Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in with the appropriate templates -- assuming the user has implemented the children's visit methods.
-
-%Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template.
-This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 In spite of this, our reasoning for choosing to pursue dynamic allocation over static, rests in the language itself.
-Being a language that relies heavily on the notion of formally specified objects (components), everything in RESOLVE from the `primitive' types such as booleans and integers, to the more complicated (user defined) ones such as Stacks and Queues, are modeled, specified, and implemented in the same way: Using the standard RESOLVE machinery discussed in Section \ref{sec:specifiying}.
+Being a language that relies heavily on the notion of formally specified objects (components), everything in RESOLVE from the `primitive' types such as booleans and integers, to the more complicated ones such as Stacks and Queues, are modeled, specified, and implemented in the same way: Using the standard RESOLVE machinery discussed in Section \ref{sec:specifiying}.
 

### 2014-04-25 tech-project/led_trans.tex
changes

@@
 
-\begin{figure}
-\centering
+\begin{figure*}
+\begin{minipage}{0.4\textwidth}
 \begin{verbatim}
@@
  */
-#ifndef __LEDS_TEST_H
-#define __LEDS_TEST_H
+#ifndef __LED_TELOS_DEMO_H
+#define __LED_TELOS_DEMO_H
 
 #include ".../RESOLVE.h"
-#include ".../Facilities/.../Std_Boolean_Fac.h"
-#include ".../Facilities/.../Std_Integer_Fac.h"
+#include ".../Facilities/.../Std_Bool_Fac.h"
+#include ".../Facilities/.../Std_Int_Fac.h"
 #include ".../Facilities/.../Std_Clock_Fac.h"
-#include ".../Concepts/.../Leds_Template.h"
-#include ".../Concepts/.../Std_Leds_Realiz.h"
+#include ".../Concepts/.../LED_Template.h"
+#include ".../Concepts/.../Std_LED_Realiz.h"
 #include ".../Concepts/.../Toggling_Realiz.h"
 
-typedef struct Led_Facility Led_Facility;
-struct Led_Facility {
-    Leds_Template* core;
-    Toggling_Capability_for_Leds_Template* 
+typedef struct LED_Facility LED_Facility;
+struct LED_Facility {
+    LED_Template* core;
+    Toggling_Capability_for_LED_Template* 
                       Toggling_Capability;
 };
-Led_Facility Led_Facility_Var;
-void Leds_Test_create();
-void Leds_Test_destroy();
+LED_Facility LED_Fac_Var;
 
+void LED_Telos_Demo_create();
+void LED_Telos_Demo_destroy();
 #endif
 \end{verbatim}
-\caption{LED\_Demo.h}
-\end{figure}
-
-\begin{figure}
-\centering
+\end{minipage}
+\hspace{1.5cm} 
+\begin{minipage}{0.4\textwidth}
 \begin{verbatim}
@@
  */
-#include "Leds_Test.h"
-void Leds_Test_create() {
-  Std_Boolean_Fac_create();
-  Std_Integer_Fac_create();
+#include "LED_Telos_Demo.h"
+
+void LED_Telos_Demo_create() {
+  Std_Bool_Fac_create();
+  Std_Int_Fac_create();
   Std_Clock_Fac_create();
-  r_type_ptr __arg_0 = Std_Integer_Fac_Var.core->
-  createFromInteger(4, Std_Integer_Fac_Var.core->Integer);
-  Led_Facility_Var.core = 
-  new_Std_Leds_Realiz_for_Leds_Template(__arg_0);
-  Led_Facility_Var.Toggling_Capability = 
-  new_Toggling_Realiz_for_Toggling_Capability_of_LED_Template(
-								      Led_Facility_Var.core);
-  Std_Integer_Fac_Var.core->Integer->
-  destroy(__arg_0, Std_Integer_Fac_Var.core->Integer);
+  r_type_ptr __arg_0 = Std_Int_Fac_Var.core->
+    createFromInt(4, Std_Int_Fac_Var.core->Integer);
+  LED_Fac_Var.core = 
+    new_Std_LED_Realiz_for_LED_Template(__arg_0);
+  LED_Fac_Var.Toggling_Capability = 
+    new_Toggling_Realiz_for_
+    Toggling_Capability_of_LED_
+    Template(LED_Fac_Var.core);
+  Std_Int_Fac_Var.core->Integer->
+    destroy(__arg_0, Std_Int_Fac_Var.core->Integer);
 }
 
-void Leds_Test_destroy() {
-    free_Std_Leds_Realiz_for_Leds_Template(
-    				    Led_Facility_Var.core);
-    Std_Boolean_Fac_destroy();
-    Std_Integer_Fac_destroy();
+void LED_Telos_Demo_destroy() {
+    free_Std_LED_Realiz_for_LED_Template(
+    				    LED_Fac_Var.core);
+    Std_Bool_Fac_destroy();
+    Std_Int_Fac_destroy();
 }
+        ...
 \end{verbatim}
-\caption{LED\_Test.c}
-\end{figure}
+\end{minipage}
+\end{figure*}

### 2014-04-26 tech-project/led_trans.tex
added a bunch of stuff to the end of the paper
updated the demo tex

@@
 % An LED Demo Translation
-\section{LED Demo}
+\section{Putting It All Together}
 
@@
   r_type_ptr __arg_0 = Std_Int_Fac_Var.core->
-    createFromInt(4, Std_Int_Fac_Var.core->Integer);
+    createFromInt(3, Std_Int_Fac_Var.core->Integer);
   LED_Fac_Var.core = 
@@
 \end{minipage}
+\label{fig:demo}
 \end{figure*}
+
+We have seen in Figure~\ref{fig:relationship} that RESOLVE facilities have corresponding \texttt{.h/c} output translations.
+Shown in Figure~\ref{fig:demo}, is an example facility realization for an LED strip with a toggling enhancement.
+Again, note, that the header file contains instantiation information for an LED facility.
+
+%The \texttt{.h} file contains a struct that holds an instance of an LED concept realization as well as the realization for a toggling enhancement.
+Take note that additional facility and concept imports are placed here corresponding to Figure~\ref{fig:relationship}, including create and destroy constructs as mentioned in Section~\ref{sec:impl}.
+
+In the \texttt{C} implementation file, the \texttt{LED\_Telos\_Demo\_create()} function provides instantiations for all the global facilities used for the \texttt{LED\_Telos\_Demo} program, including those for standard types (Integer \& Boolean), Clock, and the LED.
+To instantiate a new LED facility we must first create a new Integer realization and save it into a new \texttt{r\_type\_ptr}\footnote{An r\_type\_ptr provides the primary source of object storage in RESOLVE.
+It is represented as a (\texttt{void**} ) in its C representation.
+Although it is not detailed in this paper, the r\_type\_ptr provides the level abstraction needed to implement an object oriented design in C}.
+This new Integer realization will provide the strip length for the LED facility.
+A new facility can then use this to create a new concept using the externally realized \texttt{new\_Std\_LED\_Realiz\_for\_LED\_Template()} function.
+The facility can also create a new enhancement with \texttt{new\_Toggling\_Realiz\_for\_Toggling\_Capability\_of\_LED\_Template()}.
+Similarly, this initialization and allocation step must occur for the Integer, Boolean, and Clock facilities.
+From this relatively small example of LED toggling from RESOLVE to C,  complex programs will require even more attention to amount of memory used for each concept and facility realization.
+Curtailing the management of this memory by placing the responsibility on an allocator provides a key motivation for using \texttt{salloc()} and \texttt{sfree()}.
+
+%From this relatively small example of LED toggling from RESOLVE to C, we expect even These externally realized components utilize the memory allocator presented in Section~\ref{sec:mem}.
+
+%The corresponding \texttt{.c} file provides implementations for creating, destroying, as well as providing the execution implementation for the LED strip.
+Take note that \texttt{LED\_Telos\_Demo\_create()} provides additional functionality besides creating a new instance of an LED facility.
+Creating a new facility requires that all accompanying facilities are instantiated at this point, including those from Standard and Clock\footnote{The Std\_Clock\_Fac provides and externally realized facility to express sleep functionality for an msp430 chipset} for this example.
+To instantiate a new LED facility we must first create a new Integer realization and save it into a new \texttt{r\_type\_ptr}\footnote{An r\_type\_ptr provides the primary source of object storage in RESOLVE.
+It is represented as a (\texttt{void**} ) in its C representation.
+Although it is not discussed in this paper, the r\_type\_ptr provides the level abstraction needed to implement an object oriented design in C}.
+This new Integer realization will provide the strip length for the LED facility.
+A new facility can then be instantiated by calling the \texttt{new\_Std\_LED\_Realiz\_for\_LED\_Template()} function.
+This is where memory is allocated and stored for a new LED facility and its enhancements.
+Once a facility is instantiated, we can create a new realization for LED toggling and store this as a part of the facility in \texttt{LED\_Fac\_Var.Toggling\_Capability}.
+
+%Since an LED strip is specified by Std_Boolean and Std_Integer, we must create instantiations of both facilities.
+We must also include \texttt{Std_Clock_Fac_create())} because our LED toggling program will utilize the msp430 clock utilities to put the MCU to sleep.
+
+\begin{figure}
+\begin{verbatim}
+void Main() {
+  r_type_ptr L = LED_Fac_Var.core->LED->
+    create(LED_Fac_Var.core->LED);
+  r_type_ptr Loop = ...createFromBoolean(1, ...);
+  r_type_ptr I0 = ... createFromInteger(0, ...);
+  r_type_ptr I1 = ... createFromInteger(1, ...);
+  r_type_ptr I2 = ... createFromInteger(2, ...);
+
+  while(**(int**)Loop) {
+    LED_Facility_Var.Toggling_Capability->
+      Toggle(L, I0, LED_Fac_Var.Toggling_Capability);
+    Std_Clock_Fac_Var.core->
+      Wait_500_Milli_Seconds(Std_Clock_Fac_Var.core);
+    LED_Fac_Var.Toggling_Capability->
+      Toggle(L, I1, LED_Fac_Var.Toggling_Capability);
+    Std_Clock_Fac_Var.core->
+      Wait_500_Milli_Seconds(Std_Clock_Fac_Var.core);
+    LED_Fac_Var.Toggling_Capability->
+      Toggle(L, I2, LED_Fac_Var.Toggling_Capability);
+    Std_Clock_Fac_Var.core->
+      Wait_500_Milli_Seconds(Std_Clock_Fac_Var.core);
+  }
+
+  Std_Int_Fac_Var.core->Integer->
+  ...
+  LED_Fac_Var.core->LED->
+    destroy(L, LED_Fac_Var.core->LED);
+}
+\end{verbatim}
+\label{fig:loop}
+\end{figure}
+
+The code presented by Figure~\ref{fig:loop} introduces the toggling capability for an LED strip.
+It toggles each LED\footnote{in the case of the telos motes, we will consider the LED strip to have an LED\{0, 1, 2\}}, separated by a delay of 500ms.
+This is repeated indefinitely using a while statement.
+
+To implement this, realizations for the local LED strip, the loop condition, and the index for each LED must be created as demonstrated.
+Within the loop, we call the \texttt{Toggle()} function from the \texttt{Toggling\_Capability} enhancement created from Figure~\ref{fig:demo}.
+
+%An instance of a new LED strip must be created from the facility to denote a new, local, LED realization.
+Other local facilities, must be instantiated, including a Boolean, \texttt{Loop}, which provides the loop condition as well as Integers I0, I1, and I2 which will denote a specific index of an LED\footnote{in the case of the telos motes, we will consider the LED strip to have an LED\{0, 1, 2\}.} Within the loop, we call the \texttt{Toggle()} function from the \texttt{Toggling\_Capability} enhancement created from Figure~\ref{fig:demo}.
+
+The toggling realization takes an LED strip, the index to toggle, and the reference to the enhancement.
+Within \texttt{Toggle()}, we use the externally realized LED concepts \texttt{Status()} to get the current state of the LED, and \texttt{Set()} to flip the specified LED at an index to its opposite value (on or off).
+Retrieving the status, as well as setting an LED strip at an index to on or off requires more memory allocation to save these to temporary Boolean and Integer types.
+In this instance, we note that we need to have the capability of creating and destroying an arbitrary number of times, provides another key motivation for dynamic memory allocation.
+Determining the minimum memory size needed, becomes increasingly difficult with the while statement.
+Similarly, other programs may require an implementation of stacks or queues that require a locally unbounded depth.
+
+A wait utility is then called using the \texttt{Std\_Clock\_Fac} facility.
+This facility uses the externally realized concept to the msp430 \texttt{\_\_delay\_cycles()} command.
+Internally the MCU is delayed for a given number of cycles.
+
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%

### 2014-04-26 tech-project/related_works_and_conclusion.tex

\section{Related Work}

There are a number of existing systems that ultimately seek to prove the functional correctness of programs. While we discuss only a handful here, readers interested in learning more about the systems mentioned might to refer to \cite{klebanov:2011} for a more in depth discussion. Perhaps most notable among the systems we list here (and perhaps the closest to RESOLVE's approach) is Microsoft research's Dafny \cite{leino:2010}. Designed to be capable of verifying pointer based structures, Dafny currently stands as one of the more popular approaches. Replacing RESOLVE's notion of mathematical variables with what are termed `ghost' variables, reasoning is kept, like RESOLVE, disconnected from implementation-level code. Dafny uses an intermediate verification language, termed Boogie, to generate verification conditions which are then dispatched via Z3, Microsoft's automated prover.

Another system worth mentioning here is VCC, also a Microsoft research project, which is designed for the verification of C programs.

% shortcoming -- concurrency.

\section{Discussion and Future Work}

Using embedded application development as an example, we envision the work presented in this paper as a step towards more fully exploring the role of formal verification in lower level system-oriented contexts. Indeed, the realm of embedded systems has served as an ideal stepping off point for this challenge, as it encourages (or, indeed, requires) RESOLVE as a language to expand to provide support for not only new target languages (namely C), but also new language constructs that give the user freedom to more easily author drivers of the sort required for any serious embedded application. While we have made some progress with the latter in the form of the externally keyword, a natural direction for future work should involve moving beyond functional correctness, and instead focus more heavily on RESOLVE's mechanisms for specifying time and duration. With performance capabilities such as these in place, a natural next step in this work would be to formally specify and externally realize a simple memory allocation scheme, not dissimilar to the one presented in this paper.

Another language characteristic that we feel would benefit especially specification of lower level applications is having some means within RESOLVE of dictating \textit{static objects}. While currently RESOLVE allows users create single instance concepts that are tied to particular facility instantiations, we currently have no means of limiting how many instantiations of a particular facility there might be (not even via standard facilities). Thus, in terms of specifying concepts such as clocks, LED strips, and other hardware-centric concepts that only appear once on circuit board, RESOLVE might benefit from an in-language mechanism that restricts allowable instances of these and other objects.

\section{Conclusions}

In this paper we present new RESOLVE language constructs and tools with the objective of translating RESOLVE to embedded platform friendly C. We provide representative specifications of an LED strip component that both demonstrates the benefits of RESOLVE's approach to reusable mathematical developments, as well as formal verification of a single driver enhancement. We illustrate usage of this component in the context of a client facility module, wherein we introduce the externally keyword that allows users to transparently pair non-native RESOLVE implementations with native RESOLVE specifications. We then translate this facility application, illustrating a proof-of-concept dynamic memory allocator working in tandem with what we consider to be an accurate C representation of RESOLVE code. The examples and results listed in this paper have been successfully run on a Telos mote, and the overall tool -- now fully integrated with the RESOLVE compiler -- actively continues to undergo improvements and optimizations on all fronts.

### 2014-05-01 tech-project/abstract.tex
changes since initial turn in

@@
 In doing so, we enrich the work originally presented in \cite{regula:2010} with the following: A model view controller (MVC) based implementation of a RESOLVE to C translator, a dynamic memory allocation scheme tailored towards embedded systems running the code generated by our tool, and the addition of a new language keyword that enables users to pair custom RESOLVE specifications with `externally' implemented (non-native RESOLVE) realizations.
-We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of a toggling capability enhancement that we demonstrate running on a Telos mote.
+We demonstrate these additions on an LED (Light emitting diode) driver that showcases recent mathematical developments, as well as formal verification of a toggling capability enhancement.
 \end{abstract}

### 2014-05-01 tech-project/implementation.tex
updated the demo tex
changes since initial turn in

@@
 BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
-\section{Implementation}
+\section{Implementation}\label{sec:impl}
 Development of our C translation tool can be logically partitioned into three distinct phases: 
@@
 \item Arriving at a translation model (or, strategy) for an accurate C representation of RESOLVE.
-\item Implementing reusable mechanisms for carrying out the C code generation process.
+\item Implementing suitable mechanisms for carrying out the C code generation process.
 \item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
@@
 In an effort to make such considerations, at the highest level, the C code we generate makes special considerations for concepts, facilities, and realizations.
-This scheme is depicted in Figure \ref{fig:relationship} and briefly summarized in Sections \ref{sec:conceptoverview} - \ref{sec:facilitiesrealizations}.
+This scheme is depicted in Figure \ref{fig:relationship} and briefly summarized throughout Sections \ref{sec:conceptoverview} - \ref{sec:facilitiesrealizations}.
 
@@
 \end{figure}
+
+\begin{figure*}[!htb]
+\begin{center}
+\includegraphics[scale=.54]{figs/ast_traversal2.pdf}
+\end{center}
+\caption{The general flow of information from the AST (first), to user defined templates (middle), ending with formed output (last).}
+\label{fig:ast}
+\end{figure*}
 
@@
 While a .h/.c pair is still produced, the create method designated in the header for realizations is designed to create instances of all types specified by the concept, while the destroy method deallocates these types -- as opposed to simply destroying user created globals.
-
-%The memory model must also be considered as an additional verifiable component.
-Currently, RESOLVE is not capable of creating a complete specification of memory\footnote{RESOLVE is an object based language and has variable sized structures.
-Using dynamically allocatable memory is the favored approach to allow arbitrarily sized data.}.
-Thus, a memory model must be realized without a specification.
-To provide a straight forward translation from RESOLVE to C, we provide a dynamically-based memory allocator for use on embedded systems.
-
-%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=.55]{figs/ast_traversal2.pdf}
-\end{center}
-\caption{The general flow of information from the AST (first), to user defined templates (middle), ending with formed output (last).}
-\label{fig:ast}
-\end{figure*}
 
@@
 Shown in Figure \ref{fig:ast} is a high level depiction of steps taken in translating this operation to C.
-The first box depicts the AST of \texttt{Nothing}, where nodes are represented with boxes labeled by the constructs they contain.
-Throughout the walk of this tree, useful information (such as the operation's name, ``Nothing") are extracted from the nodes containing these constructs, and added to a user defined string-template\footnote{A template can simply be thought of as a ``document with holes" which the user choses when and how to fill.}, in this case: \texttt{c\_function\_def}.
+The first box depicts the AST of \texttt{Nothing}, where nodes are represented as boxes labeled by the constructs they contain.
+Throughout the walk of this tree, useful information such as the operation's name, ``Nothing", are extracted from nodes, and added as parameters to user defined templates\footnote{A template can simply be thought of as a ``document with holes" which the user choses when and how to fill.}, in this case: \texttt{c\_function\_def}.
 
@@
 That is, the only actual work being performed within the C translator is forwarding information gathered from individual treenodes, to a series of externally defined templates.
-This allows us to exploit (in design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates which shape our output (view).
+This allows us to exploit (in design pattern parlance \cite{krasner:1988}) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates which shape our output (view).
 
 We feel this approach lends itself well to the challenge discussed in this paper, as this separation allows us to easily iterate changes to our generated C code without needing to concern ourselves with the Java written inside the compiler itself.
-This allows us to easily and iteratively tweak generated code -- making arbitrarily complicated changes and optimizations, some of which are detailed later in Section \#.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Memory Allocation}\label{sec:mem}
+\subsection{Strategy for Dynamic Memory Allocation}\label{sec:mem}
 
-Any model seeking to convert RESOLVE to a lower level representation such as C demands a strategy for handling any memory utilized by the generated code.
+Any model seeking to convert RESOLVE to a lower level representation such as C demands a strategy for handling memory utilized by the generated code.
 While dynamic allocation is typically the norm, it is not however the first choice for embedded applications.
-With the Telos mote constrained to 128 bytes of RAM, developers targeting embedded platforms tend to favor static memory allocation over dynamic, due the memory efficiency it affords.
+With the Telosb mote constrained to 128 bytes of RAM, developers targeting embedded platforms tend to favor static memory allocation over dynamic, due the memory efficiency it affords.
 
@@
 In spite of this, our reasoning for choosing to pursue dynamic allocation over static, rests in the language itself.
-Being a language that relies heavily on the notion of formally specified objects (components), everything in RESOLVE from the `primitive' types such as booleans and integers, to the more complicated ones such as Stacks and Queues, are modeled, specified, and implemented in the same way: Using the standard RESOLVE machinery discussed in Section \ref{sec:specifiying}.
+Being a language that relies heavily on the notion of formally specified, verifiable objects (components), everything in RESOLVE from the `primitive' types such as booleans and integers, to the more complicated ones such as Stacks and Queues, are modeled, specified, and implemented in the same way: Using the standard component machinery showcased in Section \ref{sec:specifiying}.
 
 As such, even the simplest RESOLVE programs still rely heavily on the notion of objects coming and going.
-Thus, from a verification perspective, creating a tool that allows our translated code to create and destroy such objects in the manner the language itself uses is an important component to capture in formally verified code.
+Thus, from a verification perspective, creating a tool that allows our translated code to create and destroy such objects in a manner consistent with the language is an extremely important aspect towards maintaining the ``correct-by-construction" property of our automatically generated C code.
 
-\subsubsection{Allocation using \texttt{salloc}}
+The previous iteration of this tool \cite{regula:2010} (favoring static allocation) carries out ``pseudo allocation"  by effectively introducing second pass to the compiler dedicated to replacing all formal parameters, with their corresponding facility-instantiated literal values.
+This additional, hidden step to compilation is less than ideal in the context of a verifying compiler designed from the ground up to be a single pass system.
+We feel the work we present here avoids these wrinkles with a dynamic approach.
 
-The particular allocation scheme that we chose to use is \texttt{salloc()}: A first fit memory allocator.
+\subsubsection{Allocation using ``salloc''}
+
+The dynamic allocatior we create for our generated code is \texttt{salloc()}: A first fit memory allocator.
 Rather than conventional, heap-based allocators, \texttt{salloc()} uses stack memory for allocation.
-This approach requires that a fixed size of memory is chosen at compilation.
-In addition, \texttt{salloc()}, requires a section of meta-data, which is denoted as a \texttt{block}, for each record in the memory pool.
-A \texttt{block} holds referential information of neighboring blocks, the size of the record the block maintains, and if the block is free or is in use.
+This approach requires that a single fixed block of memory is chosen at compilation.
+In addition, \texttt{salloc()}, requires a section of meta-data, denoted as a \texttt{block}, for each record in memory.
+A \texttt{block} holds referential information about neighboring blocks, the size of the record the block maintains, and if the block is free or is in use.
 Figure~\ref{fig:stack} is an example of the stack after several calls to \texttt{salloc()}.
@@
 \includegraphics[scale=.55]{figs/stack.pdf}
-\caption{Representation of memory using salloc()}
-Memory allocated with salloc() allocates a block in front of data allocated. Blocks point to their immediate neighbors and hold their size and usage.
+\caption{Memory allocated with salloc() allocates a block in front of data allocated. Blocks point to their immediate neighbors and hold their size and usage.}
+
 \label{fig:stack}
@@
 
-A memory allocator must provide a mechanism to release, or free memory in order to indicate that it is not being used and can be reallocated.
-The \texttt{sfree()} function provides deallocation for memory allocated with \texttt{salloc()}.
-Figure~\ref{fig:free} shows an example set of memory before and after calling \texttt{sfree()}.
+A memory allocator must provide a mechanism to release, or free a section of memory in order to indicate that it is not being used and that it may be reallocated.
+Our \texttt{sfree()} function, which provides this functionality, is illustrated in Figure~\ref{fig:free} -- depicting memory before and after a call to \texttt{sfree()}.
 
@@
 \includegraphics[scale=.55]{figs/sfree.pdf}
-\caption{sfree to free memory}
+\caption{An illustration of sfree.}
 \label{fig:free}
@@
 A common problem that can occur in memory allocation is fragmentation.
-During execution, a program can allocate and deallocate an arbitrary number of times.
-Figure~\ref{fig:fragmentation} shows problems that result from this.
-This problem is magnified on embedded systems due to their limited memory capacities.
-There are simple optimizations that can reduce fragmentation.
+During execution, a program can allocate and deallocate memory an arbitrary number of times.
+Figure~\ref{fig:fragmentation} depicts some of the problems that might arise from this such as a decreased success rate for allocation and increased overall memory usage.
+The problem is especially magnified on embedded systems, due to their limited memory capacity.
+We employ two simple optimizations to help reduce this.
 
-Block splitting, as shown in Figure~\ref{fig:split}, occurs during allocation. It allows blocks of greater size to be partitioned into the size requested by the allocator.
+\begin{itemize}
+\item \textbf{Block splitting:} As shown in Figure~\ref{fig:split}, unused blocks can be repartitioned to the size of memory needed by \texttt{salloc()}.
+\item \textbf{Block fusing:}
+This technique is applied during deallocation.
+When memory is deallocated by \texttt{sfree()}, neighboring free blocks containing unused memory are coalesced into a single large block, as shown in Figure~\ref{fig:fuse}.
+\end{itemize}
 
-Fusing blocks is another technique used when \texttt{sfree()} is called.
+%The first is block splitting, as shown in Figure~\ref{fig:split}, occurs during allocation. It allows blocks of greater size to be partitioned into the size requested by the allocator.
+
+%Fusing blocks is another technique used when \texttt{sfree()} is called.
 When memory is deallocated, neighboring free blocks are coalesced to form a single large block, as shown in Figure~\ref{fig:fuse}.
@@
 \includegraphics[scale=.55]{figs/fragmentation.pdf}
-\caption{Performing naive allocation and deallocations, allocatable blocks are restricted to those that match the exact size of memory requested from the allocator}
+\caption{Performing naive allocation and deallocations restricts allocatable blocks to those that match the size requested.}
 \label{fig:fragmentation}

### 2014-05-01 tech-project/introduction.tex
changes since initial turn in

@@
 Within little more than a decade, the area of embedded network systems and wireless sensing has exploded in popularity within industry and academia alike.
-Tempering however this extremely quick rise in popularity is the inherent difficulties in developing applications that function as intended in low power, event-driven environments.
-In response to these difficulties, a variety of tools and languages have been put forth  to help ease the burden on developers.
+With this quick and widespread proliferation of embedded devices, the need for provably correct embedded code increases -- especially in those industries where the cost of failure could be extreme both in terms of cost and human life.
+
+From a non-verification related perspective, a variety of tools and languages have been put forth to help make developing embedded applications a simpler, less error prone endeavor.
 On one end of this effort are languages such as NesC, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
-The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Arora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
-Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed in the field.
+The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Avrora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
+Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed.
 
-We approach this problem by using RESOLVE (Reusable SOftware Language with VErification) as means of authoring, specifying, and ultimately verifying code for embedded network systems.
+We approach this problem by using RESOLVE (Reusable SOftware Language with VErification) as means of authoring, specifying, and ultimately verifying code, prior to execution, for embedded network systems.
 Our decision to use RESOLVE as a language frontend -- as opposed to verifying C code directly -- ultimately stems from a verification amenability standpoint: Not only does RESOLVE prohibit verification crippling operations such as uncontrolled referencing and aliasing (prevalent in C and many other current languages)\cite{kulczycki:2004}, but also embodies a number of other characteristics ideal for embedded platforms including:
@@
 \begin{itemize}
-\item \textbf{Modularity} RESOLVE enforces a strict separation of concerns between module specifications and client implementations.
+\item \textbf{Modularity} RESOLVE enforces a strict separation of concerns between module level specifications and client level implementations.
 As a result, for any one particular specification, there can be any number of interchangeable implementations.
@@
 
-\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own.
-This is ideal in a setting where drivers might encompass a wide spectrum possible applications, where each might require unique, new mathematical developments.% reword this to be less vague.
+\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of pre-existing mathematical units when writing specifications, or simply create their own.
+This is ideal in a setting where drivers might encompass a wide spectrum possible applications -- each requiring new mathematical developments.
 
@@
 The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code.
-We conclude with suggestions for tool improvements, as well as a review of some longer term research goals.
+We conclude with suggestions for tool improvements, as well as a review of some long term research goals.

### 2014-05-01 tech-project/led_trans.tex
changes since initial turn in

--- 2014-04-25 tech-project/led_trans.tex
@@
-% An LED Demo Translation
-\section{LED Demo}
+\section{Putting It All Together}
 
@@
 #include ".../RESOLVE.h"
-#include ".../Facilities/.../Std_Bool_Fac.h"
-#include ".../Facilities/.../Std_Int_Fac.h"
-#include ".../Facilities/.../Std_Clock_Fac.h"
+  ...
 #include ".../Concepts/.../LED_Template.h"
@@
 \begin{verbatim}
-/*
- * Generated by the RESOLVE to C translator. 
- * This file should not be modified.
- */
 #include "LED_Telos_Demo.h"
@@
   LED_Fac_Var.Toggling_Capability = 
-    new_Toggling_Realiz_for_
-    Toggling_Capability_of_LED_
-    Template(LED_Fac_Var.core);
+    new_Toggling_Realiz_for_Toggling_Capability_
+    of_LED_Template(LED_Fac_Var.core);
   Std_Int_Fac_Var.core->Integer->
@@
     Std_Int_Fac_destroy();
-}
-        ...
+} ...
 \end{verbatim}
 \end{minipage}
+\caption{C Translation of \texttt{LED\_Telos\_Demo}.}
+\label{fig:demo}
 \end{figure*}
+
+Given our RESOLVE realization of the \texttt{LED\_Telos\_Demo} described in Section 3, we now discuss our translator's output in greater detail.
+
+Depicted in figure \ref{fig:demo} is the C translation of \texttt{LED\_Telos\_Demo} consisting of a .h (left) and a portion of the .c (right).
+The \texttt{LED\_Telos\_Demo\_create()} function provides instantiations for all global facilities used in \texttt{LED\_Telos\_Demo}, including those for standard types such as integers, booleans, clock, as well as local facilities such as \texttt{Leds\_Fac}.
+One additional thing to note within this create method is the temporary \texttt{\_\_arg\_0} integer variable -- representing the formal value \texttt{Strip\_Length} found within the concept.
+Note that this variable does not appear in the original source, but rather, is created by the translator in an effort to keep track of all literal argument values that require manual deletion.
+
+The \texttt{Leds\_Fac} facility from the original source, represented here as a struct, uses a \texttt{core} field to provide a means of accessing the methods and types in the original concept, while any remaining fields correspond to enhancement pointers that serve a similar end -- in this case, providing access to the operations declared within  \texttt{Toggling\_Capability}.
+
+Clearly facilities and other modules highly reliant on facility instantiations are no doubt going to consume much more memory than the small example detailed here. To help alleviate some of th
+
+%\texttt{new\_Toggling\_Realiz\_for\_Toggling\_Capability\_of\_LED\_Template()}.
+Similarly, this initialization and allocation step must occur for the Integer, Boolean, and Clock facilities.
+From this relatively small example of LED toggling from RESOLVE to C,  complex programs will require even more attention to amount of memory used for each concept and facility realization.
+Curtailing the management of this memory by placing the responsibility on an allocator provides a key motivation for using \texttt{salloc()} and \texttt{sfree()}.
+
+%As seen from above, RESOLVE to C translations can produce verbose output.
+The code presented to the right introduces pseudocode for a toggling capability of an LED strip to simplify understanding of control flow.
+Denoting an LED strip as \texttt{L} and the index represented as an integer literal, this example toggles each LED \footnote{in the case of the telos motes, we will consider the LED strip to have an LED\{0, 1, 2\}} successively, separated by a 500ms delay and is repeated indefinitely through a while-loop.
+
+%Within \texttt{Toggle()}, we use the externally realized LED concepts \texttt{Status()} to get the current state of an LED strip, and \texttt{Set()} to set the specified LED at an index to complement.
+Retrieving the status, as well as setting an LED strip at an index to on or off requires more memory allocation to save these to temporary Boolean and Integer types.
+In this instance, we note that we need to have the capability of creating and destroying an arbitrary number of times, provides another key motivation for dynamic memory allocation.
+Determining the minimum memory size needed, becomes increasingly difficult with the while statement.
+Similarly, other programs may require an implementation of stacks or queues that require a locally unbounded depth.
+
+%Turning to the \texttt{main} function, we first call the appropriate create function to instantiate and allocate all global variables required by the facility.
+We then make a call to the user supplied \texttt{Main()} operation, which performs the user code.
+In normal applications the destroy method will be invoked, however here we employ a busy which prevents it from ever being called.
+
+%A wait utility is then called using the \texttt{Std\_Clock\_Fac} facility.
+This facility uses the externally realized concept to the msp430 \texttt{\_\_delay\_cycles()} command.
+Internally the MCU is delayed for a given number of cycles.
+
+\begin{figure}
+\begin{verbatim}
+int Main() {
+  while(TRUE) {
+    Toggle(L, 0);
+    Wait_500_Milli_Seconds();
+    Toggle(L, 1);
+    Wait_500_Milli_Seconds();
+    Toggle(L, 2);
+    Wait_500_Milli_Seconds();
+  }
+}
+
+int main() {
+  LED_Telos_Demo_create();
+  Main();
+  LED_Telos_Demo_destroy();
+}
+\end{verbatim}
+\label{fig:loop}
+\end{figure}
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%

### 2014-05-01 tech-project/paper.tex
changes since initial turn in

@@
 \conferenceinfo{Clemson 2014}{7th Clemson University Mini-Conference on Embedded Network Systems}
-\title{An Extensible Approach to Verification of Embedded Network Systems*}
+\title{An Extensible Approach to Verification of Embedded Systems}
 
-%Re-evaluating Verification of Embedded Network Systems:
-%An Extensible Approach to Verification of Embedded Network Systems*}
 \numberofauthors{2}
@@
 \affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{dtwelch\}@clemson.edu}}}
+\email{\texttt{\large{dtwelch@clemson.edu}}}
 %author
@@
 \affaddr{Clemson, South Carolina, 29634}\\
-\email{\texttt{\large{\{tbolte\}@clemson.edu}}}
+\email{\texttt{\large{tbolte@clemson.edu}}}
 }
@@
 \terms{Reliability, Verification, Languages, Networks}
-\keywords{automation, components, formal methods, specification, verifying compiler, embedded networks, wireless sensing}
+\keywords{automation, components, formal methods, specification, verifying compiler, embedded systems, wireless sensing}
 
@@
 \input{implementation.tex}
+\input{led_trans.tex}
+\input{related_works_and_conclusion.tex}
 \input{acknowledge.tex}

### 2014-05-01 tech-project/related_works_and_conclusion.tex
changes since initial turn in

@@
 There are a number of existing systems that ultimately seek to prove the functional correctness of programs.
-While we discuss only a handful here, readers interested in learning more about the systems mentioned might to refer to \cite{klebanov:2011} for a more in depth discussion.
+While we discuss only two here, readers interested in learning more about the systems mentioned might to refer to \cite{klebanov:2011} for a more in depth discussion.
 Perhaps most notable among the systems we list here (and perhaps the closest to RESOLVE's approach) is Microsoft research's Dafny \cite{leino:2010}.
-Designed to be capable of verifying pointer based structures, Dafny currently stands as one of the more popular approaches.
-Replacing RESOLVE's notion of mathematical variables with what are termed `ghost' variables, reasoning is kept, like RESOLVE, disconnected from implementation-level code.
+Designed to be capable of verifying pointer based structures, Dafny currently stands as one of the more popular approaches to verification.
+Substituting RESOLVE's notion of mathematical variables with what are termed `ghost' variables, reasoning is kept, like RESOLVE, disconnected from implementation-level code.
 Dafny uses an intermediate verification language, termed Boogie, to generate verification conditions which are then dispatched via Z3, Microsoft's automated prover.
 
-Another system worth mentioning here is VCC, also a Microsoft research project, which is designed for the verification of C programs.
+Another system, also a Microsoft research endeavor, is VCC -- a system designed for the verification of C programs \cite{vcc:2009}.
+One of the main draws of VCC is that it has mechanisms for verification of concurrent code -- an ideal feature when presented with asynchronous, event driven code common in most embedded applications.
+
+RESOLVE differs from the projects mentioned above most notably in that it does not make use of third party automated provers or decision procedures to discharge verification conditions.
+Rather, it makes use of an integrated, minimalist term rewrite prover that applies higher order theorems and definitions in attempting to transform givens into a provable goal.
 
@@
 
-Using embedded application development as an example, we envision the work presented in this paper as a step towards more fully exploring the role of formal verification in lower level system-oriented contexts.
-Indeed, the realm of embedded systems has served as an ideal stepping off point for this challenge, as it encourages (or, indeed, requires) RESOLVE as a language to expand to provide support for not only new target languages (namely C), but also new language constructs that give the user freedom to more easily author drivers of the sort required for any serious embedded application.
-While we have made some progress with the latter in the form of the externally keyword, a natural direction for future work should involve moving beyond functional correctness, and instead focus more heavily on RESOLVE's mechanisms for specifying time and duration.
-With performance capabilities such as these in place, a natural next step in this work would be to formally specify and externally realize a simple memory allocation scheme, not dissimilar to the one presented in this paper.
+Using embedded application development as an example, we perceive this work as a step towards more fully exploring the role of formal verification in lower level system-oriented contexts.
+Indeed, the realm of embedded systems provides an ideal stepping off point for this challenge, as it encourages (and indeed, requires) RESOLVE to provide support for not only new target languages (namely C), but also new language constructs that give the user the ability to author drivers required for any serious embedded application.
+While we have made progress with the latter in the form of the externally keyword, a natural direction for future work would entail using RESOLVE's performance specification mechanisms to prove the time and duration estimates for a memory allocator, not unlike the one presented here.
 
-Another language characteristic that we feel would benefit especially specification of lower level applications is having some means within RESOLVE of dictating \textit{static objects}.
-While currently RESOLVE allows users create single instance concepts that are tied to particular facility instantiations, we currently have no means of limiting how many instantiations of a particular facility there might be (not even via standard facilities).
-Thus, in terms of specifying concepts such as clocks, LED strips, and other hardware-centric concepts that only appear once on circuit board, RESOLVE might benefit from an in-language mechanism that restricts allowable instances of these and other objects.
+Further, an additional language characteristic that we feel would be beneficial is having some means of dictating \textit{static objects}.
+While RESOLVE makes considerations for single instance concepts that are tied to particular facility instantiations, we currently have no means of strictly limiting how many instantiations of a particular facility there might be (not even via standard facilities).
+Thus, in terms of specifying concepts such as clocks, LED strips, and other hardware-centric concepts that only appear once on a circuit board, RESOLVE could benefit from a mechanism that restricts allowable instances of these and other objects.
 
-\section{Conclusions}
+\section{Conclusion}
 
-In this paper we present new RESOLVE language constructs and tools with the objective of translating RESOLVE to embedded platform friendly C.
+In this paper we present a new RESOLVE language construct, and a translation tool that aims to produce an accurate, embedded platform-friendly C representation of RESOLVE.
 We provide representative specifications of an LED strip component that both demonstrates the benefits of RESOLVE's approach to reusable mathematical developments, as well as formal verification of a single driver enhancement.
@@
 We then translate this facility application, illustrating a proof-of-concept dynamic memory allocator working in tandem with what we consider to be an accurate C representation of RESOLVE code.
-The examples and results listed in this paper have been successfully run on a Telos mote, and the overall tool -- now fully integrated with the RESOLVE compiler -- actively continues to undergo improvements and optimizations on all fronts.
+The examples and results listed in this paper have been successfully run on a Telosb mote, and the overall tool -- now fully integrated with the RESOLVE compiler -- actively continues to undergo improvements and optimizations on all fronts.

### 2014-05-01 tech-project/specify_led.tex
changes since initial turn in

--- 2014-04-25 tech-project/specify_led.tex
@@
 In RESOLVE, programs are composed of several different modules that range from interfaces and realizations, to client (facility) modules.
-A \textit{concept} module in RESOLVE defines a specification for a mathematical, abstract type.
+The first we  discuss here, termed a \textit{concept}, defines a specification for a mathematical, abstract type.
 Similar to an interface in Java, a concept provides a number of operation signatures that implementors are expected to realize.
-Shown below is a \texttt{LED\_Template} concept that provides a light strip abstraction.
+Shown below is an \texttt{LED\_Template} concept that provides an LED light strip abstraction.
 
@@
     uses Boolean_Theory, String_Theory;
-    requires 0 < Strip_Length <= 4;
+    requires 0 < Strip_Length
 
@@
         requires 0 <= i < |L|;
-        ensures |L| = |#L| and 
-                   Element_At(i, L) = b;
+        ensures L = (Prt_Btwn(0, i, #L) o <#b>) o
+            Prt_Btwn(i, |#L|, #L) and |L| = |#L|;
 
     Oper Status(preserves L : LED; 
-                   eval i : Integer) : Boolean;
+                        updates b : Boolean;
+            eval i : Integer);
         requires 0 <= i < |L|;
-        ensures Status = Element_At(i, L);
+        ensures Status = Element_At(i, #L);
 
@@
 
-%The \texttt{Type Family} clause introduces an abstract type for the LED strip which we mathematically model using strings of booleans, denoted \texttt{Str(B)}, while the \texttt{exemplar} declared immediately after provides a handle to this type family.
-Use of the \texttt{exemplar} can be observed in the \texttt{constraint} clause, where it is used to assert that length of the strip is fixed to be whatever the user has specified via the \texttt{Strip\_Length} parameter.
-Finally, the \texttt{initialization} \texttt{ensures} clause makes explicit the state of the structure at the time it is initialized.
-We omit this verification specific clause, as it has little bearing on verification due to the fact that the realization we provide is \textit{externally} realized -- a point discussed in the next section\footnote{This clause, if it were provided, would need to communicate the following: ``For each position $i$ within the strip, the LED (or, value) at position $i$ is initially false."}
-
 It's worth noting that unlike the \texttt{LED\_Template} presented in \cite{regula:2010} which models an LED as the \textit{cartesian product} of booleans $b_0$, $b_1$, \ldots , $b_4$, the strip model we present here instead uses strings for the following reasons:
@@
 \item This approach demonstrates the benefits of reusable mathematical theories.
-The specifications listed here are based (almost) entirely in \texttt{String\_Theory} and are therefore able to make use of RESOLVE's pre-existing math libraries.
+Indeed, the specifications listed here are based (almost) entirely in \texttt{String\_Theory} and are therefore able to make use of RESOLVE's pre-existing math libraries.
 \end{itemize}
 
-Finally, the concept provides two operations.
+The concept provides two operations.
 The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}.
-The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} two things upon completion: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}.
+The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} two things upon completion: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}\footnote{Note that the \texttt{ensures} clause in this case is strong enough to assert that \textit{only} the boolean at location \texttt{i} has changed}.
 The \texttt{Status} operation is specified similarly.
-
-%Each operation carries with it a pre and post condition in the form of \texttt{requires} and \texttt{ensures} clause, which make explicit what must be true coming into the function, and what must be true after.
-For instance, the requires clause to \texttt{Status} states that \texttt{i} must fall somewhere within the bounds of the string which models our LED strip, while the \texttt{ensures} clause makes use of a \texttt{String\_Theory} definition, \texttt{Element\_At}, to assert that the boolean returned from \texttt{Status} is indeed the value occupying position \texttt{i} of \texttt{L}.
-It's important to note that the variables appearing in the \texttt{requires} and \texttt{ensures} clauses are strictly mathematical values.
-Thus, the \texttt{L} parameter of operation \texttt{Status} is referring to the mathematical value of an \texttt{LED}, as opposed to a programmatic one (typically defined in a realization).
 
@@
 \begin{verbatim}
-Enhancement Toggling_Capability for LEDs_Template;
+Enhancement Toggling_Capability for LED_Template;
 
     Oper Toggle(upd L : LED; eval i : Integer);
-        requires 0 <= i < |L|;
-        ensures Element_At(i, L) = 
-                        not(Element_At(i, #L));
+        requires i >= 0 and i < |L|
+        ensures L = (Prt_Btwn(0, i, #L) o  
+                  <not(Element_At(i, #L))>) o
+                  Prt_Btwn(i, |#L|, #L);
 end Toggling_Capability;
@@
 Realization Toggling_Realiz for
-            Toggling_Capability of LEDs_Template;
+            Toggling_Capability of LED_Template;
 
     Proc Toggle(upd L : LED; eval i : Integer);
-        Var Content : Boolean;
-
-        Content := Status(L, Replica(i));
-        Set(L, Not(Content), Replica(i));
+        Var Flipped_Contents : Boolean;
+        Status(L, Flipped_Contents, Replica(i));
+        Set(L, Not(Flipped_Contents), Replica(i));
     end Toggle;
@@
 
-Enhancement realizations are neutral as well since any method called within the context of an enhancement realization refers to the operation specified in the concept -- meaning no knowledge of implementation details is required.
+Enhancement realizations are similar in the sense that any operation called within the context of an enhancement realization refers to the operation specified in the concept -- meaning no knowledge of its implementation details are required.
 
@@
 The first step in doing so is to generate Verification Conditions (VCs) for \texttt{Toggle\_Realiz}, which, if proven, will establish the correctness of this particular implementation.
-One thing to note about the VCs themselves is that they are generated from specific lines of a realization, and exist to ensure that the content of the realization is consistent with its specification: This entails checking for things such as array access boundary violations, etc.
+One thing to note about the VCs themselves is that they are generated from specific lines of a realization, and exist to ensure that the content of the realization is consistent with its specification: This entails checking for array access violations, parameters not meeting preconditions, etc.
 
@@
 	\midrule
-	VC 0\_1	& 4426	& 5	& 0	\\
-	VC 0\_2	& 5039	& 5	& 0	\\
-	VC 0\_3	& 6324	& 6	& 0	\\
+	VC 0\_1	& 7009	& 6	& 0	\\
+	VC 0\_2	& 5185	& 5	& 0	\\
+	VC 0\_3	& 3354	& 6	& 0	\\
+	VC 0\_4	& 4810	& 5	& 0	\\
+	VC 0\_5	& 7133	& 5	& 0	\\
 	\bottomrule
@@
 As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness.
-In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety.
+In terms of proof difficulty, given the number of steps and time taken to establish each goal, we conclude that the VCs generated are of a straightforward variety.
 Readers interested however in learning more about the steps and specific actions the prover takes in transforming givens and dispatching similar (and more complex) VCs should refer to \cite{smith:2013}.
@@
         (* Declare LED strip indices *)
-        Var I1, I2, I3 : Integer;
+        Var I0, I1, I2 : Integer;
         Var Loop : Boolean;
@@
 
-        I1 := 1; I2 := 2; I3 := 3;
+        I0 := 0; I1 := 1; I2 := 2;
 
@@
         do
+            Leds_Fac.Toggle(L, I0);
+            Std_Clock_Fac.Wait_500_Milli_Seconds();
+
             Leds_Fac.Toggle(L, I1);
@@
             Leds_Fac.Toggle(L, I2);
-            Std_Clock_Fac.Wait_500_Milli_Seconds();
-
-            Leds_Fac.Toggle(L, I3);
             Std_Clock_Fac.Wait_500_Milli_Seconds();
@@
 \end{verbatim}
-%smaller file sizes
-%reusable code
-%only have to translate a file once
-% be able to say that the code we have is the code that was verified.
-% our approach takes less ROM. Its not less efficient, it is differently efficient.
+
 Prior to using the LED component developed in the previous sections, we first must bind our \texttt{LED\_Template} specification with an appropriate realization.
@@
 Note that the ability to toggle is added \textit{on top} of this facility declaration in a similar fashion.
-The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.
+The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each LED within the strip on, then off.
 
@@
 \includegraphics[scale=.55]{figs/component_graph.pdf}
-\caption{A diagram illustrating inter-component relationships for the example in Section \ref{sec:specifying}}
+\caption{A diagram illustrating inter-component relationships for the example detailed in Section 3.
+Files displayed in clouds indicate externally realized components, while dotted line separating these from others indicates the current boundary between low-level, hardcoded components, and native RESOLVE abstractions.}
 \end{figure*}
@@
 Readers might note that we never presented a realization of \texttt{LED\_Template}.
-Indeed, after having written the concept, the RESOLVE programmer would ideally provide it with a verifiable, native RESOLVE implementation.
+Indeed, after having written the concept, the RESOLVE programmer would ideally provide a verifiable, native RESOLVE implementation.
 However, as our target platform is embedded, and our concept aims to provide control for LEDs -- a decidedly low level feature on embedded hardware -- our realization is forced to operate at similarly low levels by directly manipulating hardware pins provided by the msp430's chipset.
@@
 \begin{itemize}
-\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code.
+\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE.
 The ``externally" keyword now transparently indicates this.

### 2014-05-01 tech-project/implementation.tex
more progress

@@
 
-The previous iteration of this tool \cite{regula:2010} (favoring static allocation) carries out ``pseudo allocation"  by effectively introducing second pass to the compiler dedicated to replacing all formal parameters, with their corresponding facility-instantiated literal values.
+The previous iteration of this tool \cite{regula:2010} achieves static allocation by effectively introducing a second pass to the compiler dedicated to replacing all formal parameters with their corresponding facility-instantiated literal values.
 This additional, hidden step to compilation is less than ideal in the context of a verifying compiler designed from the ground up to be a single pass system.

### 2014-05-01 tech-project/led_trans.tex
more progress

@@
 \end{minipage}
-\caption{C Translation of \texttt{LED\_Telos\_Demo}.}
+\caption{C Translation of \texttt{LED\_Telos\_Demo}. The .h (left) and .c implementation (right).}
 \label{fig:demo}
@@
 One additional thing to note within this create method is the temporary \texttt{\_\_arg\_0} integer variable -- representing the formal value \texttt{Strip\_Length} found within the concept.
-Note that this variable does not appear in the original source, but rather, is created by the translator in an effort to keep track of all literal argument values that require manual deletion.
+Note that this variable does not appear in the original source, but rather, is created by the translator in an effort to keep track of all literal argument values that require manual deletion (as illustrated after the assignment of \texttt{Toggling\_Capability}).
 
@@
 
-Clearly facilities and other modules highly reliant on facility instantiations are no doubt going to consume much more memory than the small example detailed here. To help alleviate some of th
+Clearly, facilities and other modules highly reliant on instantiated facilities are no doubt going to consume much more memory than the small example detailed here -- as each would (naively) be represented as a struct.
+To help alleviate some of this memory usage, we make special considerations in the translated code to only create structs for \textit{enhanced} facilities.
+That is, \textit{unenhanced} facilities (comprising structs with only a single \texttt{core} field) are not created, but rather, dereferenced manually within the source.
+
+The body of the .c file (omitted from Figure \ref{fig:demo} for clarity and space), operates as expected: A C while loop iterates indefinitely, making successive 500ms delayed calls to toggle each LED.
+Perhaps the last thing worth mentioning is the invoking main method:
+
+\begin{verbatim}
+int main() {
+    LED_Telos_Demo_create();
+    Main();
+    LED_Telos_Demo_destroy();
+}
+\end{verbatim}
 
@@
 
-\begin{figure}
-\begin{verbatim}
-int Main() {
-  while(TRUE) {
-    Toggle(L, 0);
-    Wait_500_Milli_Seconds();
-    Toggle(L, 1);
-    Wait_500_Milli_Seconds();
-    Toggle(L, 2);
-    Wait_500_Milli_Seconds();
-  }
-}
+%\begin{figure}
+%\begin{verbatim}
+%int Main() {
+%  while(TRUE) {
+%    Toggle(L, 0);
+%    Wait_500_Milli_Seconds();
+%    Toggle(L, 1);
+%    Wait_500_Milli_Seconds();
+%    Toggle(L, 2);
+%    Wait_500_Milli_Seconds();
+%  }
+%}
 
-int main() {
-  LED_Telos_Demo_create();
-  Main();
-  LED_Telos_Demo_destroy();
-}
-\end{verbatim}
-\label{fig:loop}
-\end{figure}
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
+%int main() {
+%  LED_Telos_Demo_create();
+%  Main();
+%  LED_Telos_Demo_destroy();
+%}
+%\end{verbatim}
+%\label{fig:loop}
+%\end{figure}

### 2014-05-01 tech-project/related_works_and_conclusion.tex
more progress

@@
 
-There are a number of existing systems that ultimately seek to prove the functional correctness of programs.
+Though RESOLVE is the only system we know of that proves, prior to compilation, the full functional correctness of embedded software, there are a number of other systems that 
+%There are a number of existing systems that ultimately seek to prove the functional correctness of programs.
 While we discuss only two here, readers interested in learning more about the systems mentioned might to refer to \cite{klebanov:2011} for a more in depth discussion.
@@
 
-Another system, also a Microsoft research endeavor, is VCC -- a system designed for the verification of C programs \cite{vcc:2009}.
+%Another system, also a Microsoft research endeavor, is VCC -- a system designed for the verification of C programs \cite{vcc:2009}.
 One of the main draws of VCC is that it has mechanisms for verification of concurrent code -- an ideal feature when presented with asynchronous, event driven code common in most embedded applications.
 
-RESOLVE differs from the projects mentioned above most notably in that it does not make use of third party automated provers or decision procedures to discharge verification conditions.
+%RESOLVE differs from the projects mentioned above most notably in that it does not make use of third party automated provers or decision procedures to discharge verification conditions.
 Rather, it makes use of an integrated, minimalist term rewrite prover that applies higher order theorems and definitions in attempting to transform givens into a provable goal.
@@
 While we have made progress with the latter in the form of the externally keyword, a natural direction for future work would entail using RESOLVE's performance specification mechanisms to prove the time and duration estimates for a memory allocator, not unlike the one presented here.
+Indeed, by being able to prove aspects of this system at this level of granularity (down to time and space) confidence in the systems we rely upon everyday (embedded systems included)
+
+proving memory and time constraints on any allocation scheme will provide assurance that we never exceed limitations or behave unexpectedly.
+
+Moreover, if we do In the future if we do it dynamically or statically there is no difference, if the static people are concerned about memory, the It might not seem like we're doing much w
 

### 2014-05-02 tech-project/implementation.tex
fixed minor bugs

@@
 While dynamic allocation is typically the norm, it is not however the first choice for embedded applications.
-With the Telosb mote constrained to 128 bytes of RAM, developers targeting embedded platforms tend to favor static memory allocation over dynamic, due the memory efficiency it affords.
+With the Telosb mote constrained to 10kB of RAM, developers targeting embedded platforms tend to favor static memory allocation over dynamic, due the memory efficiency it affords.
 

### 2014-05-02 tech-project/led_trans.tex
some changes -- references, etc. Starting work on re-rewriting related work

@@
 
-The \texttt{Leds\_Fac} facility from the original source, represented here as a struct, uses a \texttt{core} field to provide a means of accessing the methods and types in the original concept, while any remaining fields correspond to enhancement pointers that serve a similar end -- in this case, providing access to the operations declared within  \texttt{Toggling\_Capability}.
+The \texttt{Leds\_Fac} facility from the original source, represented here as a struct, uses a \texttt{core} field to access the methods and types found in the original concept, while any remaining fields correspond to enhancement pointers that serve a similar end -- in this case, providing access to the operations declared within  \texttt{Toggling\_Capability}.
 
 Clearly, facilities and other modules highly reliant on instantiated facilities are no doubt going to consume much more memory than the small example detailed here -- as each would (naively) be represented as a struct.
-To help alleviate some of this memory usage, we make special considerations in the translated code to only create structs for \textit{enhanced} facilities.
-That is, \textit{unenhanced} facilities (comprising structs with only a single \texttt{core} field) are not created, but rather, dereferenced manually within the source.
+To help alleviate some of this memory usage, we make special considerations in the translator to only create structs for \textit{enhanced} facilities.
+That is, \textit{unenhanced} facilities (comprising structs with only a single \texttt{core} field) are not created, but rather, dereferenced manually within the source via their \texttt{core} field.
 
-The body of the .c file (omitted from Figure \ref{fig:demo} for clarity and space), operates as expected: A C while loop iterates indefinitely, making successive 500ms delayed calls to toggle each LED.
-Perhaps the last thing worth mentioning is the invoking main method:
+The body of the .c file (omitted from Figure \ref{fig:demo} for reasons of clarity and space), operates largely as one would expect: A while loop iterates indefinitely, making successive, 500ms delayed calls to toggle each LED.
+Since calls to \texttt{Set}, \texttt{Status}, and \texttt{Toggle} involved in some form or another within this loop, we note that the the task of allocating and deallocating memory used by the local variables within these methods falls to our dynamic allocator.
+
+The main method we use to invoke this logic is shown below.
 
@@
 }
-\end{verbatim}
-
-%\texttt{new\_Toggling\_Realiz\_for\_Toggling\_Capability\_of\_LED\_Template()}.
-Similarly, this initialization and allocation step must occur for the Integer, Boolean, and Clock facilities.
-From this relatively small example of LED toggling from RESOLVE to C,  complex programs will require even more attention to amount of memory used for each concept and facility realization.
-Curtailing the management of this memory by placing the responsibility on an allocator provides a key motivation for using \texttt{salloc()} and \texttt{sfree()}.
-
-%As seen from above, RESOLVE to C translations can produce verbose output.
-The code presented to the right introduces pseudocode for a toggling capability of an LED strip to simplify understanding of control flow.
-Denoting an LED strip as \texttt{L} and the index represented as an integer literal, this example toggles each LED \footnote{in the case of the telos motes, we will consider the LED strip to have an LED\{0, 1, 2\}} successively, separated by a 500ms delay and is repeated indefinitely through a while-loop.
-
-%Within \texttt{Toggle()}, we use the externally realized LED concepts \texttt{Status()} to get the current state of an LED strip, and \texttt{Set()} to set the specified LED at an index to complement.
-Retrieving the status, as well as setting an LED strip at an index to on or off requires more memory allocation to save these to temporary Boolean and Integer types.
-In this instance, we note that we need to have the capability of creating and destroying an arbitrary number of times, provides another key motivation for dynamic memory allocation.
-Determining the minimum memory size needed, becomes increasingly difficult with the while statement.
-Similarly, other programs may require an implementation of stacks or queues that require a locally unbounded depth.
-
-%Turning to the \texttt{main} function, we first call the appropriate create function to instantiate and allocate all global variables required by the facility.
-We then make a call to the user supplied \texttt{Main()} operation, which performs the user code.
-In normal applications the destroy method will be invoked, however here we employ a busy which prevents it from ever being called.
-
-%A wait utility is then called using the \texttt{Std\_Clock\_Fac} facility.
-This facility uses the externally realized concept to the msp430 \texttt{\_\_delay\_cycles()} command.
-Internally the MCU is delayed for a given number of cycles.
-
-%\begin{figure}
-%\begin{verbatim}
-%int Main() {
-%  while(TRUE) {
-%    Toggle(L, 0);
-%    Wait_500_Milli_Seconds();
-%    Toggle(L, 1);
-%    Wait_500_Milli_Seconds();
-%    Toggle(L, 2);
-%    Wait_500_Milli_Seconds();
-%  }
-%}
-
-%int main() {
-%  LED_Telos_Demo_create();
-%  Main();
-%  LED_Telos_Demo_destroy();
-%}
-%\end{verbatim}
-%\label{fig:loop}
-%\end{figure}
+\end{verbatim}As facility modules are the source of all execution in RESOLVE, this is an ideal place to instantiate all required elements using single call to our facility-defined create method.
+After execution has completed, the destroy method deallocates all globally declared facilities and variables.
+Note that the call to destroy for each individual type, in turn calls a similar destroy method defined within the realization for that particular type, resulting in a cascade effect of deallocation.

### 2014-05-02 tech-project/related_works_and_conclusion.tex

@@
 
-Though RESOLVE is the only system we know of that proves, prior to compilation, the full functional correctness of embedded software, there are a number of other systems that 
-%There are a number of existing systems that ultimately seek to prove the functional correctness of programs.
-While we discuss only two here, readers interested in learning more about the systems mentioned might to refer to \cite{klebanov:2011} for a more in depth discussion.
-Perhaps most notable among the systems we list here (and perhaps the closest to RESOLVE's approach) is Microsoft research's Dafny \cite{leino:2010}.
-Designed to be capable of verifying pointer based structures, Dafny currently stands as one of the more popular approaches to verification.
-Substituting RESOLVE's notion of mathematical variables with what are termed `ghost' variables, reasoning is kept, like RESOLVE, disconnected from implementation-level code.
-Dafny uses an intermediate verification language, termed Boogie, to generate verification conditions which are then dispatched via Z3, Microsoft's automated prover.
+There are a number of existing systems and techniques geared towards verification of embedded programs written in C.
+While we discuss only a handful here, readers interested in learning more about the systems and approaches mentioned are encouraged to refer to the references provided for each.
+
+The first approach, bounded model checking, is the main focus of the work detailed in \ref{cordeiro:2009}.
+
+%Though RESOLVE is the only system we know of that proves, prior to compilation, the full functional correctness of embedded software, there are a number of other systems that
 
@@
 While we have made progress with the latter in the form of the externally keyword, a natural direction for future work would entail using RESOLVE's performance specification mechanisms to prove the time and duration estimates for a memory allocator, not unlike the one presented here.
-Indeed, by being able to prove aspects of this system at this level of granularity (down to time and space) confidence in the systems we rely upon everyday (embedded systems included)
-
-proving memory and time constraints on any allocation scheme will provide assurance that we never exceed limitations or behave unexpectedly.
-
-Moreover, if we do In the future if we do it dynamically or statically there is no difference, if the static people are concerned about memory, the It might not seem like we're doing much w
+Indeed, by being able to prove aspects of this system at time and space level granularity, the question of whether our programs will exhaust stack space becomes a non-issue, as we will be assured -- prior to execution -- that we are within the systems limitations.
 

### 2014-05-02 tech-project/introduction.tex

@@
 From a non-verification related perspective, a variety of tools and languages have been put forth to help make developing embedded applications a simpler, less error prone endeavor.
-On one end of this effort are languages such as NesC, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
-The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Avrora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
+On one end of this effort are languages such as NesC\cite{Gay:2003}, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
+The other end of this effort is largely comprised of simulation tools such as TOSSIM\cite{levis:2003}, Cooja\cite{osterlind:2006}, and Avrora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
 Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed.

### 2014-05-02 tech-project/introduction.tex
changed some bibs

@@
 On one end of this effort are languages such as NesC\cite{Gay:2003}, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions.
-The other end of this effort is largely comprised of simulation tools such as TOSSIM\cite{levis:2003}, Cooja\cite{osterlind:2006}, and Avrora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
+The other end of this effort is largely comprised of simulation tools such as TOSSIM\cite{levis:2003}, Cooja\cite{osterlind:2006}, and Avrora\cite{titzer:2005} that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments.
 Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed.

### 2014-05-03 tech-project/led_trans.tex
fuck

@@
-\section{Putting It All Together}
+\section{EVALUATION}
 
@@
 Depicted in figure \ref{fig:demo} is the C translation of \texttt{LED\_Telos\_Demo} consisting of a .h (left) and a portion of the .c (right).
-The \texttt{LED\_Telos\_Demo\_create()} function provides instantiations for all global facilities used in \texttt{LED\_Telos\_Demo}, including those for standard types such as integers, booleans, clock, as well as local facilities such as \texttt{Leds\_Fac}.
+The \texttt{LED\_Telos\_Demo\_create()} function provides instantiations for all global facilities used in \texttt{LED\_Telos\_Demo}, including those for standard types such as integers, booleans, clock, as well as local facilities such as \texttt{LED\_Fac}.
 One additional thing to note within this create method is the temporary \texttt{\_\_arg\_0} integer variable -- representing the formal value \texttt{Strip\_Length} found within the concept.
@@
 
-The \texttt{Leds\_Fac} facility from the original source, represented here as a struct, uses a \texttt{core} field to access the methods and types found in the original concept, while any remaining fields correspond to enhancement pointers that serve a similar end -- in this case, providing access to the operations declared within  \texttt{Toggling\_Capability}.
+The \texttt{LED\_Fac} facility from the original source, represented here as a struct, uses a \texttt{core} field to access the methods and types found in the original concept, while any remaining fields correspond to enhancement pointers that serve a similar end -- in this case, providing access to the operations declared within  \texttt{Toggling\_Capability}.
 

### 2014-05-03 tech-project/specify_led.tex
fuck

@@
 
-end LEDs_Template;
+end LED_Template;
 \end{verbatim}
@@
 
-    Facility Leds_Fac is LED_Template(3)
-        externally realized by Std_Led_Realiz
+    Facility LED_Fac is LED_Template(3)
+        externally realized by Std_LED_Realiz
      enhanced by Toggling_Capability
@@
         (* Declare an LED strip *)
-        Var L : Led;
+        Var L : LED;
 
@@
         do
-            Leds_Fac.Toggle(L, I0);
+            LED_Fac.Toggle(L, I0);
             Std_Clock_Fac.Wait_500_Milli_Seconds();
 
-            Leds_Fac.Toggle(L, I1);
+            LED_Fac.Toggle(L, I1);
             Std_Clock_Fac.Wait_500_Milli_Seconds();
 
-            Leds_Fac.Toggle(L, I2);
+            LED_Fac.Toggle(L, I2);
             Std_Clock_Fac.Wait_500_Milli_Seconds();

### 2014-05-03 tech-project/telos_platform.tex
changes since initial turn in
fixed minor bugs
fuck

@@
 
-The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley.
-Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory.
-A cc2420 radio stack provides the mote with broadcast and receiving capabilities, while optional sensing capabilities may be added in the form of light, humidity, and temperature sensors.
+The Telos mote\cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley.
+Its hardware includes an MSP430-F1611 microcontroller containing 10kB of RAM and 48kB of programmable flash memory\cite{msp:2011}.
+A CC2420 radio stack provides the mote with broadcast and receiving capabilities, while optional sensing capabilities may be added in the form of light, humidity, and temperature sensors.
 The mote also contains three onboard LEDs: One blue, one red, and one green.
-
-%Additionally, the Telos board contains a total of three LEDs -- one red, one green, and one blue.
